### 2014-06-06 paper/paper.tex
start paper

\documentclass[JIP]{ipsj}

\usepackage{graphicx}
\usepackage{latexsym}

\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
\def\|{\verb|}

\setcounter{volume}{20}
\setcounter{number}{4}
\setcounter{page}{1}

\usepackage[varg]{txfonts}%%!!
\makeatletter%
\input{ot1txtt.fd}
\makeatother%

\begin{document}

\title{Towards Cloud Bursting for Extreme Scale Supercomputers}
\affiliate{Titech}{Tokyo institute of technology, Meguro, Tokyo, 152-8550,Japan}

\author{Tianqi Xu}{Titech}
\author{Kento Sato}{Titech}
\author{Satoshi Matsuok}{Titech}

\begin{abstract}
\end{abstract}

\begin{keyword}
	Cloud, I/O Buffer Model, Supercomputer
\end{keyword}

\maketitle

%1
\section{Introduction}

\end{document}

### 2014-06-09 paper/paper.tex
1
0609

@@
-\documentclass[JIP]{ipsj}
-
-\usepackage{graphicx}
-\usepackage{latexsym}
-
-\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
-\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
-\def\|{\verb|}
-
-\setcounter{volume}{20}
-\setcounter{number}{4}
-\setcounter{page}{1}
-
-\usepackage[varg]{txfonts}%%!!
-\makeatletter%
-\input{ot1txtt.fd}
-\makeatother%
+\documentclass[JIP,draft]{ipsj}
 
@@
 \title{Towards Cloud Bursting for Extreme Scale Supercomputers}
-\affiliate{Titech}{Tokyo institute of technology, Meguro, Tokyo, 152-8550,Japan}
-
-\author{Tianqi Xu}{Titech}
-\author{Kento Sato}{Titech}
-\author{Satoshi Matsuok}{Titech}
 
 \begin{abstract}
+Nowadays Supercomputers are widely used in scientifical computation, such as simulation and data analyse etc. 
+Parallel programming are used to reduce execution time of complex problems, also fully utilizing computing resource of Supercomputers.
+However, large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
+One solution is running virtual machine on 
+In this paper, a comparision was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
 \end{abstract}
@@
 \section{Introduction}
+An increasing number of scientifical application are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency Ethernet environment, also a great number of processors for high scalability.
+High parallel application runs faster on Supercomputer for fully usage of computing resource.
+However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
+Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, casusing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
+One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer.
+However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critial in summer and nearly half of computing nodes have be shutted down to reduce electricity consumation in the case of TSUBAME Supercomputer.
+
+%2
+\section{Background}
+
+%3
+\section{}
 

### 2014-06-10 paper/paper.tex
0610

@@
 \begin{document}
-
 \title{Towards Cloud Bursting for Extreme Scale Supercomputers}
@@
 \begin{keyword}
-	Cloud, I/O Buffer Model, Supercomputer
+Supercomputer, Cloud, I/O Buffer Model
 \end{keyword}
@@
 \section{Introduction}
-An increasing number of scientifical application are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency Ethernet environment, also a great number of processors for high scalability.
+An increasing number of scientifical applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
 High parallel application runs faster on Supercomputer for fully usage of computing resource.
@@
 However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critial in summer and nearly half of computing nodes have be shutted down to reduce electricity consumation in the case of TSUBAME Supercomputer.
+Facing these problems, one solution will be federate supercomputer with public cloud.
+By using pulic cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
+Of cause, there will be many callenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also
 

### 2014-06-10 paper/paper.tex
0610

@@
 By using pulic cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-Of cause, there will be many callenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also
+Of cause, there will be many callenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
 
@@
 %3
-\section{}
+\section{I/O Buffer Model}
+\subsection{
 

### 2014-06-12 paper/paper.tex
0611

@@
 \documentclass[JIP,draft]{ipsj}
+\usepackage{graphicx}
 
@@
 \begin{keyword}
-Supercomputer, Cloud, I/O Buffer Model
+Supercomputer, Cloud, I/O Bursting Buffer Model
 \end{keyword}
@@
 %3
-\section{I/O Buffer Model}
-\subsection{
+\section{I/O Bursting Buffer}
+An overview of cloud environment and I/O Burst Buffer Model is described in this section.
+
+\subsection{Cloud Environment}
+First each cloud is defined as follow:
+
+For security consideration and the fact that IPv4 addresses becomes rare, all computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each cloud, so topology is not specifid here, interconnection network performance is measured by throughput.
+There are a constant number of public IP addresses can be assigned to some computing nodes.
+There is a shared storage for date sharing inside cloud, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
+
+\subsection{I/O Bursting Buffer Archiecture}
+Fig.~\ref{overview} is the overall illustrate of I/O Bursting Buffer Model
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=6cm]{overview}
+	\caption{overall illustrate of I/O Bursting Buffer Archiecture}
+	\label{overview}
+\end{figure}
+There are two clouds here, cloud condition is defined above.
+Orange arrows stand for innerconnection networks, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
+Circles stand for computing nodes, which are used for standard computation.
+Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
+I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
+cylinders are shared storages, which are used to store data used by computing nodes.
+Both I/O buffer nodes and computing nodes are connected with shared storages.
+
+For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.
+
+\section{I/O Bursting Buffer Model}
+
+\subsection{data reading}
+When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splited into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.
+
+After transfering data from shared storage, a I/O buffer node in cloud 1 connects with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2, and transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
 

### 2014-06-12 paper/paper.tex
0611

@@
 \subsection{data reading}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=8cm]{reading}
+	\caption{data reading operation}
+	\label{reading}
+\end{figure}
+
 When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splited into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.

### 2014-06-12 paper/paper.tex
0612

@@
 %3
-\section{I/O Bursting Buffer}
+\section{I/O Bursting Buffer Overview}
 An overview of cloud environment and I/O Burst Buffer Model is described in this section.
@@
 
-For security consideration and the fact that IPv4 addresses becomes rare, all computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each cloud, so topology is not specifid here, interconnection network performance is measured by throughput.
+%For security consideration and the fact that IPv4 addresses becomes rare,
+All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each cloud, so topology is not specifid here, interconnection network performance is measured by throughput.
 There are a constant number of public IP addresses can be assigned to some computing nodes.
@@
 \subsection{I/O Bursting Buffer Archiecture}
-Fig.~\ref{overview} is the overall illustrate of I/O Bursting Buffer Model
+
 \begin{figure}[tb]
@@
 \end{figure}
+
+Fig.~\ref{overview} is the overall illustrate of I/O Bursting Buffer Model
+
 There are two clouds here, cloud condition is defined above.
-Orange arrows stand for innerconnection networks, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
+
+Arrows stand for network connection.
+Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
+Black arrows are Internet connections, since there are a few amount of public IP addresses avaliable, only I/O buffer nodes are connect to Internet, also the amount of avaliable public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
+Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
+
 Circles stand for computing nodes, which are used for standard computation.
+Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
 Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
 I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-cylinders are shared storages, which are used to store data used by computing nodes.
-Both I/O buffer nodes and computing nodes are connected with shared storages.
+Cylinders are shared storages, which are used to store data used by computing nodes, .
 
@@
 \section{I/O Bursting Buffer Model}
+
+There are many facts will affect throughput of Internet,
 

### 2014-06-12 paper/paper.tex
0612

@@
 However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critial in summer and nearly half of computing nodes have be shutted down to reduce electricity consumation in the case of TSUBAME Supercomputer.
+
 Facing these problems, one solution will be federate supercomputer with public cloud.
@@
 Of cause, there will be many callenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
+Since the biggest problem will be data transfer throughput between two clouds, this paper focuses on methodology of increasing throughput.
 
+In order to increase data transfer throughtput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transfering, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
+Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
+Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, this model evalues total cost with and without I/O nodes.
+
+Our contribution can be summary as following:
+\begin{itemize}
+	\item An architecture of I/O bursting buffer for increasing data transfer throughput between two clouds.
+	\item A throughput-based I/O bursting buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when fedorating two clouds, and a cost-based I/O bursting buffer model uses to reduce the total cost.
+	%\item 
+	\item a evaluation of i/o busrting buffer archiecture and two models by using data taken from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
+\end{itemize}
 %2
@@
 \section{I/O Bursting Buffer Overview}
-An overview of cloud environment and I/O Burst Buffer Model is described in this section.
+An overview of I/O Burst Buffer archiecture is described in this section. 
+Although our gloal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we federate virtual machine nodes running on supercomputer physical nodes with public cloud.
+In the follow section, we treat the set of supercomputer's virtual machines as a cloud environment
 
@@
 	\centering
-	\includegraphics[width=6cm]{overview}
+%	\includegraphics[width=6cm]{overview}
 	\caption{overall illustrate of I/O Bursting Buffer Archiecture}
@@
 I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-Cylinders are shared storages, which are used to store data used by computing nodes, .
+Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
+
+%Since there is a big gap between cloud inside data transfering and accross two clouds in throughput, our goal is to fill the gap.
 
@@
 
-\section{I/O Bursting Buffer Model}
-
-There are many facts will affect throughput of Internet,
-
-\subsection{data reading}
+\subsubsection{Data Reading}
 
@@
 	\centering
-	\includegraphics[width=8cm]{reading}
+%	\includegraphics[width=8cm]{reading}
 	\caption{data reading operation}
@@
 
-When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splited into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.
+When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splited into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth, I/O buffer nodes use a main index to refer to the data position in global data.
 
-After transfering data from shared storage, a I/O buffer node in cloud 1 connects with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2, and transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
+After transfering data from shared storage, a I/O buffer node in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2, here a sub-index is used to refer to each piece's position, then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
+
+When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using main index and sub-index, of cause all data transfer are done in parallel.
+
+\subsubsection{Data Writing}
+
+\begin{figure}[tb]
+	\centering
+%	\includegraphics[width=8cm]{writing}
+	\caption{data writing operation}
+	\label{writing}
+\end{figure}
+
+Data writing operation doing the opposite operation as reading operation.
+
+When a node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
+After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes with index refering to data position Simultaneously.
+
+I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position. and
+
+\subsubsection{Index Protocol}
+
+\begin{figure}[tb]
+	\centering
+%	\includegraphics
+	\caption{index protocol}
+	\label{index protocol}
+\end{figure}
+
+\section{I/O Bursting Buffer Model}
+Throughput-based Model and Cost-based Model will be discribed in this section.
+
+\subsection{Throughput-based Model}
+There are many facts will affect throughput of Internet,
 

### 2014-06-14 paper/paper.tex
0613

--- 2014-06-12 paper/paper.tex
@@
 \usepackage{graphicx}
+\usepackage{amsmath}
 
@@
 \section{Introduction}
-An increasing number of scientifical applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
+An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
 High parallel application runs faster on Supercomputer for fully usage of computing resource.
 However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
-Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, casusing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
+Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
 One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer.
-However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critial in summer and nearly half of computing nodes have be shutted down to reduce electricity consumation in the case of TSUBAME Supercomputer.
+However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.
+
 Facing these problems, one solution will be federate supercomputer with public cloud.
-By using pulic cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-Of cause, there will be many callenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
+By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
+Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
+Since the biggest problem will be data transfer throughput between two clouds, this paper focuses on methodology of increasing throughput.
 
+In order to increase data transfer throughput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
+Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
+Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, this model evaluate total cost with and without I/O nodes.
+
+Our contribution can be summary as following:
+\begin{itemize}
+	\item An architecture of I/O bursting buffer for increasing data transfer throughput between two clouds.
+	\item A throughput-based I/O bursting buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two clouds, and a cost-based I/O bursting buffer model uses to reduce the total cost.
+	%\item 
+	\item a evaluation of i/o bursting buffer architecture and two models by using data taken from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
+\end{itemize}
 %2
@@
 \section{I/O Bursting Buffer Overview}
-An overview of cloud environment and I/O Burst Buffer Model is described in this section.
+An overview of I/O Burst Buffer architecture and two operations: reading writing are described in this section.
+Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
+Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment.
+
+Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage.
+
+Migration operation occurs when some nodes have to be shutted down in one cloud 
+all jobs running on these nodes have to be backed up by using snapshot,
 
@@
 %For security consideration and the fact that IPv4 addresses becomes rare,
-All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each cloud, so topology is not specifid here, interconnection network performance is measured by throughput.
+All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each cloud, so topology is not specified here, interconnection network performance is measured by throughput.
 There are a constant number of public IP addresses can be assigned to some computing nodes.
@@
 
-\subsection{I/O Bursting Buffer Archiecture}
+\subsection{I/O Bursting Buffer Architecture}
 
@@
 	\centering
-	\includegraphics[width=6cm]{overview}
-	\caption{overall illustrate of I/O Bursting Buffer Archiecture}
+%	\includegraphics[width=6cm]{overview}
+	\caption{overall illustrate of I/O Bursting Buffer Architecture}
 	\label{overview}
@@
 Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
-Black arrows are Internet connections, since there are a few amount of public IP addresses avaliable, only I/O buffer nodes are connect to Internet, also the amount of avaliable public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
+Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
 Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
@@
 I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-Cylinders are shared storages, which are used to store data used by computing nodes, .
+Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
+
+%Since there is a big gap between cloud inside data transferring and accross two clouds in throughput, our goal is to fill the gap.
 
@@
 
-When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splited into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.
+When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
 
-After transfering data from shared storage, a I/O buffer node in cloud 1 connects with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2, and transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
+After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
+%here a sub-index is used to refer to each piece's position, 
+then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
+
+When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
+
+\subsubsection{Data Writing}
+
+\begin{figure}[tb]
+	\centering
+%	\includegraphics[width=8cm]{writing}
+	\caption{data writing operation}
+	\label{writing}
+\end{figure}
+
+Data writing operation doing the opposite operation as reading operation.
+
+When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
+After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.
+
+I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position.
+and then start to transfer data concurrently.
+
+Then I/O buffer nodes write data to storage in cloud 1.
+
+\subsubsection{Index Protocol}
+
+\begin{figure}[tb]
+	\centering
+%	\includegraphics
+	\caption{index protocol}
+	\label{index protocol}
+\end{figure}
+
+As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
+There are two phases of data splitting in both reading and writing operation,
+
+\section{I/O Bursting Buffer Model}
+
+\begin{figure}[tb]
+	\centering
+%	\includegraphics
+	\caption{definition}
+	\label{definition}
+\end{figure}
+
+Throughput-based Model and Cost-based Model will be described in this section.
+All definitions used are described in Fig.~\ref{definition}:
+
+\begin{itemize}
+	\item Numbers of computing nodes are $c_1,c_2$, and numbers of I/O buffer nodes are $n_1, n_2$ respectively.
+	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in cloud 1 connect to storage in cloud 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each cloud have Internet connection.
+	\item Since overall Internet throughput is affected by number of nodes involved in connection. $I(n_1,n_2)$ is used to refer to Internet throughput using $n_1,n_2$ I/O buffer nodes respectively.
+	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in cloud 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in cloud 2 with $n_2$ I/O nodes.
+	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in cloud 1 and ,storage and $n_2$ I/O nodes in cloud 2.
+	\item Cost for standard node in cloud 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in cloud 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.
+
+\end{itemize}
+
+\subsection{Throughput-based Model}
+%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
+When I/O buffer nodes in cloud 2 connect to storage in cloud 1, there are two data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to storage in cloud 1, so throughput will be:
+
+\begin{equation}
+	\text{throughput}_{\text{direct}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
+\end{equation}
+
+In the case of using I/O buffer nodes in both cloud, there are three data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to I/O buffer nodes in cloud 1, I/O buffer nodes in cloud 1 to storage in cloud 1, throughput will be:
+
+\begin{equation}
+	\text{throughput}_{\text{I/O buffer}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
+\end{equation}
+
+In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:
+
+\begin{equation}
+	\begin{cases}
+		\text{throughput}_{\text{direct}} \geq \text{throughput}_{\text{I/O buffer}} & \text{use direct connection}\\
+		\text{throughput}_{\text{direct}} < \text{throughput}_{\text{I/O buffer}} & \text{use I/O buffer}
+	\end{cases}
+\end{equation}
+
+\subsection{Cost-based Model}
+In the case of cost-based model, we consider
+using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:
+
+\begin{equation}
+	\begin{cases}
+		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{direct connection}\\
+		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{I/O buffer}
+	\end{cases}
+\end{equation}
+
+here we compute cost by using $T_1,T_2$:
+\begin{equation}
+	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
+\end{equation}
+\begin{align}
+	\text{cost}_\text{I/O buffer}&=c_2\times C_2\_Money(T_2)\\\nonumber 
+				     &+n_1\times C_1\_High\_Money(T_2)\\ \nonumber
+				     &+n_2\times C_2\_High\_Money(T_2)
+\end{align}
+\subsection{Migration Model}
+%\begin{equation}
+
+%\end{eqaution}
+\section{Evaluation}
 

### 2014-06-17 performance/TSUBAME/IOR/S3/auto.py
add S3

@@ -1,0 +1,24 @@
+#!/usr/bin/python
+
+#auto process expironment data
+import xlwt
+import os
+
+excel = xlwt.Workbook()
+sheet = excel.add_sheet('sheet 1')
+sheet.write(0,1,'write')
+sheet.write(0,2,'read')
+i=1
+pwd=os.getcwd()
+for file in os.listdir(pwd+'/data'):
+	f=open(pwd+'/data/'+file,'r')
+	content=f.read().split('\n')
+	try:
+		sheet.write(i,0,file)
+		sheet.write(i,1,float(content[35][11:16]))
+		sheet.write(i,2,float(content[36][11:16]))
+	except IndexError:
+		print content
+	i=i+1
+	f.close()
+excel.save('TSUBAME IOR S3.xls')

### 2014-06-17 paper/paper.tex
0617

@@
 	%\item 
-	\item a evaluation of i/o bursting buffer architecture and two models by using data taken from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
+	\item a evaluation of I/O bursting buffer architecture and two models by using data taken from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
 \end{itemize}
@@
 \section{I/O Bursting Buffer Overview}
-An overview of I/O Burst Buffer architecture and two operations: reading writing are described in this section.
+An overview of I/O Burst Buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
 Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
-Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment.
+Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.
 
-Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage.
+%Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage
 
-Migration operation occurs when some nodes have to be shutted down in one cloud 
-all jobs running on these nodes have to be backed up by using snapshot,
+%Migration operation occurs when some nodes have to be shutted down in one cloud 
+%all jobs running on these nodes have to be backed up by using snapshot,
 
@@
 
-\subsubsection{Data Reading}
+\subsubsection{Direct Connection}
+
+\begin{figure}[tb]
+	\centering
+%	\includegraphics[width=8cm]{direct}
+	\caption{direct access}
+	\label{direct access}
+\end{figure}
+
+As Fig.~\ref{} shows, direct connection is a connection between I/O buffer nodes in cloud 2 and storage cloud 2 directly, only one side I/O buffer nodes are used in this model.
+When computing nodes issue a read request, data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
+After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.
+
+Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
+After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
+When I/O buffer nodes received data, then they writing data back to storage in cloud 1.
+
+\subsubsection{I/O Bursting Buffer}
 
@@
 
-When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assgined a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
+\begin{figure}[tb]
+	\centering
+%	\includegraphics[width=8cm]{writing}
+	\caption{data writing operation}
+	\label{writing}
+\end{figure}
+
+I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
+
+When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
 
@@
 When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
-
-\subsubsection{Data Writing}
-
-\begin{figure}[tb]
-	\centering
-%	\includegraphics[width=8cm]{writing}
-	\caption{data writing operation}
-	\label{writing}
-\end{figure}
 
@@
 \subsection{Migration Model}
-%\begin{equation}
-
-%\end{eqaution}
+Since there are some condition that some supercomputer nodes must be shutted down, and jobs running on these nodes have to be migrate to another cloud. There are 
+\begin{equation}
+	Data	
+\end{equation}
 \section{Evaluation}
-
+In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2, 
 \end{document}

### 2014-06-18 paper/paper.tex
0618

@@
 An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
-High parallel application runs faster on Supercomputer for fully usage of computing resource.
-However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
-Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
-One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer.
-However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.
+Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
 
-Facing these problems, one solution will be federate supercomputer with public cloud.
-By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
-Since the biggest problem will be data transfer throughput between two clouds, this paper focuses on methodology of increasing throughput.
+%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
+However, when operating a supercomputer, there are some problems, high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
+Another problem is the power problem in summer, in order to reduce power comsumation, some nodes will be forced to be shutted down, reducing numbers of nodes will make the first problem more serous.
+One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
+Although cloud bursting is used by several companies and already have some sophisticated solution, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to ferderate a supercomputer with a public cloud.
+The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user.
+This paper focuses on methodology of increasing throughput when we do federation.
 
 In order to increase data transfer throughput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
+This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
 Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
@@
 	%\item 
-	\item a evaluation of I/O bursting buffer architecture and two models by using data taken from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
+	\item Evaluating I/O bursting buffer architecture and two models by using data obtained from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
 \end{itemize}
 %2
-\section{Background}
+The remainder of this paper is orginized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
+will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
+
+\section{Motivation and Background}
+
+%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
+%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
+%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
+%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
+%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
+%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
+%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
+%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.
+Since the 
+Facing these problems, one solution will be federate supercomputer with public cloud.
+By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
+Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
 
@@
 \end{align}
+
 \subsection{Migration Model}

### 2014-06-18 paper/paper.tex
0618

@@
 Another problem is the power problem in summer, in order to reduce power comsumation, some nodes will be forced to be shutted down, reducing numbers of nodes will make the first problem more serous.
+
 One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
@@
 %However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.
-Since the 
-Facing these problems, one solution will be federate supercomputer with public cloud.
-By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
+%Facing these problems, one solution will be federate supercomputer with public cloud.
+%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
+%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
+
+Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
+\begin{figure}[tb]
+	\centering
+	%\includegraphics{}
+	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
+	\label{throughput TSUBAME}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	%\includegraphics{}
+	\caption{I/O Throughput from AMAZON EC2 to TSUBAME Lustre by using sshfs}
+	\label{throughput AMAZON to TSUBAME Lustre}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	%\includegraphics{}
+	\caption{point to point connection TSUBAME}
+	\label{point to point connection TSUBAME}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	%\includegraphics{}
+	\caption{point to point connection inside AMAZON}
+	\label{point to point connection AMAZON}
+\end{figure}
+
+From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
+If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of low throughput, for a data sensitive application, it will be devastating.
+
+But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput
 
@@
 
-As Fig.~\ref{} shows, direct connection is a connection between I/O buffer nodes in cloud 2 and storage cloud 2 directly, only one side I/O buffer nodes are used in this model.
+As Fig.~\ref{direct access} shows, direct connection is a connection between I/O buffer nodes in cloud 2 and storage cloud 2 directly, only one side I/O buffer nodes are used in this model.
 When computing nodes issue a read request, data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
@@
 There are two phases of data splitting in both reading and writing operation,
+
+\subsubsection{Node Migration}
+Node migration happens when some nodes have to be shutted down due to some situation like power problem in summer, and still need to provide service to users.
+In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
+
+However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
+When using I/O buffer nodes
 
@@
 \end{equation}
+
 \section{Evaluation}
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2, 
+In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2.
+
+\section{Conclusion and Related Work}
+
 \end{document}

### 2014-06-18 paper/paper.tex
0619

@@
 	\centering
-%	\includegraphics[width=6cm]{overview}
+	\includegraphics[width=6cm]{overview}
 	\caption{overall illustrate of I/O Bursting Buffer Architecture}
@@
 	\centering
-%	\includegraphics[width=8cm]{reading}
+	\includegraphics[width=8cm]{reading}
 	\caption{data reading operation}
@@
 	\centering
-%	\includegraphics[width=8cm]{writing}
+	\includegraphics[width=8cm]{writing}
 	\caption{data writing operation}
@@
 
-\begin{figure}[tb]
-	\centering
+%\begin{figure}[tb]
+%	\centering
 %	\includegraphics
-	\caption{definition}
-	\label{definition}
-\end{figure}
+%	\caption{definition}
+%	\label{definition}
+%\end{figure}
 
 Throughput-based Model and Cost-based Model will be described in this section.
-All definitions used are described in Fig.~\ref{definition}:
+All definitions used are described in Fig.~\ref{overview}:
 
@@
 \section{Evaluation}
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=8cm]{ThroughputAMAZONTSUBAME}
+	\caption{Throughput between AMAZON and TSUBAME}
+	\label{Throughput between AMAZON and TSUBAME}
+\end{figure}
+
 In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2.

### 2014-06-22 paper/paper.tex
0622

@@
 \begin{abstract}
-Nowadays Supercomputers are widely used in scientifical computation, such as simulation and data analyse etc. 
-Parallel programming are used to reduce execution time of complex problems, also fully utilizing computing resource of Supercomputers.
-However, large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
-One solution is running virtual machine on 
-In this paper, a comparision was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
+%Parallel programming are used to reduce execution time of complex problems, also fully utilizing computing resource of Supercomputers.
+
+%supercomputers usually consist of a large number of nodes, provide high parallelism for multi-user.
+%However computing nodes in supercomputers will not meet the request in some situation, such as some nodes have to be shutted down to reduce electric consumption in summer or just several serial applications occupy nodes making others must wait.
+%large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
+%One solution is running virtual machine on 
+%In this paper, a comparision was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
+%In order to satisfy these temporary request peak, we are trying to federate supercomputers with public cloud, which is known as cloud bursting.
+%Although some sophisticated solutions are available, still we are facing several challenges, since there are a significant performance gap between supercomputers and public cloud.
+%In this paper, we focus on I/O throughput between these two environments, we propose a I/O Bursting Buffer Model to burst I/O throughput between supercomputer and public cloud and reduce the cost for extra time usage caused by low I/O throughput.
+%we also provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
+%The result shows our model can provide a stable and high I/O throughput as well as a low cost in most cases.
+
+Extreme-scale HPC systems, which consist of a large number of compute nodes, can provide high computational capacity for multiple users.
+However, computing nodes in the systems occasionally can not meet the demand due to bursty job requests in short period times.
+In order to accommodate the bursty requests, we consider federating HPC systems with public clouds, which is known as cloud bursting.
+Although the federated systems can acquire virtually infinite computational power with cloud bursting, the QoS may not be guaranteed due to a significant performance gap between HPC systems and public clouds.
+The most critical problem is a gap in I/O performance.
+In this paper, we propose an I/O acceleration technique using distributed cloud bursting buffers.
+We also create the I/O performance model to explore the effectiveness.
+Our model-based simulations, which target the TSUBAME supercomputer for an HPC system, and AMAZON EC2 for a public cloud, show that the distributed cloud busting buffer can improve I/O throughput while reducing the cost.
+
 \end{abstract}
@@
 An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
-Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
+%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
 
 %Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-However, when operating a supercomputer, there are some problems, high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
+Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until perious job finished although there are
+%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
 Another problem is the power problem in summer, in order to reduce power comsumation, some nodes will be forced to be shutted down, reducing numbers of nodes will make the first problem more serous.
@@
 
-Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
+%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
 \begin{figure}[tb]
@@
 	%\includegraphics{}
-	\caption{point to point connection TSUBAME}
-	\label{point to point connection TSUBAME}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics{}
 	\caption{point to point connection inside AMAZON}
@@
 \end{figure} 
+As we know, throughput gap between innerconnection network and Internet is extremely large.
+Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes and TSBUAME Lustre file system, we can see that the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in [].
+On the other hand, Fig.~\ref{throughput AMAZON to TSUBAME Lustre} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and TSUBAME Lustre file system, the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
+%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
+If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy, longer execution time means more cost.
 
-From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
-If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of low throughput, for a data sensitive application, it will be devastating.
-
-But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput
+%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput 
+However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection TSUBAME}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, and it shows a strong scalability.
+Since we can achieve a high innerconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
 
@@
 \section{I/O Bursting Buffer Overview}
-An overview of I/O Burst Buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
-Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
-Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.
+
+\begin
+
+An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
+The main idea is we use some of computing nodes as a I/O buffer nodes in each system, I/O data will first buffered in these I/O buffer nodes, and then transferred to storage in another system, 
+Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in all I/O buffer nodes in the same system
+%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
+%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.
 
@@
 
-\subsection{Cloud Environment}
-First each cloud is defined as follow:
+\subsection{System Environment}
+First a general system is defined as follow:
 
 %For security consideration and the fact that IPv4 addresses becomes rare,
-All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each cloud, so topology is not specified here, interconnection network performance is measured by throughput.
+All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
 There are a constant number of public IP addresses can be assigned to some computing nodes.
-There is a shared storage for date sharing inside cloud, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
+There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
 
@@
 
-There are two clouds here, cloud condition is defined above.
+There are two system here, and conditions are defined above.
 

### 2014-06-23 paper/paper.tex
0623

@@
 As we know, throughput gap between innerconnection network and Internet is extremely large.
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes and TSBUAME Lustre file system, we can see that the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in [].
+Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes and TSBUAME Lustre file system, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in [].
 On the other hand, Fig.~\ref{throughput AMAZON to TSUBAME Lustre} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and TSUBAME Lustre file system, the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
@@
 
-\begin
+%\begin
 
 An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
-The main idea is we use some of computing nodes as a I/O buffer nodes in each system, I/O data will first buffered in these I/O buffer nodes, and then transferred to storage in another system, 
-Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in all I/O buffer nodes in the same system
+The main idea is we use some of computing nodes as a I/O buffer nodes in each system, I/O data will be buffered in the same 
+%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
+Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in all I/O buffer nodes in the same system,
 %Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
@@
 	\centering
-	\includegraphics[width=8cm]{ThroughputAMAZONTSUBAME}
+	%\includegraphics[width=8cm]{ThroughputAMAZONTSUBAME}
 	\caption{Throughput between AMAZON and TSUBAME}

### 2014-06-23 paper/paper.tex
0623

@@
 \usepackage{amsmath}
+\usepackage{verbatim}
 
@@
 %Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until perious job finished although there are
+Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until perious job finished although there are 49 nodes remainning available.
 %high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
@@
 	\centering
+	\includegraphics[width=7cm]{point_to_point_lab}
 	%\includegraphics{}
@@
 	\centering
+	\includegraphics[width=7cm]{point_to_point_lab}
 	%\includegraphics{}
-	\caption{I/O Throughput from AMAZON EC2 to TSUBAME Lustre by using sshfs}
-	\label{throughput AMAZON to TSUBAME Lustre}
+	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
+	\label{throughput AMAZON to MATSULAB}
 \end{figure}
@@
 \end{figure}
-As we know, throughput gap between innerconnection network and Internet is extremely large.
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes and TSBUAME Lustre file system, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in [].
-On the other hand, Fig.~\ref{throughput AMAZON to TSUBAME Lustre} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and TSUBAME Lustre file system, the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=7cm]{point_to_point_lab}
+	\caption{point to point connection throughput between AMAZON and our lab}
+	\label{point to point connection LAB}
+\end{figure}
+
+As we know, throughput gap between innerconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
+Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in [].
+On the other hand, Fig.~\ref{throughput AMAZON to MATSULAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access, since TSUBAME Lustre can not be mountted outside of TSUBAME because of security problem, we use a file system inside our lab instead of TSUBAME Lustre file system, we can see that the I/O throughput also grows as number of nodes grows but the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
 %From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
+%Also, if we compare the one nodes I/O throughput, 
 If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy, longer execution time means more cost.
@@
 %But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput 
-However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection TSUBAME}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, and it shows a strong scalability.
+However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, and it shows a strong scalability.
 Since we can achieve a high innerconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
@@
 An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
-The main idea is we use some of computing nodes as a I/O buffer nodes in each system, I/O data will be buffered in the same 
+As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
+The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be tranferred to final storage system.
 %the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
-Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in all I/O buffer nodes in the same system,
+Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
+Since data transfer rate is extremely low in Internet compared to innerconnection network, user do not want to ,in this model, we just consider the situation that all nodes used for the same job are settled in the same system.
 %Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
@@
 \subsection{System Environment}
-First a general system is defined as follow:
+First a general system used in following sections is defined as follow:
 
 %For security consideration and the fact that IPv4 addresses becomes rare,
-All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
-There are a constant number of public IP addresses can be assigned to some computing nodes.
-There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
+\begin{itemize}
+	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
+	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
+	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
+\end{itemize}
 
-\subsection{I/O Bursting Buffer Architecture}
+\subsection{I/O Burst Buffer Architecture}
 
@@
 	\centering
-	\includegraphics[width=6cm]{overview}
-	\caption{overall illustrate of I/O Bursting Buffer Architecture}
+	\includegraphics[width=7cm]{IOserver}
+	\caption{I/O server and buffer queue}
+	\label{I/O server}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=7cm]{overview}
+	\caption{overall illustrate of I/O Burst Buffer Architecture}
 	\label{overview}
@@
 
-Fig.~\ref{overview} is the overall illustrate of I/O Bursting Buffer Model
+%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
+There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assgined only  and I/O burst buffer nodes, which assigned both private IP address.
 
-There are two system here, and conditions are defined above.
+Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
+In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
+Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
 
-Arrows stand for network connection.
-Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
-Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
-Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
+When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
+First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are settled in the same system, so data consistency can be guaranteed since that.
+Buffer queue operation includeing data write back and operation when queue is full will be described in following section.
 
-Circles stand for computing nodes, which are used for standard computation.
-Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
-Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
-I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
+When user issue a read request, there are two conditions: file is bufferred in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
+In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
+If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.
+
+Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture:
+Consider there are two systems, named system 1 and system 2, and we assume that 
+%Arrows stand for network connection.
+%Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
+%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
+%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
+
+%Circles stand for computing nodes, which are used for standard computation.
+%Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
+%Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
+%I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
+%Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
 
@@
 
-For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.
+%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.
 
-\subsubsection{Direct Connection}
+\subsubsection{One-side Buffer}
 
@@
 	\centering
-%	\includegraphics[width=8cm]{direct}
-	\caption{direct access}
-	\label{direct access}
+	\includegraphics[width=7cm]{read_and_write}
+	\caption{read and write operation}
+	\label{read and write}
 \end{figure}
 
-As Fig.~\ref{direct access} shows, direct connection is a connection between I/O buffer nodes in cloud 2 and storage cloud 2 directly, only one side I/O buffer nodes are used in this model.
+As Fig.~\ref{read and write} shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
 When computing nodes issue a read request, data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
@@
 
-\subsubsection{I/O Bursting Buffer}
+\subsubsection{Two-side Buffer}
+
+\subsubsection{Buffer Queue Write Back}
 
@@
 	\centering
-	\includegraphics[width=8cm]{reading}
-	\caption{data reading operation}
-	\label{reading}
+	\includegraphics[width=7cm]{buffer_queue}
+	\caption{buffer queue}
+	\label{buffer queue}
 \end{figure}
 
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=8cm]{writing}
-	\caption{data writing operation}
-	\label{writing}
-\end{figure}
+in this subsection, we introduce operation of buffer queue
 
-I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
+%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
 
-When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
+%When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
 
-After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
+%After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
 %here a sub-index is used to refer to each piece's position, 
-then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
+%then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
 
-When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
+%When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
 
-Data writing operation doing the opposite operation as reading operation.
+%Data writing operation doing the opposite operation as reading operation.
+%When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
+%After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.
 
-When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
-After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.
-
-I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position.
+%I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position.
 and then start to transfer data concurrently.
 
-Then I/O buffer nodes write data to storage in cloud 1.
+%Then I/O buffer nodes write data to storage in cloud 1.
 
+\begin{comment}
 \subsubsection{Index Protocol}
@@
 There are two phases of data splitting in both reading and writing operation, 
+\end{comment}
+%\subsubsection{Node Migration}
+%Node migration happens when some nodes have to be shutted down due to some situation like power problem in summer, and still need to provide service to users.
+%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
 
-\subsubsection{Node Migration}
-Node migration happens when some nodes have to be shutted down due to some situation like power problem in summer, and still need to provide service to users.
-In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
-
-However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
-When using I/O buffer nodes
+%However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
+%When using I/O buffer nodes
 
@@
 Throughput-based Model and Cost-based Model will be described in this section.
-All definitions used are described in Fig.~\ref{overview}:
+We make following definitions in order to describe our model:
 
@@
 	\item Numbers of computing nodes are $c_1,c_2$, and numbers of I/O buffer nodes are $n_1, n_2$ respectively.
-	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in cloud 1 connect to storage in cloud 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each cloud have Internet connection.
+	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in sytem 1 connect to storage in system 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each system have Internet connection.
 	\item Since overall Internet throughput is affected by number of nodes involved in connection. $I(n_1,n_2)$ is used to refer to Internet throughput using $n_1,n_2$ I/O buffer nodes respectively.
-	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in cloud 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in cloud 2 with $n_2$ I/O nodes.
-	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in cloud 1 and ,storage and $n_2$ I/O nodes in cloud 2.
-	\item Cost for standard node in cloud 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in cloud 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.
-
+	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
+	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in system 1 and ,storage and $n_2$ I/O nodes in system 2.
+	\item Cost for standard node in system 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.
+	\item Available 
 \end{itemize}
@@
 
-\subsection{Migration Model}
-Since there are some condition that some supercomputer nodes must be shutted down, and jobs running on these nodes have to be migrate to another cloud. There are 
-\begin{equation}
-	Data	
-\end{equation}
+%\subsection{}
+%\subsection{Migration Model}
+%Since there are some condition that some supercomputer nodes must be shutted down, and jobs running on these nodes have to be migrate to another cloud. There are 
+%\begin{equation}
+%	Data	
+%\end{equation}
 

### 2014-06-24 paper/paper.tex
0624

@@
 \usepackage{verbatim}
+
+\bibliographystyle{ipsjunsrt-e.bst}
 
@@
 One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
-Although cloud bursting is used by several companies and already have some sophisticated solution, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to ferderate a supercomputer with a public cloud.
+Although cloud bursting is used by several companies and already have some sophisticated solutions\cite{Eucalyptus,stratos,Seagull}, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to ferderate a supercomputer with a public cloud, and there are several studies on .
 The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user.
@@
 In order to increase data transfer throughput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
-This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
-Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
-Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, this model evaluate total cost with and without I/O nodes.
+%This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
+%Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
+Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.
 
@@
 	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
+	\includegraphics[width=6cm]{point_to_point_lab}
 	%\includegraphics{}
@@
 	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
+	\includegraphics[width=6cm]{point_to_point_AMAZON}
 	%\includegraphics{}
@@
 	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
+	\includegraphics[width=6cm]{point_to_point_lab}
 	\caption{point to point connection throughput between AMAZON and our lab}
@@
 As we know, throughput gap between innerconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in [].
-On the other hand, Fig.~\ref{throughput AMAZON to MATSULAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access, since TSUBAME Lustre can not be mountted outside of TSUBAME because of security problem, we use a file system inside our lab instead of TSUBAME Lustre file system, we can see that the I/O throughput also grows as number of nodes grows but the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
+We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
+
+Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
+On the other hand, Fig.~\ref{throughput AMAZON to MATSULAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
+Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
+We can see that the I/O throughput also grows as number of nodes grows but the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
 %From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
 %Also, if we compare the one nodes I/O throughput, 
-If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy, longer execution time means more cost.
+If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.
 
 %But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput 
-However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, and it shows a strong scalability.
+However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linar line also a strong scalability.
 Since we can achieve a high innerconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
+
+Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with innerconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are settled in the same system.
 
@@
 Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
-Since data transfer rate is extremely low in Internet compared to innerconnection network, user do not want to ,in this model, we just consider the situation that all nodes used for the same job are settled in the same system.
 %Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
@@
 	\centering
-	\includegraphics[width=7cm]{IOserver}
+	\includegraphics[width=6cm]{IOserver}
 	\caption{I/O server and buffer queue}
@@
 	\centering
-	\includegraphics[width=7cm]{overview}
+	\includegraphics[width=6cm]{overview}
 	\caption{overall illustrate of I/O Burst Buffer Architecture}
@@
 Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture:
+
 Consider there are two systems, named system 1 and system 2, and we assume that 
@@
 %For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation. 
-
-\subsubsection{One-side Buffer}
+\subsection{Buffer Queue Write Back}
 
@@
 	\centering
-	\includegraphics[width=7cm]{read_and_write}
-	\caption{read and write operation}
-	\label{read and write}
-\end{figure}
-
-As Fig.~\ref{read and write} shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
-When computing nodes issue a read request, data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
-After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.
-
-Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
-After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
-When I/O buffer nodes received data, then they writing data back to storage in cloud 1.
-
-\subsubsection{Two-side Buffer}
-
-\subsubsection{Buffer Queue Write Back}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{buffer_queue}
+	\includegraphics[width=6cm]{buffer_queue}
 	\caption{buffer queue}
@@
 in this subsection, we introduce operation of buffer queue
+
+\subsection{Read and Write}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=6cm]{read_and_write}
+	\caption{read and write operation}
+	\label{read and write}
+\end{figure}
+
+In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
+We propose two kindes of model: one-side buffer and two-side buffer.
+
+\subsubsection{One-side Buffer}
+
+As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
+When I/O nodes need to write data back to storage in system 1, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.
+
+%data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
+%After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.
+
+%Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
+%After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
+%When I/O buffer nodes received data, then they writing data back to storage in cloud 1.
+
+\subsubsection{Two-side Buffer}
 
@@
 
+\bibliography{reference}
 \end{document}

### 2014-06-26 paper/paper.tex
0625

@@
 \usepackage{verbatim}
-
+\usepackage{supertabular}
 \bibliographystyle{ipsjunsrt-e.bst}
@@
 %supercomputers usually consist of a large number of nodes, provide high parallelism for multi-user.
-%However computing nodes in supercomputers will not meet the request in some situation, such as some nodes have to be shutted down to reduce electric consumption in summer or just several serial applications occupy nodes making others must wait.
+%However computing nodes in supercomputers will not meet the request in some situation, such as some nodes have to be shut down to reduce electric consumption in summer or just several serial applications occupy nodes making others must wait.
 %large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
 %One solution is running virtual machine on 
-%In this paper, a comparision was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
+%In this paper, a comparison was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
 %In order to satisfy these temporary request peak, we are trying to federate supercomputers with public cloud, which is known as cloud bursting.
@@
 %Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until perious job finished although there are 49 nodes remainning available.
+Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
 %high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
-Another problem is the power problem in summer, in order to reduce power comsumation, some nodes will be forced to be shutted down, reducing numbers of nodes will make the first problem more serous.
+Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down, reducing numbers of nodes will make the first problem more serous.
 
 One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
-Although cloud bursting is used by several companies and already have some sophisticated solutions\cite{Eucalyptus,stratos,Seagull}, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to ferderate a supercomputer with a public cloud, and there are several studies on .
+Although cloud bursting is used by several companies and already have some sophisticated solutions\cite{Eucalyptus,stratos,Seagull}, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to federate a supercomputer with a public cloud, and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
 The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user.
@@
 
-In order to increase data transfer throughput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
+In order to increase data transfer throughput, we propose a I/O burst buffer architecture that uses several nodes in each system as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O burst buffer model that uses to switch between I/O burst buffer mode and direct connect mode.
 %This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
@@
 \begin{itemize}
-	\item An architecture of I/O bursting buffer for increasing data transfer throughput between two clouds.
-	\item A throughput-based I/O bursting buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two clouds, and a cost-based I/O bursting buffer model uses to reduce the total cost.
+	\item An architecture of I/O burst buffer for increasing data transfer throughput between two systems.
+	\item A throughput-based I/O burst buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two systems, a cost-based I/O burst buffer model uses to reduce the total cost and a queue model used.
 	%\item 
-	\item Evaluating I/O bursting buffer architecture and two models by using data obtained from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
+	\item Evaluating I/O burst buffer architecture and two models by using data obtained from several benchmarks from TSUBAME supercomputer and AMAZON EC2 public cloud.
 \end{itemize}
 %2
-The remainder of this paper is orginized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
+The remainder of this paper is organized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
 will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
@@
 %For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
-%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.
+%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shut down to reduce electricity consumption in the case of TSUBAME Supercomputer.
 %Facing these problems, one solution will be federate supercomputer with public cloud.
@@
 	\centering
-	\includegraphics[width=6cm]{point_to_point_lab}
-	%\includegraphics{}
+	\includegraphics[width=6cm]{throughput_tsubame}
 	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
@@
 	\centering
-	\includegraphics[width=6cm]{point_to_point_lab}
-	%\includegraphics{}
+	\includegraphics[width=6cm]{AMAZON_to_OUR_LAB}
 	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
-	\label{throughput AMAZON to MATSULAB}
+	\label{throughput AMAZON to OURLAB}
 \end{figure}
@@
 	\includegraphics[width=6cm]{point_to_point_AMAZON}
-	%\includegraphics{}
 	\caption{point to point connection inside AMAZON}
@@
 
-As we know, throughput gap between innerconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
+As we know, throughput gap between interconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
 We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
 
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
-On the other hand, Fig.~\ref{throughput AMAZON to MATSULAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
+Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
+On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
 Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
-We can see that the I/O throughput also grows as number of nodes grows but the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
-%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
+We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
+%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of interconnection inside supercomputer is quit larger than that from AMAZON.
 %Also, if we compare the one nodes I/O throughput, 
+Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput 
 If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.
 
-%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput 
-However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linar line also a strong scalability.
-Since we can achieve a high innerconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
+%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the interconnection throughput 
+However, if we consider interconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
+Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
 
-Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with innerconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are settled in the same system.
+Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with interconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are allocated in the same system.
 
@@
 As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be tranferred to final storage system.
+The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system.
 %the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
@@
 
-%Migration operation occurs when some nodes have to be shutted down in one cloud 
+%Migration operation occurs when some nodes have to be shut down in one cloud 
 %all jobs running on these nodes have to be backed up by using snapshot,
@@
 %Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
-There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assgined only  and I/O burst buffer nodes, which assigned both private IP address.
+There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assigned only  and I/O burst buffer nodes, which assigned both private IP address.
 
@@
 When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
-First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are settled in the same system, so data consistency can be guaranteed since that.
-Buffer queue operation includeing data write back and operation when queue is full will be described in following section.
+First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are allocated in the same system, so data consistency can be guaranteed since that.
+Buffer queue operation including data write back and operation when queue is full will be described in following section.
 
-When user issue a read request, there are two conditions: file is bufferred in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
+When user issue a read request, there are two conditions: file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
 In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
@@
 
-Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture:
+Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture.
 
-Consider there are two systems, named system 1 and system 2, and we assume that 
+%Consider there are two systems, named system 1 and system 2
+
 %Arrows stand for network connection.
-%Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
+%Orange arrows are interconnection networks inside cloud, although two clouds used the same color for interconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
 %Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
@@
 %For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.
-\subsection{Buffer Queue Write Back}
 
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{buffer_queue}
-	\caption{buffer queue}
-	\label{buffer queue}
-\end{figure}
-
-in this subsection, we introduce operation of buffer queue
+%in this subsection, we introduce operations of buffer queue write back.
 
@@
 In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
-We propose two kindes of model: one-side buffer and two-side buffer.
+We propose two kinds of model: one-side buffer and two-side buffer.
 
@@
 As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
-When I/O nodes need to write data back to storage in system 1, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.
+When I/O nodes need to write data back to storage in another system, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.
 
+Similarly, when I/O nodes need to read data from storage in another system, several I/O nodes will be assigned equal size of data, and then these nodes read assigned piece of data from the storage concurrently.
+
+There will be two problems in this solution:
+\begin{itemize}
+	\item First storage should be opened to Internet, in order that I/O nodes can read from or write to it.
+		However storage system in supercomputer store Petabyte of research data, open the access of storage system means that put these research data under risk of attack.
+	\item As we mentioned before, throughput of one side communication is lower than two side communication, since we use SSH protocol based File system for security reason.
+		also two side communication can achieve a higher throughput with fewer nodes, according to pay-as-you-go policy, reduce number of nodes can reduce cost.
+\end{itemize}
 %data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
@@
 \subsubsection{Two-side Buffer}
+
+On the contrary, two-side buffer solution use I/O buffer nodes in both two systems as Fig.~\ref{read and write} orange arrows show.
+I/O data will be split twice, transferred throughput two sides of I/O buffer nodes and then reached the destination.
+
+Consider I/O nodes in system 2 issue a write back operation, also, data is already spread among I/O nodes in system 2, each I/O node will find a pair among I/O nodes in system 1, then transfer their piece of data to system 1 concurrently.
+After I/O node in system 1 received data, they write data back to storage in system 1.
+
+Compared with one-side buffer, two-side buffer required one more data transfer (I/O nodes to storage in the same system), if storage data transfer throuhput become a bottleneck, two-side buffer will cost more time than one-side buffer.
+Also, two-side buffer require both systems allocate I/O buffer nodes, if node usage is charge in both system, total cost may be larger than one-side buffer.
+
+%the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
+Since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
+Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.
 
@@
 %\subsubsection{Node Migration}
-%Node migration happens when some nodes have to be shutted down due to some situation like power problem in summer, and still need to provide service to users.
+%Node migration happens when some nodes have to be shut down due to some situation like power problem in summer, and still need to provide service to users.
 %In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
@@
 
-\section{I/O Bursting Buffer Model}
+\section{I/O Burst Buffer Model}
 
@@
 
-Throughput-based Model and Cost-based Model will be described in this section.
-We make following definitions in order to describe our model:
-
-\begin{itemize}
-	\item Numbers of computing nodes are $c_1,c_2$, and numbers of I/O buffer nodes are $n_1, n_2$ respectively.
-	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in sytem 1 connect to storage in system 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each system have Internet connection.
-	\item Since overall Internet throughput is affected by number of nodes involved in connection. $I(n_1,n_2)$ is used to refer to Internet throughput using $n_1,n_2$ I/O buffer nodes respectively.
-	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
-	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in system 1 and ,storage and $n_2$ I/O nodes in system 2.
-	\item Cost for standard node in system 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.
-	\item Available 
-\end{itemize}
+Throughput-based Model, Cost-based Model and buffer queue write back model will be described in this section.
+Throughput-based Model compare one-side buffer throughput with two-side buffer, cost-based model compare one-side buffer cost with two-side buffer, and buffer queue write back model. 
+We make definitions shows in Table.~\ref{definition} in order to describe our model:
+\begin{table}[tb]
+	\caption{Definition of parameters}
+	\label{definition}
+\begin{tabular}{|p{3cm}|p{5cm}|}
+	\hline
+	$c_1,c_2$&Numbers of computing nodes in system 1 and system 2\\\hline
+	$n_1, n_2$&Numbers of I/O buffer nodes in system 1 and system 2.\\\hline
+	$m_1,m_2$&Available memory size for each I/O node in system 1 and 2, also the maximum buffer size will be $n_1\times m_1$ and $n_2\times m_2$\\\hline
+	$D_1(n_2),D_2(n_2)$&Throughput when $n_2$($n_1$) I/O nodes in system 1 (system 2) connect to storage in the other system directly, here we assume only I/O nodes in each system have Internet connection.\\\hline
+	$I(n_1,n_2)$& 	Internet throughput using $n_1,n_2$ I/O buffer nodes respectively, Since overall Internet throughput is affected by number of nodes involved in connection.\\\hline
+	$E_1(n_1), E_2(n_2)$&Interconnection network throughput in system 1 and 2, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes.\\\hline
+	%, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
+	$M_1(n_1),M_2(n_2)$& Throughput of connection between storage and $n_1$ I/O nodes in system 1 and storage and $n_2$ I/O nodes in system 2.\\\hline
+	$C_1\_Money(T)$,$C_2\_Money(T)$& Cost for standard node in system 1 and 2 for $T$ time usage\\\hline
+	%and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, 
+	$C_1\_High\_Money(T)$,$C_2\_High\_Money(T)$& cost I/O nodes in system 1 and 2 for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
+\end{tabular}
+\end{table}
 
@@
 %There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
-When I/O buffer nodes in cloud 2 connect to storage in cloud 1, there are two data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to storage in cloud 1, so throughput will be:
+In the case of one-side buffer, there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
+\begin{equation}
+	\text{throughput}_{\text{one-side}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
+\end{equation}
+
+In the case of two-side buffer, there are three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, throughput will be:
 
 \begin{equation}
-	\text{throughput}_{\text{direct}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
+	\text{throughput}_{\text{two-side}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
 \end{equation}
 
-In the case of using I/O buffer nodes in both cloud, there are three data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to I/O buffer nodes in cloud 1, I/O buffer nodes in cloud 1 to storage in cloud 1, throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{I/O buffer}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
-\end{equation}
-
-In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:
+In this throughput-based model, these two throughputs are evaluated, and a switch is based on these two values:
 
@@
 	\begin{cases}
-		\text{throughput}_{\text{direct}} \geq \text{throughput}_{\text{I/O buffer}} & \text{use direct connection}\\
-		\text{throughput}_{\text{direct}} < \text{throughput}_{\text{I/O buffer}} & \text{use I/O buffer}
+		\text{throughput}_{\text{one-side}} \geq \text{throughput}_{\text{two-side}} & \text{use one-side}\\
+		\text{throughput}_{\text{one-side}} < \text{throughput}_{\text{two-side}} & \text{use two-side}
 	\end{cases}
@@
 	\begin{cases}
-		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{direct connection}\\
-		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{I/O buffer}
+		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{one-side}\\
+		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{two-side}
 	\end{cases}
@@
 \begin{equation}
-	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
+	\text{cost}_\text{one-side}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
 \end{equation}
 \begin{align}
-	\text{cost}_\text{I/O buffer}&=c_2\times C_2\_Money(T_2)\\\nonumber 
+	\text{cost}_\text{two-side}&=c_2\times C_2\_Money(T_2)\\\nonumber 
 				     &+n_1\times C_1\_High\_Money(T_2)\\ \nonumber
@@
 
+In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:
+
+\begin{equation}
+	\begin{cases}
+		\text{cost}_{\text{one-side}} \geq \text{cost}_{\text{two-side}} & \text{use one-side}\\
+		\text{cost}_{\text{one-side}} < \text{cost}_{\text{two-side}} & \text{use two-side}
+	\end{cases}
+\end{equation}
+
 %\subsection{}
 %\subsection{Migration Model}
-%Since there are some condition that some supercomputer nodes must be shutted down, and jobs running on these nodes have to be migrate to another cloud. There are 
+%Since there are some condition that some supercomputer nodes must be shut down, and jobs running on these nodes have to be migrate to another cloud. There are 
 %\begin{equation}
@@
 %\end{equation}
+\subsection{Buffer Queue Write Back Model}
+
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=6cm]{buffer_queue}
+	\caption{buffer queue}
+	\label{buffer queue}
+\end{figure}
+
+If the buffer size is unlimited. then we can buffer all data in the I/O buffer nodes, and achieve a high throughput in cloud burst.
+However buffer size can not be unlimited, we can not buffer all data in the I/O buffer nodes, data in buffer nodes have to be write back to storage in another system.
+The problem is which data should be written back to storage, like cache in cpu, if we can reduce cache miss in this situation, we can increase throughput. 
+According to data locality, we use a priority queue to determine which data should be write back.
+
+Consider Fig.~\ref{buffer queue}, assume average incoming throughput is A MB/s and average outgoing throughput is B MB/s, if A always larger than B, after $T$ time buffer queue will full.
+\[T=\frac{m_2\times n_2}{A-B}\]
+
+After that, since buffer queue is full, I/O server can not send more data to I/O buffer nodes, have to block any read and write request since that.
+In this case, jobs running on public cloud have to be moved back to original system until buffer queue is empty.
 
 \section{Evaluation}
+
 \begin{figure}[tb]
 	\centering
-	%\includegraphics[width=8cm]{ThroughputAMAZONTSUBAME}
-	\caption{Throughput between AMAZON and TSUBAME}
-	\label{Throughput between AMAZON and TSUBAME}
+	%\includegraphics[width=6cm]{}
+	\caption{throughput comparison with and without I/O burst buffer}
+	\label{throughput}
 \end{figure}
 
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2.
+\begin{figure}[tb]
+	\centering
+	%\includegraphics[width=6cm]{}
+	\caption{cost comparison with and without I/O burst buffer}
+	\label{cost}
+\end{figure}
 
-\section{Conclusion and Related Work}
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=6cm]{compress_rate}
+	\caption{compress rate}
+	\label{compress rate}
+\end{figure}
 
+\begin{figure}[tb]
+	\centering
+	\includegraphics[width=6cm]{compress_time}
+	\caption{compress time on TSUBAME V queue and AMAZON EC2}
+	\label{compress time}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	%\includegraphics[width=6cm]{}
+	\caption{throughput comparison with and without compress}
+	\label{compress}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	%\includegraphics
+	\caption{cache hit and miss throughput comparison}
+	\label{cache hit}
+\end{figure}
+
+%\begin{figure}[tb]
+%	\centering
+%	\includegraphics[width=6cm]{tsubamelustre}
+%	\caption{TSUBAME Lustre workload}
+%	\label{Lustre workload}
+%\end{figure}
+
+In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region, using
+%m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
+m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}.
+Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{point to point connection LAB} ).
+%According to these data and definition described above, we use values defined below.
+
+%\begin{center}
+%\begin{tabular}[tb]{|c|c|}\hline
+%	$D_2$&$E_1$\\\hline
+%	8TB/s&1.08Gbit/s(135MB/s)\\\hline
+
+%\end{tabular}
+%\end{center}
+For throughput between two systems and inside system, from benchmark data, it shows it is hard to achieve a high throughput with only one nodes, and also there is a limit on maximum throughput between two systems and inside system.
+Although incresing nodes can increse throughput before reach the maximum, throughput achieved by each nodes decrease because of conflict.
+For these reason, we use following formular for throughput between two systems and inside system.
+%TSUBAME and AMAZON EC2, we use similar model in \cite{ccgrid}:
+\begin{equation}
+throughput=-Ax^2+Bx+C~~ A,B>0\\
+\end{equation}
+we use following equations to determine $A,B,C$
+\begin{equation}
+\begin{cases}
+	-A+B+C=throughput_{one}\\\nonumber
+	\frac{B}{2A}=n_{max}\\\nonumber
+	-An_{max}^2+Bn_{max}+C=throughput_{max}\\
+\end{cases}
+\end{equation}
+
+First, we compare throughput with and without I/O buffer nodes.
+Since it is hard for one node to fully utilize Internet and Ethernet bandwidth, according to Fig.~\ref{throughput AMAZON to OURLAB}, we assume that one node can achieve half of maximum bandwidth.
+We can see from Fig.~\ref{throughput}, when interconnection throughput is larger than Internet throughput, our I/O buffer can achieve a higher throughput.
+
+Then, we compare overall cost by using I/O burst buffer,
+
+we compare throughput with and without compression, Fig.~\ref{compress rate} shows compress and Fig.~\ref{compress time} shows compress and decompress time on TSUBAME V queue and AMAZON EC2 with a different compress level by using zlib\cite{zlib}.
+We can achieve a high compress rate, but the throughput is low, up to 160MB/s, depends on compress level, it is hard to find a compress library can compress data faster and smaller, so the compress throughput may become a bottleneck.
+On the other hand, the compress rate is high, since the buffer size is limited, if we can make data smaller, it means we can increase the buffer hit rate, Fig.~\ref{cache hit} shows a throughput comparison between cache miss and hit.
+
+Fig.~\ref{compress}
+\section{Conclusion and Future Work}
+
+In this paper, we propose a I/O burst buffer architecture to burst I/O throughput, provide throughput-based, cost-based and queue write back model, and provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
+we use several nodes in each system as a I/O buffer nodes, and use data buffering to hide the low throughput between two systems connected by Internet.
+
+From simulation result, we showed that our I/O burst buffer can increase I/O throughput when Internet throughput is far smaller than interconnection throughput as well as reducing the overall cost.
+
+For future work, we plan to implement this I/O burst buffer architecture.
 \bibliography{reference}

### 2014-06-27 paper/section/abstract.tex
section

--- 2014-06-23 paper/paper.tex
@@
-\documentclass[JIP,draft]{ipsj}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{verbatim}
-
-\begin{document}
-\title{Towards Cloud Bursting for Extreme Scale Supercomputers}
-
 \begin{abstract}
@@
 \maketitle
-
-%1
-\section{Introduction}
-An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
-%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
-
-%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until perious job finished although there are 49 nodes remainning available.
-%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
-Another problem is the power problem in summer, in order to reduce power comsumation, some nodes will be forced to be shutted down, reducing numbers of nodes will make the first problem more serous.
-
-One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
-Although cloud bursting is used by several companies and already have some sophisticated solution, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to ferderate a supercomputer with a public cloud.
-The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user.
-This paper focuses on methodology of increasing throughput when we do federation.
-
-In order to increase data transfer throughput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
-This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
-Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
-Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, this model evaluate total cost with and without I/O nodes.
-
-Our contribution can be summary as following:
-\begin{itemize}
-	\item An architecture of I/O bursting buffer for increasing data transfer throughput between two clouds.
-	\item A throughput-based I/O bursting buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two clouds, and a cost-based I/O bursting buffer model uses to reduce the total cost.
-	%\item 
-	\item Evaluating I/O bursting buffer architecture and two models by using data obtained from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
-\end{itemize}
-%2
-The remainder of this paper is orginized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
-will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
-
-\section{Motivation and Background}
-
-%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
-%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
-%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
-%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
-%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
-%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
-%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
-%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.
-%Facing these problems, one solution will be federate supercomputer with public cloud.
-%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
-
-%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
-	\label{throughput TSUBAME}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
-	\label{throughput AMAZON to MATSULAB}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{point to point connection inside AMAZON}
-	\label{point to point connection AMAZON}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	\caption{point to point connection throughput between AMAZON and our lab}
-	\label{point to point connection LAB}
-\end{figure}
-
-As we know, throughput gap between innerconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in [].
-On the other hand, Fig.~\ref{throughput AMAZON to MATSULAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access, since TSUBAME Lustre can not be mountted outside of TSUBAME because of security problem, we use a file system inside our lab instead of TSUBAME Lustre file system, we can see that the I/O throughput also grows as number of nodes grows but the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
-%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
-%Also, if we compare the one nodes I/O throughput, 
-If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy, longer execution time means more cost.
-
-%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput 
-However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, and it shows a strong scalability.
-Since we can achieve a high innerconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
-
-%3
-\section{I/O Bursting Buffer Overview}
-
-%\begin
-
-An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
-As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be tranferred to final storage system.
-%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
-Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
-Since data transfer rate is extremely low in Internet compared to innerconnection network, user do not want to ,in this model, we just consider the situation that all nodes used for the same job are settled in the same system.
-%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
-%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.
-
-%Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage
-
-%Migration operation occurs when some nodes have to be shutted down in one cloud 
-%all jobs running on these nodes have to be backed up by using snapshot,
-
-\subsection{System Environment}
-First a general system used in following sections is defined as follow:
-
-%For security consideration and the fact that IPv4 addresses becomes rare,
-\begin{itemize}
-	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
-	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
-	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
-\end{itemize}
-
-\subsection{I/O Burst Buffer Architecture}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{IOserver}
-	\caption{I/O server and buffer queue}
-	\label{I/O server}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{overview}
-	\caption{overall illustrate of I/O Burst Buffer Architecture}
-	\label{overview}
-\end{figure}
-
-%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
-There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assgined only  and I/O burst buffer nodes, which assigned both private IP address.
-
-Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
-In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
-Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
-
-When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
-First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are settled in the same system, so data consistency can be guaranteed since that.
-Buffer queue operation includeing data write back and operation when queue is full will be described in following section.
-
-When user issue a read request, there are two conditions: file is bufferred in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
-In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
-If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.
-
-Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture:
-Consider there are two systems, named system 1 and system 2, and we assume that 
-%Arrows stand for network connection.
-%Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
-%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
-%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
-
-%Circles stand for computing nodes, which are used for standard computation.
-%Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
-%Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
-%I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-%Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
-
-%Since there is a big gap between cloud inside data transferring and accross two clouds in throughput, our goal is to fill the gap.
-
-%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.
-
-\subsubsection{One-side Buffer}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{read_and_write}
-	\caption{read and write operation}
-	\label{read and write}
-\end{figure}
-
-As Fig.~\ref{read and write} shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
-When computing nodes issue a read request, data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
-After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.
-
-Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
-After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
-When I/O buffer nodes received data, then they writing data back to storage in cloud 1.
-
-\subsubsection{Two-side Buffer}
-
-\subsubsection{Buffer Queue Write Back}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{buffer_queue}
-	\caption{buffer queue}
-	\label{buffer queue}
-\end{figure}
-
-in this subsection, we introduce operation of buffer queue
-
-%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
-
-%When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
-
-%After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
-%here a sub-index is used to refer to each piece's position, 
-%then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
-
-%When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
-
-%Data writing operation doing the opposite operation as reading operation.
-%When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
-%After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.
-
-%I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position.
-and then start to transfer data concurrently.
-
-%Then I/O buffer nodes write data to storage in cloud 1.
-
-\begin{comment}
-\subsubsection{Index Protocol}
-
-\begin{figure}[tb]
-	\centering
-%	\includegraphics
-	\caption{index protocol}
-	\label{index protocol}
-\end{figure}
-
-As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
-There are two phases of data splitting in both reading and writing operation, 
-\end{comment}
-%\subsubsection{Node Migration}
-%Node migration happens when some nodes have to be shutted down due to some situation like power problem in summer, and still need to provide service to users.
-%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
-
-%However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
-%When using I/O buffer nodes
-
-\section{I/O Bursting Buffer Model}
-
-%\begin{figure}[tb]
-%	\centering
-%	\includegraphics
-%	\caption{definition}
-%	\label{definition}
-%\end{figure}
-
-Throughput-based Model and Cost-based Model will be described in this section.
-We make following definitions in order to describe our model:
-
-\begin{itemize}
-	\item Numbers of computing nodes are $c_1,c_2$, and numbers of I/O buffer nodes are $n_1, n_2$ respectively.
-	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in sytem 1 connect to storage in system 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each system have Internet connection.
-	\item Since overall Internet throughput is affected by number of nodes involved in connection. $I(n_1,n_2)$ is used to refer to Internet throughput using $n_1,n_2$ I/O buffer nodes respectively.
-	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
-	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in system 1 and ,storage and $n_2$ I/O nodes in system 2.
-	\item Cost for standard node in system 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.
-	\item Available 
-\end{itemize}
-
-\subsection{Throughput-based Model}
-%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
-When I/O buffer nodes in cloud 2 connect to storage in cloud 1, there are two data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to storage in cloud 1, so throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{direct}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
-\end{equation}
-
-In the case of using I/O buffer nodes in both cloud, there are three data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to I/O buffer nodes in cloud 1, I/O buffer nodes in cloud 1 to storage in cloud 1, throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{I/O buffer}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
-\end{equation}
-
-In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:
-
-\begin{equation}
-	\begin{cases}
-		\text{throughput}_{\text{direct}} \geq \text{throughput}_{\text{I/O buffer}} & \text{use direct connection}\\
-		\text{throughput}_{\text{direct}} < \text{throughput}_{\text{I/O buffer}} & \text{use I/O buffer}
-	\end{cases}
-\end{equation}
-
-\subsection{Cost-based Model}
-In the case of cost-based model, we consider
-using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:
-
-\begin{equation}
-	\begin{cases}
-		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{direct connection}\\
-		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{I/O buffer}
-	\end{cases}
-\end{equation}
-
-here we compute cost by using $T_1,T_2$:
-\begin{equation}
-	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
-\end{equation}
-\begin{align}
-	\text{cost}_\text{I/O buffer}&=c_2\times C_2\_Money(T_2)\\\nonumber 
-				     &+n_1\times C_1\_High\_Money(T_2)\\ \nonumber
-				     &+n_2\times C_2\_High\_Money(T_2)
-\end{align}
-
-%\subsection{}
-%\subsection{Migration Model}
-%Since there are some condition that some supercomputer nodes must be shutted down, and jobs running on these nodes have to be migrate to another cloud. There are 
-%\begin{equation}
-%	Data	
-%\end{equation}
-
-\section{Evaluation}
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=8cm]{ThroughputAMAZONTSUBAME}
-	\caption{Throughput between AMAZON and TSUBAME}
-	\label{Throughput between AMAZON and TSUBAME}
-\end{figure}
-
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2.
-
-\section{Conclusion and Related Work}
-
-\end{document}

### 2014-06-27 paper/section/conclusion.tex
section

--- 2014-06-23 paper/paper.tex
@@
-\documentclass[JIP,draft]{ipsj}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{verbatim}
+\section{Conclusion and Future Work}
 
-\begin{document}
-\title{Towards Cloud Bursting for Extreme Scale Supercomputers}
+In this paper, we propose a I/O burst buffer architecture to burst I/O throughput, provide throughput-based, cost-based and queue write back model, and provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
+we use several nodes in each system as a I/O buffer nodes, and use data buffering to hide the low throughput between two systems connected by Internet.
 
-\begin{abstract}
-%Parallel programming are used to reduce execution time of complex problems, also fully utilizing computing resource of Supercomputers.
+From simulation result, we showed that our I/O burst buffer can increase I/O throughput when Internet throughput is far smaller than interconnection throughput as well as reducing the overall cost.
 
-%supercomputers usually consist of a large number of nodes, provide high parallelism for multi-user.
-%However computing nodes in supercomputers will not meet the request in some situation, such as some nodes have to be shutted down to reduce electric consumption in summer or just several serial applications occupy nodes making others must wait.
-%large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
-%One solution is running virtual machine on 
-%In this paper, a comparision was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
-%In order to satisfy these temporary request peak, we are trying to federate supercomputers with public cloud, which is known as cloud bursting.
-%Although some sophisticated solutions are available, still we are facing several challenges, since there are a significant performance gap between supercomputers and public cloud.
-%In this paper, we focus on I/O throughput between these two environments, we propose a I/O Bursting Buffer Model to burst I/O throughput between supercomputer and public cloud and reduce the cost for extra time usage caused by low I/O throughput.
-%we also provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
-%The result shows our model can provide a stable and high I/O throughput as well as a low cost in most cases.
-
-Extreme-scale HPC systems, which consist of a large number of compute nodes, can provide high computational capacity for multiple users.
-However, computing nodes in the systems occasionally can not meet the demand due to bursty job requests in short period times.
-In order to accommodate the bursty requests, we consider federating HPC systems with public clouds, which is known as cloud bursting.
-Although the federated systems can acquire virtually infinite computational power with cloud bursting, the QoS may not be guaranteed due to a significant performance gap between HPC systems and public clouds.
-The most critical problem is a gap in I/O performance.
-In this paper, we propose an I/O acceleration technique using distributed cloud bursting buffers.
-We also create the I/O performance model to explore the effectiveness.
-Our model-based simulations, which target the TSUBAME supercomputer for an HPC system, and AMAZON EC2 for a public cloud, show that the distributed cloud busting buffer can improve I/O throughput while reducing the cost.
-
-\end{abstract}
-
-\begin{keyword}
-Supercomputer, Cloud, I/O Bursting Buffer Model
-\end{keyword}
-
-\maketitle
-
-%1
-\section{Introduction}
-An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
-%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
-
-%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until perious job finished although there are 49 nodes remainning available.
-%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
-Another problem is the power problem in summer, in order to reduce power comsumation, some nodes will be forced to be shutted down, reducing numbers of nodes will make the first problem more serous.
-
-One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
-Although cloud bursting is used by several companies and already have some sophisticated solution, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to ferderate a supercomputer with a public cloud.
-The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user.
-This paper focuses on methodology of increasing throughput when we do federation.
-
-In order to increase data transfer throughput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
-This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
-Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
-Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, this model evaluate total cost with and without I/O nodes.
-
-Our contribution can be summary as following:
-\begin{itemize}
-	\item An architecture of I/O bursting buffer for increasing data transfer throughput between two clouds.
-	\item A throughput-based I/O bursting buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two clouds, and a cost-based I/O bursting buffer model uses to reduce the total cost.
-	%\item 
-	\item Evaluating I/O bursting buffer architecture and two models by using data obtained from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
-\end{itemize}
-%2
-The remainder of this paper is orginized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
-will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
-
-\section{Motivation and Background}
-
-%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
-%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
-%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
-%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
-%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
-%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
-%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
-%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.
-%Facing these problems, one solution will be federate supercomputer with public cloud.
-%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
-
-%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
-	\label{throughput TSUBAME}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
-	\label{throughput AMAZON to MATSULAB}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{point to point connection inside AMAZON}
-	\label{point to point connection AMAZON}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	\caption{point to point connection throughput between AMAZON and our lab}
-	\label{point to point connection LAB}
-\end{figure}
-
-As we know, throughput gap between innerconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in [].
-On the other hand, Fig.~\ref{throughput AMAZON to MATSULAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access, since TSUBAME Lustre can not be mountted outside of TSUBAME because of security problem, we use a file system inside our lab instead of TSUBAME Lustre file system, we can see that the I/O throughput also grows as number of nodes grows but the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
-%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
-%Also, if we compare the one nodes I/O throughput, 
-If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy, longer execution time means more cost.
-
-%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput 
-However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, and it shows a strong scalability.
-Since we can achieve a high innerconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
-
-%3
-\section{I/O Bursting Buffer Overview}
-
-%\begin
-
-An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
-As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be tranferred to final storage system.
-%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
-Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
-Since data transfer rate is extremely low in Internet compared to innerconnection network, user do not want to ,in this model, we just consider the situation that all nodes used for the same job are settled in the same system.
-%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
-%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.
-
-%Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage
-
-%Migration operation occurs when some nodes have to be shutted down in one cloud 
-%all jobs running on these nodes have to be backed up by using snapshot,
-
-\subsection{System Environment}
-First a general system used in following sections is defined as follow:
-
-%For security consideration and the fact that IPv4 addresses becomes rare,
-\begin{itemize}
-	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
-	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
-	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
-\end{itemize}
-
-\subsection{I/O Burst Buffer Architecture}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{IOserver}
-	\caption{I/O server and buffer queue}
-	\label{I/O server}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{overview}
-	\caption{overall illustrate of I/O Burst Buffer Architecture}
-	\label{overview}
-\end{figure}
-
-%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
-There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assgined only  and I/O burst buffer nodes, which assigned both private IP address.
-
-Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
-In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
-Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
-
-When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
-First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are settled in the same system, so data consistency can be guaranteed since that.
-Buffer queue operation includeing data write back and operation when queue is full will be described in following section.
-
-When user issue a read request, there are two conditions: file is bufferred in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
-In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
-If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.
-
-Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture:
-Consider there are two systems, named system 1 and system 2, and we assume that 
-%Arrows stand for network connection.
-%Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
-%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
-%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
-
-%Circles stand for computing nodes, which are used for standard computation.
-%Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
-%Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
-%I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-%Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
-
-%Since there is a big gap between cloud inside data transferring and accross two clouds in throughput, our goal is to fill the gap.
-
-%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.
-
-\subsubsection{One-side Buffer}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{read_and_write}
-	\caption{read and write operation}
-	\label{read and write}
-\end{figure}
-
-As Fig.~\ref{read and write} shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
-When computing nodes issue a read request, data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
-After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.
-
-Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
-After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
-When I/O buffer nodes received data, then they writing data back to storage in cloud 1.
-
-\subsubsection{Two-side Buffer}
-
-\subsubsection{Buffer Queue Write Back}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{buffer_queue}
-	\caption{buffer queue}
-	\label{buffer queue}
-\end{figure}
-
-in this subsection, we introduce operation of buffer queue
-
-%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
-
-%When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
-
-%After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
-%here a sub-index is used to refer to each piece's position, 
-%then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
-
-%When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
-
-%Data writing operation doing the opposite operation as reading operation.
-%When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
-%After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.
-
-%I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position.
-and then start to transfer data concurrently.
-
-%Then I/O buffer nodes write data to storage in cloud 1.
-
-\begin{comment}
-\subsubsection{Index Protocol}
-
-\begin{figure}[tb]
-	\centering
-%	\includegraphics
-	\caption{index protocol}
-	\label{index protocol}
-\end{figure}
-
-As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
-There are two phases of data splitting in both reading and writing operation, 
-\end{comment}
-%\subsubsection{Node Migration}
-%Node migration happens when some nodes have to be shutted down due to some situation like power problem in summer, and still need to provide service to users.
-%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
-
-%However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
-%When using I/O buffer nodes
-
-\section{I/O Bursting Buffer Model}
-
-%\begin{figure}[tb]
-%	\centering
-%	\includegraphics
-%	\caption{definition}
-%	\label{definition}
-%\end{figure}
-
-Throughput-based Model and Cost-based Model will be described in this section.
-We make following definitions in order to describe our model:
-
-\begin{itemize}
-	\item Numbers of computing nodes are $c_1,c_2$, and numbers of I/O buffer nodes are $n_1, n_2$ respectively.
-	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in sytem 1 connect to storage in system 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each system have Internet connection.
-	\item Since overall Internet throughput is affected by number of nodes involved in connection. $I(n_1,n_2)$ is used to refer to Internet throughput using $n_1,n_2$ I/O buffer nodes respectively.
-	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
-	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in system 1 and ,storage and $n_2$ I/O nodes in system 2.
-	\item Cost for standard node in system 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.
-	\item Available 
-\end{itemize}
-
-\subsection{Throughput-based Model}
-%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
-When I/O buffer nodes in cloud 2 connect to storage in cloud 1, there are two data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to storage in cloud 1, so throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{direct}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
-\end{equation}
-
-In the case of using I/O buffer nodes in both cloud, there are three data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to I/O buffer nodes in cloud 1, I/O buffer nodes in cloud 1 to storage in cloud 1, throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{I/O buffer}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
-\end{equation}
-
-In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:
-
-\begin{equation}
-	\begin{cases}
-		\text{throughput}_{\text{direct}} \geq \text{throughput}_{\text{I/O buffer}} & \text{use direct connection}\\
-		\text{throughput}_{\text{direct}} < \text{throughput}_{\text{I/O buffer}} & \text{use I/O buffer}
-	\end{cases}
-\end{equation}
-
-\subsection{Cost-based Model}
-In the case of cost-based model, we consider
-using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:
-
-\begin{equation}
-	\begin{cases}
-		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{direct connection}\\
-		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{I/O buffer}
-	\end{cases}
-\end{equation}
-
-here we compute cost by using $T_1,T_2$:
-\begin{equation}
-	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
-\end{equation}
-\begin{align}
-	\text{cost}_\text{I/O buffer}&=c_2\times C_2\_Money(T_2)\\\nonumber 
-				     &+n_1\times C_1\_High\_Money(T_2)\\ \nonumber
-				     &+n_2\times C_2\_High\_Money(T_2)
-\end{align}
-
-%\subsection{}
-%\subsection{Migration Model}
-%Since there are some condition that some supercomputer nodes must be shutted down, and jobs running on these nodes have to be migrate to another cloud. There are 
-%\begin{equation}
-%	Data	
-%\end{equation}
-
-\section{Evaluation}
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=8cm]{ThroughputAMAZONTSUBAME}
-	\caption{Throughput between AMAZON and TSUBAME}
-	\label{Throughput between AMAZON and TSUBAME}
-\end{figure}
-
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2.
-
-\section{Conclusion and Related Work}
-
-\end{document}
+For future work, we plan to implement this I/O burst buffer architecture.

### 2014-06-27 paper/section/evaluation.tex
section

--- 2014-06-23 paper/paper.tex
@@
-\documentclass[JIP,draft]{ipsj}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{verbatim}
+\section{Evaluation}
 
-\begin{document}
-\title{Towards Cloud Bursting for Extreme Scale Supercomputers}
-
-\begin{abstract}
-%Parallel programming are used to reduce execution time of complex problems, also fully utilizing computing resource of Supercomputers.
-
-%supercomputers usually consist of a large number of nodes, provide high parallelism for multi-user.
-%However computing nodes in supercomputers will not meet the request in some situation, such as some nodes have to be shutted down to reduce electric consumption in summer or just several serial applications occupy nodes making others must wait.
-%large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
-%One solution is running virtual machine on 
-%In this paper, a comparision was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
-%In order to satisfy these temporary request peak, we are trying to federate supercomputers with public cloud, which is known as cloud bursting.
-%Although some sophisticated solutions are available, still we are facing several challenges, since there are a significant performance gap between supercomputers and public cloud.
-%In this paper, we focus on I/O throughput between these two environments, we propose a I/O Bursting Buffer Model to burst I/O throughput between supercomputer and public cloud and reduce the cost for extra time usage caused by low I/O throughput.
-%we also provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
-%The result shows our model can provide a stable and high I/O throughput as well as a low cost in most cases.
-
-Extreme-scale HPC systems, which consist of a large number of compute nodes, can provide high computational capacity for multiple users.
-However, computing nodes in the systems occasionally can not meet the demand due to bursty job requests in short period times.
-In order to accommodate the bursty requests, we consider federating HPC systems with public clouds, which is known as cloud bursting.
-Although the federated systems can acquire virtually infinite computational power with cloud bursting, the QoS may not be guaranteed due to a significant performance gap between HPC systems and public clouds.
-The most critical problem is a gap in I/O performance.
-In this paper, we propose an I/O acceleration technique using distributed cloud bursting buffers.
-We also create the I/O performance model to explore the effectiveness.
-Our model-based simulations, which target the TSUBAME supercomputer for an HPC system, and AMAZON EC2 for a public cloud, show that the distributed cloud busting buffer can improve I/O throughput while reducing the cost.
-
-\end{abstract}
-
-\begin{keyword}
-Supercomputer, Cloud, I/O Bursting Buffer Model
-\end{keyword}
-
-\maketitle
-
-%1
-\section{Introduction}
-An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
-%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
-
-%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until perious job finished although there are 49 nodes remainning available.
-%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
-Another problem is the power problem in summer, in order to reduce power comsumation, some nodes will be forced to be shutted down, reducing numbers of nodes will make the first problem more serous.
-
-One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
-Although cloud bursting is used by several companies and already have some sophisticated solution, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to ferderate a supercomputer with a public cloud.
-The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user.
-This paper focuses on methodology of increasing throughput when we do federation.
-
-In order to increase data transfer throughput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
-This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
-Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
-Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, this model evaluate total cost with and without I/O nodes.
-
-Our contribution can be summary as following:
-\begin{itemize}
-	\item An architecture of I/O bursting buffer for increasing data transfer throughput between two clouds.
-	\item A throughput-based I/O bursting buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two clouds, and a cost-based I/O bursting buffer model uses to reduce the total cost.
-	%\item 
-	\item Evaluating I/O bursting buffer architecture and two models by using data obtained from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
-\end{itemize}
-%2
-The remainder of this paper is orginized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
-will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
-
-\section{Motivation and Background}
-
-%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
-%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
-%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
-%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
-%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
-%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
-%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
-%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.
-%Facing these problems, one solution will be federate supercomputer with public cloud.
-%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
-
-%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
 \begin{figure}[tb]
 	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
-	\label{throughput TSUBAME}
+	%\includegraphics[width=6cm]{}
+	\caption{throughput comparison with and without I/O burst buffer}
+	\label{throughput}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
-	\label{throughput AMAZON to MATSULAB}
+	%\includegraphics[width=6cm]{}
+	\caption{cost comparison with and without I/O burst buffer}
+	\label{cost}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{point to point connection inside AMAZON}
-	\label{point to point connection AMAZON}
+	\includegraphics[width=6cm]{compress_rate}
+	\caption{compress rate}
+	\label{compress rate}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=7cm]{point_to_point_lab}
-	\caption{point to point connection throughput between AMAZON and our lab}
-	\label{point to point connection LAB}
-\end{figure}
-
-As we know, throughput gap between innerconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in [].
-On the other hand, Fig.~\ref{throughput AMAZON to MATSULAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access, since TSUBAME Lustre can not be mountted outside of TSUBAME because of security problem, we use a file system inside our lab instead of TSUBAME Lustre file system, we can see that the I/O throughput also grows as number of nodes grows but the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
-%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
-%Also, if we compare the one nodes I/O throughput, 
-If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy, longer execution time means more cost.
-
-%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput 
-However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, and it shows a strong scalability.
-Since we can achieve a high innerconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
-
-%3
-\section{I/O Bursting Buffer Overview}
-
-%\begin
-
-An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
-As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be tranferred to final storage system.
-%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
-Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
-Since data transfer rate is extremely low in Internet compared to innerconnection network, user do not want to ,in this model, we just consider the situation that all nodes used for the same job are settled in the same system.
-%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
-%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.
-
-%Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage
-
-%Migration operation occurs when some nodes have to be shutted down in one cloud 
-%all jobs running on these nodes have to be backed up by using snapshot,
-
-\subsection{System Environment}
-First a general system used in following sections is defined as follow:
-
-%For security consideration and the fact that IPv4 addresses becomes rare,
-\begin{itemize}
-	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
-	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
-	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
-\end{itemize}
-
-\subsection{I/O Burst Buffer Architecture}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{IOserver}
-	\caption{I/O server and buffer queue}
-	\label{I/O server}
+	\includegraphics[width=6cm]{compress_time}
+	\caption{compress time on TSUBAME V queue and AMAZON EC2}
+	\label{compress time}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=7cm]{overview}
-	\caption{overall illustrate of I/O Burst Buffer Architecture}
-	\label{overview}
+	%\includegraphics[width=6cm]{}
+	\caption{throughput comparison with and without compress}
+	\label{compress}
 \end{figure}
-
-%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
-There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assgined only  and I/O burst buffer nodes, which assigned both private IP address.
-
-Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
-In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
-Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
-
-When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
-First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are settled in the same system, so data consistency can be guaranteed since that.
-Buffer queue operation includeing data write back and operation when queue is full will be described in following section.
-
-When user issue a read request, there are two conditions: file is bufferred in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
-In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
-If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.
-
-Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture:
-Consider there are two systems, named system 1 and system 2, and we assume that 
-%Arrows stand for network connection.
-%Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
-%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
-%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
-
-%Circles stand for computing nodes, which are used for standard computation.
-%Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
-%Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
-%I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-%Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
-
-%Since there is a big gap between cloud inside data transferring and accross two clouds in throughput, our goal is to fill the gap.
-
-%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.
-
-\subsubsection{One-side Buffer}
 
@@
 	\centering
-	\includegraphics[width=7cm]{read_and_write}
-	\caption{read and write operation}
-	\label{read and write}
+	%\includegraphics
+	\caption{cache hit and miss throughput comparison}
+	\label{cache hit}
 \end{figure}
-
-As Fig.~\ref{read and write} shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
-When computing nodes issue a read request, data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
-After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.
-
-Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
-After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
-When I/O buffer nodes received data, then they writing data back to storage in cloud 1.
-
-\subsubsection{Two-side Buffer}
-
-\subsubsection{Buffer Queue Write Back}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=7cm]{buffer_queue}
-	\caption{buffer queue}
-	\label{buffer queue}
-\end{figure}
-
-in this subsection, we introduce operation of buffer queue
-
-%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
-
-%When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
-
-%After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
-%here a sub-index is used to refer to each piece's position, 
-%then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
-
-%When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
-
-%Data writing operation doing the opposite operation as reading operation.
-%When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
-%After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.
-
-%I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position.
-and then start to transfer data concurrently.
-
-%Then I/O buffer nodes write data to storage in cloud 1.
-
-\begin{comment}
-\subsubsection{Index Protocol}
-
-\begin{figure}[tb]
-	\centering
-%	\includegraphics
-	\caption{index protocol}
-	\label{index protocol}
-\end{figure}
-
-As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
-There are two phases of data splitting in both reading and writing operation, 
-\end{comment}
-%\subsubsection{Node Migration}
-%Node migration happens when some nodes have to be shutted down due to some situation like power problem in summer, and still need to provide service to users.
-%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
-
-%However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
-%When using I/O buffer nodes
-
-\section{I/O Bursting Buffer Model}
 
@@
 %	\centering
-%	\includegraphics
-%	\caption{definition}
-%	\label{definition}
+%	\includegraphics[width=6cm]{tsubamelustre}
+%	\caption{TSUBAME Lustre workload}
+%	\label{Lustre workload}
 %\end{figure}
 
-Throughput-based Model and Cost-based Model will be described in this section.
-We make following definitions in order to describe our model:
+In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region, using
+%m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
+m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}.
+Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{point to point connection LAB} ).
+%According to these data and definition described above, we use values defined below.
 
-\begin{itemize}
-	\item Numbers of computing nodes are $c_1,c_2$, and numbers of I/O buffer nodes are $n_1, n_2$ respectively.
-	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in sytem 1 connect to storage in system 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each system have Internet connection.
-	\item Since overall Internet throughput is affected by number of nodes involved in connection. $I(n_1,n_2)$ is used to refer to Internet throughput using $n_1,n_2$ I/O buffer nodes respectively.
-	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
-	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in system 1 and ,storage and $n_2$ I/O nodes in system 2.
-	\item Cost for standard node in system 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.
-	\item Available 
-\end{itemize}
+%\begin{center}
+%\begin{tabular}[tb]{|c|c|}\hline
+%	$D_2$&$E_1$\\\hline
+%	8TB/s&1.08Gbit/s(135MB/s)\\\hline
 
-\subsection{Throughput-based Model}
-%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
-When I/O buffer nodes in cloud 2 connect to storage in cloud 1, there are two data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to storage in cloud 1, so throughput will be:
-
+%\end{tabular}
+%\end{center}
+For throughput between two systems and inside system, from benchmark data, it shows it is hard to achieve a high throughput with only one nodes, and also there is a limit on maximum throughput between two systems and inside system.
+Although incresing nodes can increse throughput before reach the maximum, throughput achieved by each nodes decrease because of conflict.
+For these reason, we use following formular for throughput between two systems and inside system.
+%TSUBAME and AMAZON EC2, we use similar model in \cite{ccgrid}:
 \begin{equation}
-	\text{throughput}_{\text{direct}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
+throughput=-Ax^2+Bx+C~~ A,B>0\\
 \end{equation}
-
-In the case of using I/O buffer nodes in both cloud, there are three data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to I/O buffer nodes in cloud 1, I/O buffer nodes in cloud 1 to storage in cloud 1, throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{I/O buffer}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
-\end{equation}
-
-In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:
-
+we use following equations to determine $A,B,C$
 \begin{equation}
 \begin{cases}
-		\text{throughput}_{\text{direct}} \geq \text{throughput}_{\text{I/O buffer}} & \text{use direct connection}\\
-		\text{throughput}_{\text{direct}} < \text{throughput}_{\text{I/O buffer}} & \text{use I/O buffer}
+	-A+B+C=throughput_{one}\\\nonumber
+	\frac{B}{2A}=n_{max}\\\nonumber
+	-An_{max}^2+Bn_{max}+C=throughput_{max}\\
 \end{cases}
@@
 
-\subsection{Cost-based Model}
-In the case of cost-based model, we consider
-using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:
+First, we compare throughput with and without I/O buffer nodes.
+Since it is hard for one node to fully utilize Internet and Ethernet bandwidth, according to Fig.~\ref{throughput AMAZON to OURLAB}, we assume that one node can achieve half of maximum bandwidth.
+We can see from Fig.~\ref{throughput}, when interconnection throughput is larger than Internet throughput, our I/O buffer can achieve a higher throughput.
 
-\begin{equation}
-	\begin{cases}
-		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{direct connection}\\
-		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{I/O buffer}
-	\end{cases}
-\end{equation}
+Then, we compare overall cost by using I/O burst buffer,
 
-here we compute cost by using $T_1,T_2$:
-\begin{equation}
-	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
-\end{equation}
-\begin{align}
-	\text{cost}_\text{I/O buffer}&=c_2\times C_2\_Money(T_2)\\\nonumber 
-				     &+n_1\times C_1\_High\_Money(T_2)\\ \nonumber
-				     &+n_2\times C_2\_High\_Money(T_2)
-\end{align}
+we compare throughput with and without compression, Fig.~\ref{compress rate} shows compress and Fig.~\ref{compress time} shows compress and decompress time on TSUBAME V queue and AMAZON EC2 with a different compress level by using zlib\cite{zlib}.
+We can achieve a high compress rate, but the throughput is low, up to 160MB/s, depends on compress level, it is hard to find a compress library can compress data faster and smaller, so the compress throughput may become a bottleneck.
+On the other hand, the compress rate is high, since the buffer size is limited, if we can make data smaller, it means we can increase the buffer hit rate, Fig.~\ref{cache hit} shows a throughput comparison between cache miss and hit.
 
-%\subsection{}
-%\subsection{Migration Model}
-%Since there are some condition that some supercomputer nodes must be shutted down, and jobs running on these nodes have to be migrate to another cloud. There are 
-%\begin{equation}
-%	Data	
-%\end{equation}
-
-\section{Evaluation}
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=8cm]{ThroughputAMAZONTSUBAME}
-	\caption{Throughput between AMAZON and TSUBAME}
-	\label{Throughput between AMAZON and TSUBAME}
-\end{figure}
-
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2.
-
-\section{Conclusion and Related Work}
-
-\end{document}
+Fig.~\ref{compress}

### 2014-06-27 paper/section/introduction.tex
section

--- 2014-06-24 paper/paper.tex
@@
-\documentclass[JIP,draft]{ipsj}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{verbatim}
-
-\bibliographystyle{ipsjunsrt-e.bst}
-
-\begin{document}
-\title{Towards Cloud Bursting for Extreme Scale Supercomputers}
-
 \begin{abstract}
@@
 \begin{itemize}
-	\item An architecture of I/O bursting buffer for increasing data transfer throughput between two clouds.
-	\item A throughput-based I/O bursting buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two clouds, and a cost-based I/O bursting buffer model uses to reduce the total cost.
+	\item An architecture of I/O burst buffer for increasing data transfer throughput between two systems.
+	\item A throughput-based I/O burst buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two systems, a cost-based I/O burst buffer model uses to reduce the total cost and a queue model used.
 	%\item 
-	\item Evaluating I/O bursting buffer architecture and two models by using data obtained from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
+	\item Evaluating I/O burst buffer architecture and two models by using data obtained from several benchmarks from TSUBAME supercomputer and AMAZON EC2 public cloud.
 \end{itemize}
 %2
-The remainder of this paper is orginized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
+The remainder of this paper is organized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
 will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
-
-\section{Motivation and Background}
-
-%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
-%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
-%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
-%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
-%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
-%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
-%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
-%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shutted down to reduce electricity consumption in the case of TSUBAME Supercomputer.
-%Facing these problems, one solution will be federate supercomputer with public cloud.
-%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
-
-%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
-	\label{throughput TSUBAME}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{point_to_point_lab}
-	%\includegraphics{}
-	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
-	\label{throughput AMAZON to MATSULAB}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{point_to_point_AMAZON}
-	%\includegraphics{}
-	\caption{point to point connection inside AMAZON}
-	\label{point to point connection AMAZON}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{point_to_point_lab}
-	\caption{point to point connection throughput between AMAZON and our lab}
-	\label{point to point connection LAB}
-\end{figure}
-
-As we know, throughput gap between innerconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
-We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
-
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
-On the other hand, Fig.~\ref{throughput AMAZON to MATSULAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
-Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
-We can see that the I/O throughput also grows as number of nodes grows but the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
-%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
-%Also, if we compare the one nodes I/O throughput, 
-If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.
-
-%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput 
-However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linar line also a strong scalability.
-Since we can achieve a high innerconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
-
-Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with innerconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are settled in the same system.
-
-%3
-\section{I/O Bursting Buffer Overview}
-
-%\begin
-
-An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
-As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be tranferred to final storage system.
-%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
-Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
-%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
-%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.
-
-%Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage
-
-%Migration operation occurs when some nodes have to be shutted down in one cloud 
-%all jobs running on these nodes have to be backed up by using snapshot,
-
-\subsection{System Environment}
-First a general system used in following sections is defined as follow:
-
-%For security consideration and the fact that IPv4 addresses becomes rare,
-\begin{itemize}
-	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
-	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
-	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
-\end{itemize}
-
-\subsection{I/O Burst Buffer Architecture}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{IOserver}
-	\caption{I/O server and buffer queue}
-	\label{I/O server}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{overview}
-	\caption{overall illustrate of I/O Burst Buffer Architecture}
-	\label{overview}
-\end{figure}
-
-%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
-There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assgined only  and I/O burst buffer nodes, which assigned both private IP address.
-
-Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
-In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
-Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
-
-When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
-First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are settled in the same system, so data consistency can be guaranteed since that.
-Buffer queue operation includeing data write back and operation when queue is full will be described in following section.
-
-When user issue a read request, there are two conditions: file is bufferred in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
-In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
-If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.
-
-Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture:
-
-Consider there are two systems, named system 1 and system 2, and we assume that 
-%Arrows stand for network connection.
-%Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
-%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
-%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
-
-%Circles stand for computing nodes, which are used for standard computation.
-%Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
-%Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
-%I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-%Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
-
-%Since there is a big gap between cloud inside data transferring and accross two clouds in throughput, our goal is to fill the gap.
-
-%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation. 
-\subsection{Buffer Queue Write Back}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{buffer_queue}
-	\caption{buffer queue}
-	\label{buffer queue}
-\end{figure}
-
-in this subsection, we introduce operation of buffer queue
-
-\subsection{Read and Write}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{read_and_write}
-	\caption{read and write operation}
-	\label{read and write}
-\end{figure}
-
-In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
-We propose two kindes of model: one-side buffer and two-side buffer.
-
-\subsubsection{One-side Buffer}
-
-As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
-When I/O nodes need to write data back to storage in system 1, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.
-
-%data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
-%After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.
-
-%Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
-%After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
-%When I/O buffer nodes received data, then they writing data back to storage in cloud 1.
-
-\subsubsection{Two-side Buffer}
-
-%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
-
-%When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
-
-%After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
-%here a sub-index is used to refer to each piece's position, 
-%then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
-
-%When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
-
-%Data writing operation doing the opposite operation as reading operation.
-%When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
-%After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.
-
-%I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position.
-and then start to transfer data concurrently.
-
-%Then I/O buffer nodes write data to storage in cloud 1.
-
-\begin{comment}
-\subsubsection{Index Protocol}
-
-\begin{figure}[tb]
-	\centering
-%	\includegraphics
-	\caption{index protocol}
-	\label{index protocol}
-\end{figure}
-
-As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
-There are two phases of data splitting in both reading and writing operation, 
-\end{comment}
-%\subsubsection{Node Migration}
-%Node migration happens when some nodes have to be shutted down due to some situation like power problem in summer, and still need to provide service to users.
-%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
-
-%However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
-%When using I/O buffer nodes
-
-\section{I/O Bursting Buffer Model}
-
-%\begin{figure}[tb]
-%	\centering
-%	\includegraphics
-%	\caption{definition}
-%	\label{definition}
-%\end{figure}
-
-Throughput-based Model and Cost-based Model will be described in this section.
-We make following definitions in order to describe our model:
-
-\begin{itemize}
-	\item Numbers of computing nodes are $c_1,c_2$, and numbers of I/O buffer nodes are $n_1, n_2$ respectively.
-	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in sytem 1 connect to storage in system 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each system have Internet connection.
-	\item Since overall Internet throughput is affected by number of nodes involved in connection. $I(n_1,n_2)$ is used to refer to Internet throughput using $n_1,n_2$ I/O buffer nodes respectively.
-	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
-	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in system 1 and ,storage and $n_2$ I/O nodes in system 2.
-	\item Cost for standard node in system 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.
-	\item Available 
-\end{itemize}
-
-\subsection{Throughput-based Model}
-%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
-When I/O buffer nodes in cloud 2 connect to storage in cloud 1, there are two data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to storage in cloud 1, so throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{direct}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
-\end{equation}
-
-In the case of using I/O buffer nodes in both cloud, there are three data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to I/O buffer nodes in cloud 1, I/O buffer nodes in cloud 1 to storage in cloud 1, throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{I/O buffer}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
-\end{equation}
-
-In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:
-
-\begin{equation}
-	\begin{cases}
-		\text{throughput}_{\text{direct}} \geq \text{throughput}_{\text{I/O buffer}} & \text{use direct connection}\\
-		\text{throughput}_{\text{direct}} < \text{throughput}_{\text{I/O buffer}} & \text{use I/O buffer}
-	\end{cases}
-\end{equation}
-
-\subsection{Cost-based Model}
-In the case of cost-based model, we consider
-using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:
-
-\begin{equation}
-	\begin{cases}
-		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{direct connection}\\
-		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{I/O buffer}
-	\end{cases}
-\end{equation}
-
-here we compute cost by using $T_1,T_2$:
-\begin{equation}
-	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
-\end{equation}
-\begin{align}
-	\text{cost}_\text{I/O buffer}&=c_2\times C_2\_Money(T_2)\\\nonumber 
-				     &+n_1\times C_1\_High\_Money(T_2)\\ \nonumber
-				     &+n_2\times C_2\_High\_Money(T_2)
-\end{align}
-
-%\subsection{}
-%\subsection{Migration Model}
-%Since there are some condition that some supercomputer nodes must be shutted down, and jobs running on these nodes have to be migrate to another cloud. There are 
-%\begin{equation}
-%	Data	
-%\end{equation}
-
-\section{Evaluation}
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=8cm]{ThroughputAMAZONTSUBAME}
-	\caption{Throughput between AMAZON and TSUBAME}
-	\label{Throughput between AMAZON and TSUBAME}
-\end{figure}
-
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2.
-
-\section{Conclusion and Related Work}
-
-\bibliography{reference}
-\end{document}

### 2014-06-27 paper/section/model.tex
section

--- 2014-06-26 paper/paper.tex
@@
-\documentclass[JIP,draft]{ipsj}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{verbatim}
-\usepackage{supertabular}
-\bibliographystyle{ipsjunsrt-e.bst}
-
-\begin{document}
-\title{Towards Cloud Bursting for Extreme Scale Supercomputers}
-
-\begin{abstract}
-%Parallel programming are used to reduce execution time of complex problems, also fully utilizing computing resource of Supercomputers.
-
-%supercomputers usually consist of a large number of nodes, provide high parallelism for multi-user.
-%However computing nodes in supercomputers will not meet the request in some situation, such as some nodes have to be shut down to reduce electric consumption in summer or just several serial applications occupy nodes making others must wait.
-%large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
-%One solution is running virtual machine on 
-%In this paper, a comparison was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
-%In order to satisfy these temporary request peak, we are trying to federate supercomputers with public cloud, which is known as cloud bursting.
-%Although some sophisticated solutions are available, still we are facing several challenges, since there are a significant performance gap between supercomputers and public cloud.
-%In this paper, we focus on I/O throughput between these two environments, we propose a I/O Bursting Buffer Model to burst I/O throughput between supercomputer and public cloud and reduce the cost for extra time usage caused by low I/O throughput.
-%we also provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
-%The result shows our model can provide a stable and high I/O throughput as well as a low cost in most cases.
-
-Extreme-scale HPC systems, which consist of a large number of compute nodes, can provide high computational capacity for multiple users.
-However, computing nodes in the systems occasionally can not meet the demand due to bursty job requests in short period times.
-In order to accommodate the bursty requests, we consider federating HPC systems with public clouds, which is known as cloud bursting.
-Although the federated systems can acquire virtually infinite computational power with cloud bursting, the QoS may not be guaranteed due to a significant performance gap between HPC systems and public clouds.
-The most critical problem is a gap in I/O performance.
-In this paper, we propose an I/O acceleration technique using distributed cloud bursting buffers.
-We also create the I/O performance model to explore the effectiveness.
-Our model-based simulations, which target the TSUBAME supercomputer for an HPC system, and AMAZON EC2 for a public cloud, show that the distributed cloud busting buffer can improve I/O throughput while reducing the cost.
-
-\end{abstract}
-
-\begin{keyword}
-Supercomputer, Cloud, I/O Bursting Buffer Model
-\end{keyword}
-
-\maketitle
-
-%1
-\section{Introduction}
-An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
-%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
-
-%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
-%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
-Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down, reducing numbers of nodes will make the first problem more serous.
-
-One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
-Although cloud bursting is used by several companies and already have some sophisticated solutions\cite{Eucalyptus,stratos,Seagull}, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to federate a supercomputer with a public cloud, and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
-The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user.
-This paper focuses on methodology of increasing throughput when we do federation.
-
-In order to increase data transfer throughput, we propose a I/O burst buffer architecture that uses several nodes in each system as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O burst buffer model that uses to switch between I/O burst buffer mode and direct connect mode.
-%This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
-%Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
-Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.
-
-Our contribution can be summary as following:
-\begin{itemize}
-	\item An architecture of I/O burst buffer for increasing data transfer throughput between two systems.
-	\item A throughput-based I/O burst buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two systems, a cost-based I/O burst buffer model uses to reduce the total cost and a queue model used.
-	%\item 
-	\item Evaluating I/O burst buffer architecture and two models by using data obtained from several benchmarks from TSUBAME supercomputer and AMAZON EC2 public cloud.
-\end{itemize}
-%2
-The remainder of this paper is organized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
-will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
-
-\section{Motivation and Background}
-
-%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
-%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
-%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
-%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
-%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
-%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
-%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
-%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shut down to reduce electricity consumption in the case of TSUBAME Supercomputer.
-%Facing these problems, one solution will be federate supercomputer with public cloud.
-%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
-
-%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{throughput_tsubame}
-	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
-	\label{throughput TSUBAME}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{AMAZON_to_OUR_LAB}
-	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
-	\label{throughput AMAZON to OURLAB}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{point_to_point_AMAZON}
-	\caption{point to point connection inside AMAZON}
-	\label{point to point connection AMAZON}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{point_to_point_lab}
-	\caption{point to point connection throughput between AMAZON and our lab}
-	\label{point to point connection LAB}
-\end{figure}
-
-As we know, throughput gap between interconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
-We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
-
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
-On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
-Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
-We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
-%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of interconnection inside supercomputer is quit larger than that from AMAZON.
-%Also, if we compare the one nodes I/O throughput, 
-Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput 
-If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.
-
-%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the interconnection throughput 
-However, if we consider interconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
-Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
-
-Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with interconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are allocated in the same system.
-
-%3
-\section{I/O Bursting Buffer Overview}
-
-%\begin
-
-An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
-As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system.
-%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
-Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
-%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
-%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.
-
-%Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage
-
-%Migration operation occurs when some nodes have to be shut down in one cloud 
-%all jobs running on these nodes have to be backed up by using snapshot,
-
-\subsection{System Environment}
-First a general system used in following sections is defined as follow:
-
-%For security consideration and the fact that IPv4 addresses becomes rare,
-\begin{itemize}
-	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
-	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
-	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
-\end{itemize}
-
-\subsection{I/O Burst Buffer Architecture}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{IOserver}
-	\caption{I/O server and buffer queue}
-	\label{I/O server}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{overview}
-	\caption{overall illustrate of I/O Burst Buffer Architecture}
-	\label{overview}
-\end{figure}
-
-%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
-There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assigned only  and I/O burst buffer nodes, which assigned both private IP address.
-
-Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
-In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
-Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
-
-When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
-First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are allocated in the same system, so data consistency can be guaranteed since that.
-Buffer queue operation including data write back and operation when queue is full will be described in following section.
-
-When user issue a read request, there are two conditions: file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
-In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
-If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.
-
-Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture.
-
-%Consider there are two systems, named system 1 and system 2
-
-%Arrows stand for network connection.
-%Orange arrows are interconnection networks inside cloud, although two clouds used the same color for interconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
-%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
-%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
-
-%Circles stand for computing nodes, which are used for standard computation.
-%Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
-%Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
-%I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-%Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
-
-%Since there is a big gap between cloud inside data transferring and accross two clouds in throughput, our goal is to fill the gap.
-
-%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.
-
-%in this subsection, we introduce operations of buffer queue write back.
-
-\subsection{Read and Write}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{read_and_write}
-	\caption{read and write operation}
-	\label{read and write}
-\end{figure}
-
-In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
-We propose two kinds of model: one-side buffer and two-side buffer.
-
-\subsubsection{One-side Buffer}
-
-As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
-When I/O nodes need to write data back to storage in another system, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.
-
-Similarly, when I/O nodes need to read data from storage in another system, several I/O nodes will be assigned equal size of data, and then these nodes read assigned piece of data from the storage concurrently.
-
-There will be two problems in this solution:
-\begin{itemize}
-	\item First storage should be opened to Internet, in order that I/O nodes can read from or write to it.
-		However storage system in supercomputer store Petabyte of research data, open the access of storage system means that put these research data under risk of attack.
-	\item As we mentioned before, throughput of one side communication is lower than two side communication, since we use SSH protocol based File system for security reason.
-		also two side communication can achieve a higher throughput with fewer nodes, according to pay-as-you-go policy, reduce number of nodes can reduce cost.
-\end{itemize}
-%data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
-%After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.
-
-%Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
-%After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
-%When I/O buffer nodes received data, then they writing data back to storage in cloud 1.
-
-\subsubsection{Two-side Buffer}
-
-On the contrary, two-side buffer solution use I/O buffer nodes in both two systems as Fig.~\ref{read and write} orange arrows show.
-I/O data will be split twice, transferred throughput two sides of I/O buffer nodes and then reached the destination.
-
-Consider I/O nodes in system 2 issue a write back operation, also, data is already spread among I/O nodes in system 2, each I/O node will find a pair among I/O nodes in system 1, then transfer their piece of data to system 1 concurrently.
-After I/O node in system 1 received data, they write data back to storage in system 1.
-
-Compared with one-side buffer, two-side buffer required one more data transfer (I/O nodes to storage in the same system), if storage data transfer throuhput become a bottleneck, two-side buffer will cost more time than one-side buffer.
-Also, two-side buffer require both systems allocate I/O buffer nodes, if node usage is charge in both system, total cost may be larger than one-side buffer.
-
-%the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
-Since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
-Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.
-
-%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
-
-%When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
-
-%After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
-%here a sub-index is used to refer to each piece's position, 
-%then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
-
-%When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
-
-%Data writing operation doing the opposite operation as reading operation.
-%When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
-%After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.
-
-%I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position.
-and then start to transfer data concurrently.
-
-%Then I/O buffer nodes write data to storage in cloud 1.
-
-\begin{comment}
-\subsubsection{Index Protocol}
-
-\begin{figure}[tb]
-	\centering
-%	\includegraphics
-	\caption{index protocol}
-	\label{index protocol}
-\end{figure}
-
-As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
-There are two phases of data splitting in both reading and writing operation, 
-\end{comment}
-%\subsubsection{Node Migration}
-%Node migration happens when some nodes have to be shut down due to some situation like power problem in summer, and still need to provide service to users.
-%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
-
-%However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
-%When using I/O buffer nodes
-
 \section{I/O Burst Buffer Model}
@@
 In this case, jobs running on public cloud have to be moved back to original system until buffer queue is empty.
-
-\section{Evaluation}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=6cm]{}
-	\caption{throughput comparison with and without I/O burst buffer}
-	\label{throughput}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=6cm]{}
-	\caption{cost comparison with and without I/O burst buffer}
-	\label{cost}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{compress_rate}
-	\caption{compress rate}
-	\label{compress rate}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{compress_time}
-	\caption{compress time on TSUBAME V queue and AMAZON EC2}
-	\label{compress time}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=6cm]{}
-	\caption{throughput comparison with and without compress}
-	\label{compress}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics
-	\caption{cache hit and miss throughput comparison}
-	\label{cache hit}
-\end{figure}
-
-%\begin{figure}[tb]
-%	\centering
-%	\includegraphics[width=6cm]{tsubamelustre}
-%	\caption{TSUBAME Lustre workload}
-%	\label{Lustre workload}
-%\end{figure}
-
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region, using
-%m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
-m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}.
-Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{point to point connection LAB} ).
-%According to these data and definition described above, we use values defined below.
-
-%\begin{center}
-%\begin{tabular}[tb]{|c|c|}\hline
-%	$D_2$&$E_1$\\\hline
-%	8TB/s&1.08Gbit/s(135MB/s)\\\hline
-
-%\end{tabular}
-%\end{center}
-For throughput between two systems and inside system, from benchmark data, it shows it is hard to achieve a high throughput with only one nodes, and also there is a limit on maximum throughput between two systems and inside system.
-Although incresing nodes can increse throughput before reach the maximum, throughput achieved by each nodes decrease because of conflict.
-For these reason, we use following formular for throughput between two systems and inside system.
-%TSUBAME and AMAZON EC2, we use similar model in \cite{ccgrid}:
-\begin{equation}
-throughput=-Ax^2+Bx+C~~ A,B>0\\
-\end{equation}
-we use following equations to determine $A,B,C$
-\begin{equation}
-\begin{cases}
-	-A+B+C=throughput_{one}\\\nonumber
-	\frac{B}{2A}=n_{max}\\\nonumber
-	-An_{max}^2+Bn_{max}+C=throughput_{max}\\
-\end{cases}
-\end{equation}
-
-First, we compare throughput with and without I/O buffer nodes.
-Since it is hard for one node to fully utilize Internet and Ethernet bandwidth, according to Fig.~\ref{throughput AMAZON to OURLAB}, we assume that one node can achieve half of maximum bandwidth.
-We can see from Fig.~\ref{throughput}, when interconnection throughput is larger than Internet throughput, our I/O buffer can achieve a higher throughput.
-
-Then, we compare overall cost by using I/O burst buffer,
-
-we compare throughput with and without compression, Fig.~\ref{compress rate} shows compress and Fig.~\ref{compress time} shows compress and decompress time on TSUBAME V queue and AMAZON EC2 with a different compress level by using zlib\cite{zlib}.
-We can achieve a high compress rate, but the throughput is low, up to 160MB/s, depends on compress level, it is hard to find a compress library can compress data faster and smaller, so the compress throughput may become a bottleneck.
-On the other hand, the compress rate is high, since the buffer size is limited, if we can make data smaller, it means we can increase the buffer hit rate, Fig.~\ref{cache hit} shows a throughput comparison between cache miss and hit.
-
-Fig.~\ref{compress}
-\section{Conclusion and Future Work}
-
-In this paper, we propose a I/O burst buffer architecture to burst I/O throughput, provide throughput-based, cost-based and queue write back model, and provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
-we use several nodes in each system as a I/O buffer nodes, and use data buffering to hide the low throughput between two systems connected by Internet.
-
-From simulation result, we showed that our I/O burst buffer can increase I/O throughput when Internet throughput is far smaller than interconnection throughput as well as reducing the overall cost.
-
-For future work, we plan to implement this I/O burst buffer architecture.
-\bibliography{reference}
-\end{document}

### 2014-06-27 paper/section/motivation.tex
section

--- 2014-06-24 paper/paper.tex
@@
-\documentclass[JIP,draft]{ipsj}
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{verbatim}
-
-\bibliographystyle{ipsjunsrt-e.bst}
-
-\begin{document}
-\title{Towards Cloud Bursting for Extreme Scale Supercomputers}
-
-\begin{abstract}
-%Parallel programming are used to reduce execution time of complex problems, also fully utilizing computing resource of Supercomputers.
-
-%supercomputers usually consist of a large number of nodes, provide high parallelism for multi-user.
-%However computing nodes in supercomputers will not meet the request in some situation, such as some nodes have to be shutted down to reduce electric consumption in summer or just several serial applications occupy nodes making others must wait.
-%large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
-%One solution is running virtual machine on 
-%In this paper, a comparision was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
-%In order to satisfy these temporary request peak, we are trying to federate supercomputers with public cloud, which is known as cloud bursting.
-%Although some sophisticated solutions are available, still we are facing several challenges, since there are a significant performance gap between supercomputers and public cloud.
-%In this paper, we focus on I/O throughput between these two environments, we propose a I/O Bursting Buffer Model to burst I/O throughput between supercomputer and public cloud and reduce the cost for extra time usage caused by low I/O throughput.
-%we also provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
-%The result shows our model can provide a stable and high I/O throughput as well as a low cost in most cases.
-
-Extreme-scale HPC systems, which consist of a large number of compute nodes, can provide high computational capacity for multiple users.
-However, computing nodes in the systems occasionally can not meet the demand due to bursty job requests in short period times.
-In order to accommodate the bursty requests, we consider federating HPC systems with public clouds, which is known as cloud bursting.
-Although the federated systems can acquire virtually infinite computational power with cloud bursting, the QoS may not be guaranteed due to a significant performance gap between HPC systems and public clouds.
-The most critical problem is a gap in I/O performance.
-In this paper, we propose an I/O acceleration technique using distributed cloud bursting buffers.
-We also create the I/O performance model to explore the effectiveness.
-Our model-based simulations, which target the TSUBAME supercomputer for an HPC system, and AMAZON EC2 for a public cloud, show that the distributed cloud busting buffer can improve I/O throughput while reducing the cost.
-
-\end{abstract}
-
-\begin{keyword}
-Supercomputer, Cloud, I/O Bursting Buffer Model
-\end{keyword}
-
-\maketitle
-
-%1
-\section{Introduction}
-An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
-%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
-
-%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until perious job finished although there are 49 nodes remainning available.
-%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
-Another problem is the power problem in summer, in order to reduce power comsumation, some nodes will be forced to be shutted down, reducing numbers of nodes will make the first problem more serous.
-
-One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
-Although cloud bursting is used by several companies and already have some sophisticated solutions\cite{Eucalyptus,stratos,Seagull}, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to ferderate a supercomputer with a public cloud, and there are several studies on .
-The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user.
-This paper focuses on methodology of increasing throughput when we do federation.
-
-In order to increase data transfer throughput, we propose a I/O bursting buffer architecture that uses several nodes in each cloud as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O bursting buffer model that uses to switch between I/O bursting buffer mode and direct connect mode.
-%This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
-%Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
-Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.
-
-Our contribution can be summary as following:
-\begin{itemize}
-	\item An architecture of I/O bursting buffer for increasing data transfer throughput between two clouds.
-	\item A throughput-based I/O bursting buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two clouds, and a cost-based I/O bursting buffer model uses to reduce the total cost.
-	%\item 
-	\item Evaluating I/O bursting buffer architecture and two models by using data obtained from several benchmarks from tsubame supercomputer and AMAZON EC2 public cloud.
-\end{itemize}
-%2
-The remainder of this paper is orginized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
-will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
-
 \section{Motivation and Background}
@@
 
-As we know, throughput gap between innerconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
+As we know, throughput gap between interconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
 We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
 
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a innerconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggreate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
-On the other hand, Fig.~\ref{throughput AMAZON to MATSULAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
+Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
+On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
 Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
-We can see that the I/O throughput also grows as number of nodes grows but the aggreate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
-%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of innerconnection inside supercomputer is quit larger than that from AMAZON.
+We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
+%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of interconnection inside supercomputer is quit larger than that from AMAZON.
 %Also, if we compare the one nodes I/O throughput, 
+Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput 
 If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.
 
-%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the innerconnection throughput 
-However, if we consider innerconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linar line also a strong scalability.
-Since we can achieve a high innerconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
+%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the interconnection throughput 
+However, if we consider interconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
+Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
 
-Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with innerconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are settled in the same system.
-
-%3
-\section{I/O Bursting Buffer Overview}
-
-%\begin
-
-An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
-As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be tranferred to final storage system.
-%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
-Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
-%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
-%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.
-
-%Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage
-
-%Migration operation occurs when some nodes have to be shutted down in one cloud 
-%all jobs running on these nodes have to be backed up by using snapshot,
-
-\subsection{System Environment}
-First a general system used in following sections is defined as follow:
-
-%For security consideration and the fact that IPv4 addresses becomes rare,
-\begin{itemize}
-	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
-	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
-	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
-\end{itemize}
-
-\subsection{I/O Burst Buffer Architecture}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{IOserver}
-	\caption{I/O server and buffer queue}
-	\label{I/O server}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{overview}
-	\caption{overall illustrate of I/O Burst Buffer Architecture}
-	\label{overview}
-\end{figure}
-
-%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
-There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assgined only  and I/O burst buffer nodes, which assigned both private IP address.
-
-Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
-In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
-Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
-
-When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
-First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are settled in the same system, so data consistency can be guaranteed since that.
-Buffer queue operation includeing data write back and operation when queue is full will be described in following section.
-
-When user issue a read request, there are two conditions: file is bufferred in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
-In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
-If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.
-
-Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture:
-
-Consider there are two systems, named system 1 and system 2, and we assume that 
-%Arrows stand for network connection.
-%Orange arrows are innerconnection networks inside cloud, although two clouds used the same color for innerconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
-%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
-%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
-
-%Circles stand for computing nodes, which are used for standard computation.
-%Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
-%Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
-%I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-%Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
-
-%Since there is a big gap between cloud inside data transferring and accross two clouds in throughput, our goal is to fill the gap.
-
-%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation. 
-\subsection{Buffer Queue Write Back}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{buffer_queue}
-	\caption{buffer queue}
-	\label{buffer queue}
-\end{figure}
-
-in this subsection, we introduce operation of buffer queue
-
-\subsection{Read and Write}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{read_and_write}
-	\caption{read and write operation}
-	\label{read and write}
-\end{figure}
-
-In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
-We propose two kindes of model: one-side buffer and two-side buffer.
-
-\subsubsection{One-side Buffer}
-
-As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
-When I/O nodes need to write data back to storage in system 1, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.
-
-%data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
-%After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.
-
-%Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
-%After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
-%When I/O buffer nodes received data, then they writing data back to storage in cloud 1.
-
-\subsubsection{Two-side Buffer}
-
-%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
-
-%When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
-
-%After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
-%here a sub-index is used to refer to each piece's position, 
-%then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
-
-%When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
-
-%Data writing operation doing the opposite operation as reading operation.
-%When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
-%After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.
-
-%I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position.
-and then start to transfer data concurrently.
-
-%Then I/O buffer nodes write data to storage in cloud 1.
-
-\begin{comment}
-\subsubsection{Index Protocol}
-
-\begin{figure}[tb]
-	\centering
-%	\includegraphics
-	\caption{index protocol}
-	\label{index protocol}
-\end{figure}
-
-As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
-There are two phases of data splitting in both reading and writing operation, 
-\end{comment}
-%\subsubsection{Node Migration}
-%Node migration happens when some nodes have to be shutted down due to some situation like power problem in summer, and still need to provide service to users.
-%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
-
-%However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
-%When using I/O buffer nodes
-
-\section{I/O Bursting Buffer Model}
-
-%\begin{figure}[tb]
-%	\centering
-%	\includegraphics
-%	\caption{definition}
-%	\label{definition}
-%\end{figure}
-
-Throughput-based Model and Cost-based Model will be described in this section.
-We make following definitions in order to describe our model:
-
-\begin{itemize}
-	\item Numbers of computing nodes are $c_1,c_2$, and numbers of I/O buffer nodes are $n_1, n_2$ respectively.
-	\item $D_1(n_2)$ is throughput when $n_2$ I/O nodes in sytem 1 connect to storage in system 2 directly, similar to $D_1(n_2)$, $D_2(n_1)$ refers to throughput when $n_1$ I/O nodes in cloud 2 connect to storage in cloud 1 directly, here we assume only I/O nodes in each system have Internet connection.
-	\item Since overall Internet throughput is affected by number of nodes involved in connection. $I(n_1,n_2)$ is used to refer to Internet throughput using $n_1,n_2$ I/O buffer nodes respectively.
-	\item For interconnection network throughput, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
-	\item $M_1(n_1),M_2(n_2)$ are throughput of connection between storage and $n_1$ I/O nodes in system 1 and ,storage and $n_2$ I/O nodes in system 2.
-	\item Cost for standard node in system 1 is defined as $C_1\_Money(T)$ for $T$ time usage and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, here cost for I/O nodes is defined as $C_1\_High\_Money(T),C_2\_High\_Money(T)$ for $T$ time respectively.
-	\item Available 
-\end{itemize}
-
-\subsection{Throughput-based Model}
-%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
-When I/O buffer nodes in cloud 2 connect to storage in cloud 1, there are two data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to storage in cloud 1, so throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{direct}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
-\end{equation}
-
-In the case of using I/O buffer nodes in both cloud, there are three data transfers: computation nodes to I/O buffer nodes in cloud 2, I/O buffer nodes in cloud 2 to I/O buffer nodes in cloud 1, I/O buffer nodes in cloud 1 to storage in cloud 1, throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{I/O buffer}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
-\end{equation}
-
-In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:
-
-\begin{equation}
-	\begin{cases}
-		\text{throughput}_{\text{direct}} \geq \text{throughput}_{\text{I/O buffer}} & \text{use direct connection}\\
-		\text{throughput}_{\text{direct}} < \text{throughput}_{\text{I/O buffer}} & \text{use I/O buffer}
-	\end{cases}
-\end{equation}
-
-\subsection{Cost-based Model}
-In the case of cost-based model, we consider
-using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:
-
-\begin{equation}
-	\begin{cases}
-		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{direct connection}\\
-		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{I/O buffer}
-	\end{cases}
-\end{equation}
-
-here we compute cost by using $T_1,T_2$:
-\begin{equation}
-	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
-\end{equation}
-\begin{align}
-	\text{cost}_\text{I/O buffer}&=c_2\times C_2\_Money(T_2)\\\nonumber 
-				     &+n_1\times C_1\_High\_Money(T_2)\\ \nonumber
-				     &+n_2\times C_2\_High\_Money(T_2)
-\end{align}
-
-%\subsection{}
-%\subsection{Migration Model}
-%Since there are some condition that some supercomputer nodes must be shutted down, and jobs running on these nodes have to be migrate to another cloud. There are 
-%\begin{equation}
-%	Data	
-%\end{equation}
-
-\section{Evaluation}
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=8cm]{ThroughputAMAZONTSUBAME}
-	\caption{Throughput between AMAZON and TSUBAME}
-	\label{Throughput between AMAZON and TSUBAME}
-\end{figure}
-
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME and AMAZON EC2.
-
-\section{Conclusion and Related Work}
-
-\bibliography{reference}
-\end{document}
+Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with interconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are allocated in the same system.

### 2014-06-27 paper/paper.tex
0627

@@
 %high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
-Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down, reducing numbers of nodes will make the first problem more serous.
+Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down (peak shift in TSUBAME\cite{TSUBAME}), reducing numbers of nodes will make the first problem more serous.
 
@@
 Throughput-based Model compare one-side buffer throughput with two-side buffer, cost-based model compare one-side buffer cost with two-side buffer, and buffer queue write back model. 
-We make definitions shows in Table.~\ref{definition} in order to describe our model:
+We make definitions shows in \tabref{definition} in order to describe our model:
 \begin{table}[tb]

### 2014-06-29 paper/paper.tex
0630

@@
 	%\includegraphics[width=6cm]{}
+	\caption{throughput comparison with and without compress}
+	\label{compress}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	%\includegraphics
+	\caption{cache hit and miss throughput comparison}
+	\label{cache hit}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	%\includegraphics[width=6cm]{}
 	\caption{throughput comparison with and without I/O burst buffer}
@@
 	\label{compress time}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=6cm]{}
-	\caption{throughput comparison with and without compress}
-	\label{compress}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics
-	\caption{cache hit and miss throughput comparison}
-	\label{cache hit}
 \end{figure}
@@
 \begin{equation}
+	\label{throughput equation}
 \begin{cases}
@@
 
-First, we compare throughput with and without I/O buffer nodes.
-Since it is hard for one node to fully utilize Internet and Ethernet bandwidth, according to Fig.~\ref{throughput AMAZON to OURLAB}, we assume that one node can achieve half of maximum bandwidth.
-We can see from Fig.~\ref{throughput}, when interconnection throughput is larger than Internet throughput, our I/O buffer can achieve a higher throughput.
+Since it is hard for one node to fully utilize Internet and Ethernet bandwidth, according to Fig.~\ref{throughput AMAZON to OURLAB}, we assume that one node can achieve 80\% of maximum bandwidth, and by using I/O burst buffer, can achieve 100\% of maximum bandwidth of both Ethernet and Internet, here Ethernet throughput refers to Ethernet connection throughput in public cloud.
 
-Then, we compare overall cost by using I/O burst buffer,
+First we consider the throughput comparison between direct connection and cache hit cases by using I/O burst buffer.
+If file is buffered in I/O buffer nodes, computing nodes can read it through Ethernet, Fig.~\ref{cache hit}, shows the comparison, we can see that when Ethernet throughput larger than Internet throughput, our solution can achieve a higher I/O throughput, here we assume that Ethernet throuhput can be lower than Internet throughput, but from Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{throughput TSUBAME}, Ethernet usually is faster than Internet, and by using our solution can achieve a high throughput.
 
-we compare throughput with and without compression, Fig.~\ref{compress rate} shows compress and Fig.~\ref{compress time} shows compress and decompress time on TSUBAME V queue and AMAZON EC2 with a different compress level by using zlib\cite{zlib}.
+Then, we compare throughput with and without I/O buffer nodes.
+We can see from Fig.~\ref{throughput},although our solution can be limited by both Internet and Ethernet throughput, our I/O burst buffer can fully utilize both Internet and Ethernet.
+Like previous comparison, when Ethernet is faster than Internet, our solution can achieve a throughput burst even file is not stored in buffer queue in I/O burst buffer like (read data from storage).
+
+After that, we compare overall cost when use two-side buffer and one-side buffer, since execution time, in our case, I/O time and I/O throughput will affect cost, for Internet and Ethernet throughput, we use \ref{throughput equation}.
+From Fig.~\ref{cost}, 
+Finally, we compare throughput with and without compression, Fig.~\ref{compress rate} shows compress and Fig.~\ref{compress time} shows compress and decompress time on TSUBAME V queue and AMAZON EC2 with a different compress level by using zlib\cite{zlib}.
 We can achieve a high compress rate, but the throughput is low, up to 160MB/s, depends on compress level, it is hard to find a compress library can compress data faster and smaller, so the compress throughput may become a bottleneck.

### 2014-06-30 paper/paper.tex
Splited paper.tex

--- 2014-06-26 paper/paper.tex
@@
 %1
-\section{Introduction}
-An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
-%Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
+\input{1_introduction}
 
-%Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
-%high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
-Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down, reducing numbers of nodes will make the first problem more serous.
-
-One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
-Although cloud bursting is used by several companies and already have some sophisticated solutions\cite{Eucalyptus,stratos,Seagull}, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to federate a supercomputer with a public cloud, and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
-The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user.
-This paper focuses on methodology of increasing throughput when we do federation.
-
-In order to increase data transfer throughput, we propose a I/O burst buffer architecture that uses several nodes in each system as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O burst buffer model that uses to switch between I/O burst buffer mode and direct connect mode.
-%This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
-%Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
-Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.
-
-Our contribution can be summary as following:
-\begin{itemize}
-	\item An architecture of I/O burst buffer for increasing data transfer throughput between two systems.
-	\item A throughput-based I/O burst buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two systems, a cost-based I/O burst buffer model uses to reduce the total cost and a queue model used.
-	%\item 
-	\item Evaluating I/O burst buffer architecture and two models by using data obtained from several benchmarks from TSUBAME supercomputer and AMAZON EC2 public cloud.
-\end{itemize}
-%2
-The remainder of this paper is organized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
-will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
-
-\section{Motivation and Background}
-
-%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
-%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
-%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
-%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
-%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
-%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
-%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
-%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shut down to reduce electricity consumption in the case of TSUBAME Supercomputer.
-%Facing these problems, one solution will be federate supercomputer with public cloud.
-%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
-
-%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{throughput_tsubame}
-	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
-	\label{throughput TSUBAME}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{AMAZON_to_OUR_LAB}
-	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
-	\label{throughput AMAZON to OURLAB}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{point_to_point_AMAZON}
-	\caption{point to point connection inside AMAZON}
-	\label{point to point connection AMAZON}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{point_to_point_lab}
-	\caption{point to point connection throughput between AMAZON and our lab}
-	\label{point to point connection LAB}
-\end{figure}
-
-As we know, throughput gap between interconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
-We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
-
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
-On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
-Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
-We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
-%From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of interconnection inside supercomputer is quit larger than that from AMAZON.
-%Also, if we compare the one nodes I/O throughput, 
-Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput 
-If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.
-
-%But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the interconnection throughput 
-However, if we consider interconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
-Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
-
-Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with interconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are allocated in the same system.
+\input{2_motivation}
 
 %3
-\section{I/O Bursting Buffer Overview}
+\input{3_burst_buffer}
 
-%\begin
+\input{4_model}
 
-An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
-As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system.
-%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
-Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
-%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
-%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.
+\input{5_evaluation}
 
-%Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage
+\input{6_conclusion}
 
-%Migration operation occurs when some nodes have to be shut down in one cloud 
-%all jobs running on these nodes have to be backed up by using snapshot,
-
-\subsection{System Environment}
-First a general system used in following sections is defined as follow:
-
-%For security consideration and the fact that IPv4 addresses becomes rare,
-\begin{itemize}
-	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
-	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
-	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
-\end{itemize}
-
-\subsection{I/O Burst Buffer Architecture}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{IOserver}
-	\caption{I/O server and buffer queue}
-	\label{I/O server}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{overview}
-	\caption{overall illustrate of I/O Burst Buffer Architecture}
-	\label{overview}
-\end{figure}
-
-%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
-There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assigned only  and I/O burst buffer nodes, which assigned both private IP address.
-
-Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
-In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
-Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
-
-When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
-First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are allocated in the same system, so data consistency can be guaranteed since that.
-Buffer queue operation including data write back and operation when queue is full will be described in following section.
-
-When user issue a read request, there are two conditions: file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
-In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
-If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.
-
-Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture.
-
-%Consider there are two systems, named system 1 and system 2
-
-%Arrows stand for network connection.
-%Orange arrows are interconnection networks inside cloud, although two clouds used the same color for interconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
-%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud.
-%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.
-
-%Circles stand for computing nodes, which are used for standard computation.
-%Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
-%Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
-%I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
-%Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.
-
-%Since there is a big gap between cloud inside data transferring and accross two clouds in throughput, our goal is to fill the gap.
-
-%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.
-
-%in this subsection, we introduce operations of buffer queue write back.
-
-\subsection{Read and Write}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{read_and_write}
-	\caption{read and write operation}
-	\label{read and write}
-\end{figure}
-
-In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
-We propose two kinds of model: one-side buffer and two-side buffer.
-
-\subsubsection{One-side Buffer}
-
-As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
-When I/O nodes need to write data back to storage in another system, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.
-
-Similarly, when I/O nodes need to read data from storage in another system, several I/O nodes will be assigned equal size of data, and then these nodes read assigned piece of data from the storage concurrently.
-
-There will be two problems in this solution:
-\begin{itemize}
-	\item First storage should be opened to Internet, in order that I/O nodes can read from or write to it.
-		However storage system in supercomputer store Petabyte of research data, open the access of storage system means that put these research data under risk of attack.
-	\item As we mentioned before, throughput of one side communication is lower than two side communication, since we use SSH protocol based File system for security reason.
-		also two side communication can achieve a higher throughput with fewer nodes, according to pay-as-you-go policy, reduce number of nodes can reduce cost.
-\end{itemize}
-%data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
-%After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.
-
-%Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
-%After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
-%When I/O buffer nodes received data, then they writing data back to storage in cloud 1.
-
-\subsubsection{Two-side Buffer}
-
-On the contrary, two-side buffer solution use I/O buffer nodes in both two systems as Fig.~\ref{read and write} orange arrows show.
-I/O data will be split twice, transferred throughput two sides of I/O buffer nodes and then reached the destination.
-
-Consider I/O nodes in system 2 issue a write back operation, also, data is already spread among I/O nodes in system 2, each I/O node will find a pair among I/O nodes in system 1, then transfer their piece of data to system 1 concurrently.
-After I/O node in system 1 received data, they write data back to storage in system 1.
-
-Compared with one-side buffer, two-side buffer required one more data transfer (I/O nodes to storage in the same system), if storage data transfer throuhput become a bottleneck, two-side buffer will cost more time than one-side buffer.
-Also, two-side buffer require both systems allocate I/O buffer nodes, if node usage is charge in both system, total cost may be larger than one-side buffer.
-
-%the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
-Since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
-Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.
-
-%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.
-
-%When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.
-
-%After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
-%here a sub-index is used to refer to each piece's position, 
-%then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.
-
-%When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.
-
-%Data writing operation doing the opposite operation as reading operation.
-%When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
-%After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.
-
-%I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position.
-and then start to transfer data concurrently.
-
-%Then I/O buffer nodes write data to storage in cloud 1.
-
-\begin{comment}
-\subsubsection{Index Protocol}
-
-\begin{figure}[tb]
-	\centering
-%	\includegraphics
-	\caption{index protocol}
-	\label{index protocol}
-\end{figure}
-
-As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
-There are two phases of data splitting in both reading and writing operation, 
-\end{comment}
-%\subsubsection{Node Migration}
-%Node migration happens when some nodes have to be shut down due to some situation like power problem in summer, and still need to provide service to users.
-%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.
-
-%However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
-%When using I/O buffer nodes
-
-\section{I/O Burst Buffer Model}
-
-%\begin{figure}[tb]
-%	\centering
-%	\includegraphics
-%	\caption{definition}
-%	\label{definition}
-%\end{figure}
-
-Throughput-based Model, Cost-based Model and buffer queue write back model will be described in this section.
-Throughput-based Model compare one-side buffer throughput with two-side buffer, cost-based model compare one-side buffer cost with two-side buffer, and buffer queue write back model. 
-We make definitions shows in Table.~\ref{definition} in order to describe our model:
-\begin{table}[tb]
-	\caption{Definition of parameters}
-	\label{definition}
-\begin{tabular}{|p{3cm}|p{5cm}|}
-	\hline
-	$c_1,c_2$&Numbers of computing nodes in system 1 and system 2\\\hline
-	$n_1, n_2$&Numbers of I/O buffer nodes in system 1 and system 2.\\\hline
-	$m_1,m_2$&Available memory size for each I/O node in system 1 and 2, also the maximum buffer size will be $n_1\times m_1$ and $n_2\times m_2$\\\hline
-	$D_1(n_2),D_2(n_2)$&Throughput when $n_2$($n_1$) I/O nodes in system 1 (system 2) connect to storage in the other system directly, here we assume only I/O nodes in each system have Internet connection.\\\hline
-	$I(n_1,n_2)$& 	Internet throughput using $n_1,n_2$ I/O buffer nodes respectively, Since overall Internet throughput is affected by number of nodes involved in connection.\\\hline
-	$E_1(n_1), E_2(n_2)$&Interconnection network throughput in system 1 and 2, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes.\\\hline
-	%, it is difficult to compute each throughput, so here we use $E_1(n_1)$ to refer to limitation of maximum throughput of interconnection network in system 1 with $n_1$ I/O nodes, likely ,$E_2(n_2)$ is limitation of maximum throughput of interconnection network in system 2 with $n_2$ I/O nodes.
-	$M_1(n_1),M_2(n_2)$& Throughput of connection between storage and $n_1$ I/O nodes in system 1 and storage and $n_2$ I/O nodes in system 2.\\\hline
-	$C_1\_Money(T)$,$C_2\_Money(T)$& Cost for standard node in system 1 and 2 for $T$ time usage\\\hline
-	%and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, 
-	$C_1\_High\_Money(T)$,$C_2\_High\_Money(T)$& cost I/O nodes in system 1 and 2 for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
-\end{tabular}
-\end{table}
-
-\subsection{Throughput-based Model}
-%There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
-In the case of one-side buffer, there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
-\begin{equation}
-	\text{throughput}_{\text{one-side}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
-\end{equation}
-
-In the case of two-side buffer, there are three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{two-side}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
-\end{equation}
-
-In this throughput-based model, these two throughputs are evaluated, and a switch is based on these two values:
-
-\begin{equation}
-	\begin{cases}
-		\text{throughput}_{\text{one-side}} \geq \text{throughput}_{\text{two-side}} & \text{use one-side}\\
-		\text{throughput}_{\text{one-side}} < \text{throughput}_{\text{two-side}} & \text{use two-side}
-	\end{cases}
-\end{equation}
-
-\subsection{Cost-based Model}
-In the case of cost-based model, we consider
-using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:
-
-\begin{equation}
-	\begin{cases}
-		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{one-side}\\
-		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{two-side}
-	\end{cases}
-\end{equation}
-
-here we compute cost by using $T_1,T_2$:
-\begin{equation}
-	\text{cost}_\text{one-side}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
-\end{equation}
-\begin{align}
-	\text{cost}_\text{two-side}&=c_2\times C_2\_Money(T_2)\\\nonumber 
-				     &+n_1\times C_1\_High\_Money(T_2)\\ \nonumber
-				     &+n_2\times C_2\_High\_Money(T_2)
-\end{align}
-
-In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:
-
-\begin{equation}
-	\begin{cases}
-		\text{cost}_{\text{one-side}} \geq \text{cost}_{\text{two-side}} & \text{use one-side}\\
-		\text{cost}_{\text{one-side}} < \text{cost}_{\text{two-side}} & \text{use two-side}
-	\end{cases}
-\end{equation}
-
-%\subsection{}
-%\subsection{Migration Model}
-%Since there are some condition that some supercomputer nodes must be shut down, and jobs running on these nodes have to be migrate to another cloud. There are 
-%\begin{equation}
-%	Data	
-%\end{equation}
-\subsection{Buffer Queue Write Back Model}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{buffer_queue}
-	\caption{buffer queue}
-	\label{buffer queue}
-\end{figure}
-
-If the buffer size is unlimited. then we can buffer all data in the I/O buffer nodes, and achieve a high throughput in cloud burst.
-However buffer size can not be unlimited, we can not buffer all data in the I/O buffer nodes, data in buffer nodes have to be write back to storage in another system.
-The problem is which data should be written back to storage, like cache in cpu, if we can reduce cache miss in this situation, we can increase throughput. 
-According to data locality, we use a priority queue to determine which data should be write back.
-
-Consider Fig.~\ref{buffer queue}, assume average incoming throughput is A MB/s and average outgoing throughput is B MB/s, if A always larger than B, after $T$ time buffer queue will full.
-\[T=\frac{m_2\times n_2}{A-B}\]
-
-After that, since buffer queue is full, I/O server can not send more data to I/O buffer nodes, have to block any read and write request since that.
-In this case, jobs running on public cloud have to be moved back to original system until buffer queue is empty.
-
-\section{Evaluation}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=6cm]{}
-	\caption{throughput comparison with and without I/O burst buffer}
-	\label{throughput}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=6cm]{}
-	\caption{cost comparison with and without I/O burst buffer}
-	\label{cost}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{compress_rate}
-	\caption{compress rate}
-	\label{compress rate}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	\includegraphics[width=6cm]{compress_time}
-	\caption{compress time on TSUBAME V queue and AMAZON EC2}
-	\label{compress time}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=6cm]{}
-	\caption{throughput comparison with and without compress}
-	\label{compress}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics
-	\caption{cache hit and miss throughput comparison}
-	\label{cache hit}
-\end{figure}
-
-%\begin{figure}[tb]
-%	\centering
-%	\includegraphics[width=6cm]{tsubamelustre}
-%	\caption{TSUBAME Lustre workload}
-%	\label{Lustre workload}
-%\end{figure}
-
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region, using
-%m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
-m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}.
-Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{point to point connection LAB} ).
-%According to these data and definition described above, we use values defined below.
-
-%\begin{center}
-%\begin{tabular}[tb]{|c|c|}\hline
-%	$D_2$&$E_1$\\\hline
-%	8TB/s&1.08Gbit/s(135MB/s)\\\hline
-
-%\end{tabular}
-%\end{center}
-For throughput between two systems and inside system, from benchmark data, it shows it is hard to achieve a high throughput with only one nodes, and also there is a limit on maximum throughput between two systems and inside system.
-Although incresing nodes can increse throughput before reach the maximum, throughput achieved by each nodes decrease because of conflict.
-For these reason, we use following formular for throughput between two systems and inside system.
-%TSUBAME and AMAZON EC2, we use similar model in \cite{ccgrid}:
-\begin{equation}
-throughput=-Ax^2+Bx+C~~ A,B>0\\
-\end{equation}
-we use following equations to determine $A,B,C$
-\begin{equation}
-\begin{cases}
-	-A+B+C=throughput_{one}\\\nonumber
-	\frac{B}{2A}=n_{max}\\\nonumber
-	-An_{max}^2+Bn_{max}+C=throughput_{max}\\
-\end{cases}
-\end{equation}
-
-First, we compare throughput with and without I/O buffer nodes.
-Since it is hard for one node to fully utilize Internet and Ethernet bandwidth, according to Fig.~\ref{throughput AMAZON to OURLAB}, we assume that one node can achieve half of maximum bandwidth.
-We can see from Fig.~\ref{throughput}, when interconnection throughput is larger than Internet throughput, our I/O buffer can achieve a higher throughput.
-
-Then, we compare overall cost by using I/O burst buffer,
-
-we compare throughput with and without compression, Fig.~\ref{compress rate} shows compress and Fig.~\ref{compress time} shows compress and decompress time on TSUBAME V queue and AMAZON EC2 with a different compress level by using zlib\cite{zlib}.
-We can achieve a high compress rate, but the throughput is low, up to 160MB/s, depends on compress level, it is hard to find a compress library can compress data faster and smaller, so the compress throughput may become a bottleneck.
-On the other hand, the compress rate is high, since the buffer size is limited, if we can make data smaller, it means we can increase the buffer hit rate, Fig.~\ref{cache hit} shows a throughput comparison between cache miss and hit.
-
-Fig.~\ref{compress}
-\section{Conclusion and Future Work}
-
-In this paper, we propose a I/O burst buffer architecture to burst I/O throughput, provide throughput-based, cost-based and queue write back model, and provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
-we use several nodes in each system as a I/O buffer nodes, and use data buffering to hide the low throughput between two systems connected by Internet.
-
-From simulation result, we showed that our I/O burst buffer can increase I/O throughput when Internet throughput is far smaller than interconnection throughput as well as reducing the overall cost.
-
-For future work, we plan to implement this I/O burst buffer architecture.
 \bibliography{reference}

### 2014-06-30 paper/3_burst_buffer.tex
Splited paper.tex

\section{I/O Bursting Buffer Overview}

%\begin

An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system.
%the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
%Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
%Since public clouds also run virtual machine on physical nodes, in the follow section, we treat the set of supercomputer's virtual machines as a cloud environment, also because only a few public IP address available in each cloud, I/O buffer nodes are required even in direct connection model.

%Reading operation describes operations when issues reading data from another cloud storage, and writing operation describes operation when issues writing data to another cloud storage

%Migration operation occurs when some nodes have to be shut down in one cloud 
%all jobs running on these nodes have to be backed up by using snapshot,

\subsection{System Environment}
First a general system used in following sections is defined as follow:

%For security consideration and the fact that IPv4 addresses becomes rare,
\begin{itemize}
	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
\end{itemize}

\subsection{I/O Burst Buffer Architecture}

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{IOserver}
	\caption{I/O server and buffer queue}
	\label{I/O server}
\end{figure}

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{overview}
	\caption{overall illustrate of I/O Burst Buffer Architecture}
	\label{overview}
\end{figure}

%Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assigned only  and I/O burst buffer nodes, which assigned both private IP address.

Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.

When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are allocated in the same system, so data consistency can be guaranteed since that.
Buffer queue operation including data write back and operation when queue is full will be described in following section.

When user issue a read request, there are two conditions: file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
If data is not in buffer queue, then a read operation described below will be executed, since data must be transferred from storage in another system, in this case, throughput will depend on Internet condition and it is hard to achieve a high throughput.

Fig.~\ref{overview} shows a overall illustrate of I/O burst buffer architecture.

%Consider there are two systems, named system 1 and system 2

%Arrows stand for network connection.
%Orange arrows are interconnection networks inside cloud, although two clouds used the same color for interconnection networks, bandwidth can be different, also the topolopies are not specified and can be different in each cloud.
%Black arrows are Internet connections, since there are a few amount of public IP addresses available, only I/O buffer nodes are connect to Internet, also the amount of available public IP address becomes the upper bound of the amount of I/O buffer nodes in each cloud. 
%Although nodes with private IP address can use route or other net device to connect to Internet, but consider about security problem, also using route will reduce concurrent data transfer rate, here we assume all nodes in cloud only connect to local private network except I/O buffer nodes which connect to both local network and Internet.

%Circles stand for computing nodes, which are used for standard computation.
%Here we assume all computing nodes can communicate with each other, and also I/O buffer nodes and shared storage in the same cloud environment.
%Squares are I/O buffer nodes, these nodes are used for data transfer between clouds, and are assigned with both public and private IP addresses.
%I/O buffer nodes can use the same machine or VM as computing nodes, or can use network optimized nodes for larger throughput, but it is not required here.
%Cylinders are shared storages, which are used to store data used by computing nodes, usually shared storage is consist of several nodes with a distributed filesystem and uses a better network, offers a large throughput.

%Since there is a big gap between cloud inside data transferring and accross two clouds in throughput, our goal is to fill the gap.

%For convenience, in the following section we assume data is stored in Cloud 1's shared storage, and computing nodes in Cloud 2 are used for computation.

%in this subsection, we introduce operations of buffer queue write back.

\subsection{Read and Write}

\begin{figure}[tb]
	\centering
	\includegraphics[width=6cm]{read_and_write}
	\caption{read and write operation}
	\label{read and write}
\end{figure}

In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
We propose two kinds of model: one-side buffer and two-side buffer.

\subsubsection{One-side Buffer}

As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
When I/O nodes need to write data back to storage in another system, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.

Similarly, when I/O nodes need to read data from storage in another system, several I/O nodes will be assigned equal size of data, and then these nodes read assigned piece of data from the storage concurrently.

There will be two problems in this solution:
\begin{itemize}
	\item First storage should be opened to Internet, in order that I/O nodes can read from or write to it.
		However storage system in supercomputer store Petabyte of research data, open the access of storage system means that put these research data under risk of attack.
	\item As we mentioned before, throughput of one side communication is lower than two side communication, since we use SSH protocol based File system for security reason.
		also two side communication can achieve a higher throughput with fewer nodes, according to pay-as-you-go policy, reduce number of nodes can reduce cost.
\end{itemize}
%data firstly be splitted into number of I/O buffer nodes in cloud 2 pieces and assign one I/O buffer node one piece, then I/O buffer nodes start reading assigned data concurrently in order to fully utilize Internet bandwidth.
%After reading finished, I/O buffer nodes send data to each computing node Simultaneously, there data will be restructure by using protocol described below.

%Like reading, when computing nodes start to output data, first data will be buffered inside that nodes.
%After output finished, data will be splitted into number of I/O buffer nodes in cloud 2 pieces, and assign one I/O node one piece, then data will be sent to all I/O buffer nodes concurrently.
%When I/O buffer nodes received data, then they writing data back to storage in cloud 1.

\subsubsection{Two-side Buffer}

On the contrary, two-side buffer solution use I/O buffer nodes in both two systems as Fig.~\ref{read and write} orange arrows show.
I/O data will be split twice, transferred throughput two sides of I/O buffer nodes and then reached the destination.

Consider I/O nodes in system 2 issue a write back operation, also, data is already spread among I/O nodes in system 2, each I/O node will find a pair among I/O nodes in system 1, then transfer their piece of data to system 1 concurrently.
After I/O node in system 1 received data, they write data back to storage in system 1.

Compared with one-side buffer, two-side buffer required one more data transfer (I/O nodes to storage in the same system), if storage data transfer throuhput become a bottleneck, two-side buffer will cost more time than one-side buffer.
Also, two-side buffer require both systems allocate I/O buffer nodes, if node usage is charge in both system, total cost may be larger than one-side buffer.

%the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
Since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.

%I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.

%When computing nodes issue read request, first we check whether the file has been cached in I/O buffer nodes in cloud 1, if not, File will be splitted into the same number of I/O buffer nodes in cloud 1, and each I/O buffer node will be assigned a piece of split, then all I/O buffer nodes start reading assigned piece of data from shared storage simultaneously to fully utilize the bandwidth.% I/O buffer nodes use a main index to refer to the data position in global data.

%After transferring data from shared storage finished, I/O buffer nodes in cloud 1 will connect with all I/O buffer nodes in cloud 2, then split data piece and into number of I/O buffer nodes in cloud 2,
%here a sub-index is used to refer to each piece's position, 
%then transfer these pieces to I/O buffer nodes in cloud 2 concurrently in order to fully utilize Internet bandwidth.

%When data transfer finished, I/O buffer nodes connect with all computation nodes which needs data, then transfer data to the corresponding position by using a index protocol described below, of cause all data transfer are done in parallel.

%Data writing operation doing the opposite operation as reading operation.
%When a computing node in cloud 2 issues data writing, output data will be first buffered by I/O server in that node.
%After output finished, I/O server connects with all I/O buffer nodes in the same cloud, and split output data into the number of I/O buffer nodes, then send each piece of data to each I/O buffer nodes Simultaneously.

%I/O buffer nodes then again split data into the number of I/O buffer nodes in cloud 1, like reading operation, here sub-index is used to refer to data position. and then start to transfer data concurrently.

%Then I/O buffer nodes write data to storage in cloud 1.

\begin{comment}
\subsubsection{Index Protocol}

\begin{figure}[tb]
	\centering
%	\includegraphics
	\caption{index protocol}
	\label{index protocol}
\end{figure}

As Fig.~\ref{index protocol} shows, two indexs are used in this protocol: main index and sub-index.
There are two phases of data splitting in both reading and writing operation, 
\end{comment}
%\subsubsection{Node Migration}
%Node migration happens when some nodes have to be shut down due to some situation like power problem in summer, and still need to provide service to users.
%In these cases, nodes will be migrate by snapshot, usually snapshots of these nodes will first be stored into shared storage, then these snapshots will be transferred to another cloud, and start VM by using these snapshots.

%However, the low throughput between direct connection of nodes and storage in different environment will still be a bottleneck for quick migration.
%When using I/O buffer nodes

### 2014-06-30 paper/5_evaluation.tex
Splited paper.tex

--- 2014-06-27 paper/section/evaluation.tex
@@
 \section{Evaluation}
+
+\begin{figure}[tb]
+	\centering
+	%\includegraphics[width=6cm]{}
+	\caption{throughput comparison with and without compress}
+	\label{compress}
+\end{figure}
+
+\begin{figure}[tb]
+	\centering
+	%\includegraphics
+	\caption{cache hit and miss throughput comparison}
+	\label{cache hit}
+\end{figure}
 

### 2014-06-30 paper/src/1_introduction.tex
Changed directory stractures

--- 2014-06-27 paper/section/introduction.tex
@@
-\begin{abstract}
-%Parallel programming are used to reduce execution time of complex problems, also fully utilizing computing resource of Supercomputers.
-
-%supercomputers usually consist of a large number of nodes, provide high parallelism for multi-user.
-%However computing nodes in supercomputers will not meet the request in some situation, such as some nodes have to be shut down to reduce electric consumption in summer or just several serial applications occupy nodes making others must wait.
-%large serial applications will occupy computation nodes for a long time and causes some other applications which use numerous nodes to wait in a running queue, leads a low utilization of computing resource.
-%One solution is running virtual machine on 
-%In this paper, a comparison was made between a Public Cloud (AMAZON EC2) and a Supercomputer (TSUBAME) on Ethernet Performance and leading a 
-%In order to satisfy these temporary request peak, we are trying to federate supercomputers with public cloud, which is known as cloud bursting.
-%Although some sophisticated solutions are available, still we are facing several challenges, since there are a significant performance gap between supercomputers and public cloud.
-%In this paper, we focus on I/O throughput between these two environments, we propose a I/O Bursting Buffer Model to burst I/O throughput between supercomputer and public cloud and reduce the cost for extra time usage caused by low I/O throughput.
-%we also provide a simulation based on several benchmarks on TSUBAME supercomputer and AMAZON EC2 public cloud.
-%The result shows our model can provide a stable and high I/O throughput as well as a low cost in most cases.
-
-Extreme-scale HPC systems, which consist of a large number of compute nodes, can provide high computational capacity for multiple users.
-However, computing nodes in the systems occasionally can not meet the demand due to bursty job requests in short period times.
-In order to accommodate the bursty requests, we consider federating HPC systems with public clouds, which is known as cloud bursting.
-Although the federated systems can acquire virtually infinite computational power with cloud bursting, the QoS may not be guaranteed due to a significant performance gap between HPC systems and public clouds.
-The most critical problem is a gap in I/O performance.
-In this paper, we propose an I/O acceleration technique using distributed cloud bursting buffers.
-We also create the I/O performance model to explore the effectiveness.
-Our model-based simulations, which target the TSUBAME supercomputer for an HPC system, and AMAZON EC2 for a public cloud, show that the distributed cloud busting buffer can improve I/O throughput while reducing the cost.
-
-\end{abstract}
-
-\begin{keyword}
-Supercomputer, Cloud, I/O Bursting Buffer Model
-\end{keyword}
-
-\maketitle
-
-%1
 \section{Introduction}

### 2014-06-30 paper/src/2_motivation.tex
Changed directory stractures

--- 2014-06-27 paper/section/motivation.tex
@@
 	\centering
-	\includegraphics[width=6cm]{throughput_tsubame}
+	\includegraphics[width=6cm]{../img/throughput_tsubame}
 	\caption{I/O Throughput to Lustre inside TSUBAME direct mount}
@@
 	\centering
-	\includegraphics[width=6cm]{AMAZON_to_OUR_LAB}
+	\includegraphics[width=6cm]{../img/AMAZON_to_OUR_LAB}
 	\caption{I/O Throughput from AMAZON EC2 to file system inside our lab using sshfs}
@@
 	\centering
-	\includegraphics[width=6cm]{point_to_point_AMAZON}
+	\includegraphics[width=6cm]{../img/point_to_point_AMAZON}
 	\caption{point to point connection inside AMAZON}
@@
 	\centering
-	\includegraphics[width=6cm]{point_to_point_lab}
+	\includegraphics[width=6cm]{../img/point_to_point_lab}
 	\caption{point to point connection throughput between AMAZON and our lab}

### 2014-06-30 paper/src/1_introduction.tex
added makefile_kento

@@
 \section{Introduction}
-An increasing number of scientific applications are now running on Supercomputer for high performance computing nodes, large bandwidth and low latency interconnection environment, also a great number of processors for high scalability.
+Supercomputers provide an increasing number of scientific applications with  high computational power by a large number of processors, large bandwidth memory and low leatency interconnects.
 %Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
-
 %Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-Although supercomputer can offer a high computational cpacity, there are some situations HPC system can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
+Although supercomputers can offer the high computational power, there are several situations where a supercomputer can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
 %high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
@@
 
-One solution is federating supercomputer with a public cloud, moving parts of job and computation to public cloud when there are not enough computing nodes available for user's request, which is known as cloud bursting.
-Although cloud bursting is used by several companies and already have some sophisticated solutions\cite{Eucalyptus,stratos,Seagull}, since there are a significant performance gap between supercomputer nodes and cloud nodes, there will still be several problems when we try to federate a supercomputer with a public cloud, and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
-The biggest problem will be data transfer throughput between two environment, supercomputers usual deal with Gigabyte or even Petabyte input and output of data, low I/O throughput will suffer supercomputer user.
-This paper focuses on methodology of increasing throughput when we do federation.
+One solution is federating a supercomputer with a public cloud,
+and moving a part of jobs to the public cloud when there are not enough
+computing nodes available for user's requests, which is known as \emph{cloud bursting}.
+Although cloud bursting is technically feasible~\cite{Eucalyptus,stratos,Seagull}, 
+and is employed by several private companies, 
+there is a significant performance gap between supercomputers and clouds, 
+there will still be several problems when we try to federate a supercomputer with a public cloud, 
+and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
+The biggest problem will be data transfer throughput between two environment, 
+supercomputers usual deal with Gigabyte or even Petabyte input and output of data, 
+low I/O throughput will suffer supercomputer user. This paper focuses on methodology 
+of increasing throughput when we do federation.
 
-In order to increase data transfer throughput, we propose a I/O burst buffer architecture that uses several nodes in each system as a I/O nodes to achieve high throughput concurrent data transferring, and a I/O burst buffer model that uses to switch between I/O burst buffer mode and direct connect mode.
+In this paper, we propose an I/O burst buffer architecture that uses multiple nodes in each system as an I/O nodes 
+to achieve high throughput concurrent data transferring, and an I/O burst buffer model 
+that uses to switch between I/O burst buffer mode and direct connect mode.
 %This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
 %Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
-Also, public cloud usually charges for nodes usage, using I/O bursting buffer may reduce the computation time, but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.
+Also, public cloud usually charges for nodes usage, I/O bursting buffers may reduce the computation time, 
+but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.
 
-Our contribution can be summary as following:
+Our contributions can be summrized as following:
 \begin{itemize}

### 2014-06-30 paper/src/1_introduction.tex
added new command to paper.tex, and update on intro

@@
 \begin{itemize}
-	\item An architecture of I/O burst buffer for increasing data transfer throughput between two systems.
-	\item A throughput-based I/O burst buffer model uses to switch between I/O bursting mode and direct connection mode in order to achieve a high data transfer when federating two systems, a cost-based I/O burst buffer model uses to reduce the total cost and a queue model used.
-	%\item 
+	\item A cloud-based burst buffer for increasing data transfer throughput between two systems;
+	\item A throughput-based I/O burst buffer model, which estimate I/O throughput of systems with I/O burst buffers, and a cost-based I/O burst buffer model, which estimate overall cost give a system configuration;
         \item Evaluating I/O burst buffer architecture and two models by using data obtained from several benchmarks from TSUBAME supercomputer and AMAZON EC2 public cloud.

### 2014-06-30 paper/src/1_introduction.tex
several updates

@@
 \section{Introduction}
+\label{sec:introduction}
 Supercomputers provide an increasing number of scientific applications with high computational power by a large number of processors, large bandwidth memory and low leatency interconnects.
@@
 but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.
-
+\kento{please summirize the evaluation resutls here.}
 Our contributions can be summrized as following:
@@
 	\item A throughput-based I/O burst buffer model, which estimate I/O throughput of systems with I/O burst buffers, and a cost-based I/O burst buffer model, which estimate overall cost give a system configuration;
-        \item Evaluating I/O burst buffer architecture and two models by using data obtained from several benchmarks from TSUBAME supercomputer and AMAZON EC2 public cloud.
+        \item Evaluation of the I/O burst buffer architecture based the performance models by using real data obtained from several benchmarks from the TSUBAME supercomputer and AMAZON EC2.
 \end{itemize}
 %2
-The remainder of this paper is organized as follow:in section 2, the motivation and background of this study will be introduced, a overview of I/O bursting buffer Architecture including direct connection and I/O bursting buffer will be introduced in section 3, and the model used to switch between two modes will be described in section 4, a simulation result of our model %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2
-will be shown in section 5, and finally, conclusion and related work will be seen in section 6.
+The remainder of this paper is organized as follow. 
+In Section \ref{sec:motivation}, we clarify the motivation and the background.
+We introduce an overview of the I/O bursting buffer architecture in Section \ref{sec:burst_buffer}, 
+and show the performance models to evaluate the I/O bursting buffer architecture in Section \ref{sec:model}. 
+In Section \ref{sec:evaluation}, we present our experimental results based of our perfomrance models. %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2 
+Finally, we detail related work in Section \ref{sec:related_work}, and conclusion in Section \ref{sec:conclusion}.

### 2014-06-30 paper/src/4_model.tex
Changed directory stractures
modify 4_model

--- 2014-06-27 paper/section/model.tex
@@
 Throughput-based Model, Cost-based Model and buffer queue write back model will be described in this section.
-Throughput-based Model compare one-side buffer throughput with two-side buffer, cost-based model compare one-side buffer cost with two-side buffer, and buffer queue write back model. 
-We make definitions shows in Table.~\ref{definition} in order to describe our model:
+As we explained in the previous section, two-side buffer model is better than one-side buffer model, in the following section, we will use two-side buffer model as our read from and write back model in I/O burst buffer.
+
+Throughput-based Model compares throughput with and without I/O burst buffer, cost-based model compare cost with and without I/O burst buffer, and buffer queue write back model shows the situation that I/O buffer queue will be full.
+We make definitions shows in \tabref{definition} in order to describe our model.
 \begin{table}[tb]
@@
 	$m_1,m_2$&Available memory size for each I/O node in system 1 and 2, also the maximum buffer size will be $n_1\times m_1$ and $n_2\times m_2$\\\hline
-	$D_1(n_2),D_2(n_2)$&Throughput when $n_2$($n_1$) I/O nodes in system 1 (system 2) connect to storage in the other system directly, here we assume only I/O nodes in each system have Internet connection.\\\hline
-	$I(n_1,n_2)$& 	Internet throughput using $n_1,n_2$ I/O buffer nodes respectively, Since overall Internet throughput is affected by number of nodes involved in connection.\\\hline
+	$D_1(n_2),D_2(n_2)$&Throughput when $n_2$($n_1$) I/O nodes in system 1 (system 2) connect to storage in the other system directly, here we assume I/O nodes and computing nodes in each system have the same Internet connection speed.\\\hline% have Internet connection.\\\hline
+	$I(n_1,n_2)$& 	Internet throughput using $n_1,n_2$ nodes respectively, since overall Internet throughput is affected by number of nodes involved in connection.\\\hline
 	$E_1(n_1), E_2(n_2)$&Interconnection network throughput in system 1 and 2, although interconnection throughput is also affected by numbers of I/O nodes and computing nodes, numbers of users will running application on different number of computing nodes.\\\hline
@@
 	$M_1(n_1),M_2(n_2)$& Throughput of connection between storage and $n_1$ I/O nodes in system 1 and storage and $n_2$ I/O nodes in system 2.\\\hline
-	$C_1\_Money(T)$,$C_2\_Money(T)$& Cost for standard node in system 1 and 2 for $T$ time usage\\\hline
+	$C_i\_Money(T)$& Cost for standard node in system $i$ for $T$ time usage\\\hline
 	%and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, 
-	$C_1\_High\_Money(T)$,$C_2\_High\_Money(T)$& cost I/O nodes in system 1 and 2 for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
+	$C_i\_High\_Money(T)$ &I/O nodes in system $i$ for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
 \end{tabular}
@@
 %There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
-In the case of one-side buffer, there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
+In the case of direct I/O, computing nodes connect to storage in another system directly, there is only one data transfer, so throughput will be:%there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
 \begin{equation}
-	\text{throughput}_{\text{one-side}}=\min\{D_1(n_2),E_2(n_2)\} \label{throughput1}
+	\text{thr}_{\text{direct}}=D_1(c_2) \label{throughput1}
 \end{equation}
 
-In the case of two-side buffer, there are three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, throughput will be:
-
-\begin{equation}
-	\text{throughput}_{\text{two-side}}=\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} \label{throughput2}
-\end{equation}
+When using I/O burst buffer, there will be three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, throughput will be:
+\begin{eqnarray}
+	\text{thr}_{\text{I/O buffer}}=\\\begin{cases}
+		E_2(n_2) &\text{buffer queue available}\\ 
+	\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} &\text{buffer queue full}
+	\end{cases} \label{throughput2}
+\end{eqnarray}
 
@@
 	\begin{cases}
-		\text{throughput}_{\text{one-side}} \geq \text{throughput}_{\text{two-side}} & \text{use one-side}\\
-		\text{throughput}_{\text{one-side}} < \text{throughput}_{\text{two-side}} & \text{use two-side}
+		\text{thr}_{\text{direct}} \geq \text{thr}_{\text{I/O buffer}} & \text{use direct I/O}\\
+		\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}} & \text{use I/O burst buffer}
 	\end{cases}
@@
 \subsection{Cost-based Model}
-In the case of cost-based model, we consider
+In the case of cost-based model, we consider the overall cost for using direct I/O and using I/O burst buffer.
+Although using I/O burst buffer will cost for I/O nodes, higher throughput can reduce execution time and also overall cost.
 using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:
@@
 	\begin{cases}
-		T_1=\frac{1}{\min\{D_1(n_2),E_2(n_2)\}} & \text{one-side}\\
-		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{two-side}
+		T_1=\frac{1}{D_1(c_2)} & \text{direct}\\
+		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{buffer queue available}\\
+		T_3=\frac{1}{E_2(n_2)} &\text{buffer queue full}
 	\end{cases}
@@
 
-here we compute cost by using $T_1,T_2$:
+here we compute cost by using $T_1,T_2,T_3$:
 \begin{equation}
-	\text{cost}_\text{one-side}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
+	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
 \end{equation}
 \begin{align}
-	\text{cost}_\text{two-side}&=c_2\times C_2\_Money(T_2)\\\nonumber 
-				     &+n_1\times C_1\_High\_Money(T_2)\\ \nonumber
-				     &+n_2\times C_2\_High\_Money(T_2)
+	\text{cost}_\text{I/O buffer}=\\\begin{cases}
+				c_2\times C_2\_Money(T_2)+n_1\times C_1\_High\_Money(T_2)+n_2\times C_2\_High\_Money(T_2)&\text{buffer queue available}\\
+				c_2\times C_2\_Money(T_3)+n_1\times C_1\_High\_Money(T_3)+n_2\times C_2\_High\_Money(T_3) &\text{buffer queue full}
+\end{cases}
 \end{align}
 
-In this throughput-based model, these two throughput are evaluated, and a switch is based on these two values:
-
+In this cost-based model, these two cost are evaluated, and a switch is based on these two values:
 \begin{equation}
 	\begin{cases}
-		\text{cost}_{\text{one-side}} \geq \text{cost}_{\text{two-side}} & \text{use one-side}\\
-		\text{cost}_{\text{one-side}} < \text{cost}_{\text{two-side}} & \text{use two-side}
+		\text{cost}_{\text{direct}} \geq \text{cost}_{\text{I/O buffer}} & \text{use direct I/O}\\
+		\text{cost}_{\text{direct}} < \text{cost}_{\text{I/O buffer}} & \text{use I/O burst buffer}
 	\end{cases}
@@
 	\centering
-	\includegraphics[width=6cm]{buffer_queue}
+	\includegraphics[width=6cm]{../img/buffer_queue}
 	\caption{buffer queue}

### 2014-06-30 paper/src/2_motivation.tex
Added comments in motication section, updated paper.tex for building

@@
-\section{Motivation and Background}
+\section{Background and Motivation}
+\label{sec:motivation}
+\subsection{Public Cloud}
+\label{sec:public_cloud}
+\kento{Please explain what Public cloud is with example of Amazon EC2. Then, the details which is needed to mention for readers understand the rest of the sections.
+  (1-1) Architecture (VM environment \& datacetners are geographically distributed)
+  (1-2) Explain instance types which is related to this paper. Current draft does not mention any instance types.
+  (1-3) introduce pay-as-you-go model to help readers understand the cost-based model in the modeling section 
+  (1-4) [please add whatever you think it's needed]}
+
+\subsection{Federation between supercomputers and clouds}
+\kento{Please explain (2-1) how we federate supercomputers with clouds. $=>$ Virtualize supercomputer (e.g. TSUBAME V) + VM on clouds. 
+                      (2-2) what the advantages are. $=>$ VMs can provide the same execution environment on both supercomputers and clouds
+                      (2-3) [please add whatever you think it's needed]}
+
+\subsection{Challenges in Federation with clouds}
+\label{sec:problems}
+\kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
+                        (3-2) Then, please briefly clarfy why ``(A) cloud-based burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
+                              (Remember we knew that cloud-based burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
+                        (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
+                              In addtion, the choice of instances, the trade-offs are changes depending on given a supercomputer and cloud environments, such as network throughput, PFS performance. 
+                              That's why the ``(B) perfomrance modeling`` is important}
+
+\kento{Then, in the rest of the section, we explain (A) and (B)}
+
+\subsection{(Current Section 2)}
+\kento{Please fit the below sentences to the above sections with additional explanations}
+
+\begin{table}[h]
+\caption{\small XXXXX specification}
+\label{tbl:spec}
+\begin{center}
+\begin{tabular}{|c|l|}
+  \hline
+  \cellcolor{lightgray} CPU   & Intel Core i7-3770K CPU (3.50 GHz x 4 cores)\\
+  \hline
+  \cellcolor{lightgray} Memory   & Cetus DDR3-1600 (16 GB)    \\
+  \hline
+  \cellcolor{lightgray} M/B   & GIGABYTE GA-Z77X-UD5H \\
+  \hline
+  \cellcolor{lightgray} SSD          & Crucial m4 CT256M4SSD3 (256GB,
+  mSATA)\\
+  \cellcolor{lightgray}             & (Peak read:500 MB/s, Peak write: 260
+MB/s)
+             \\
+             \hline
+             \cellcolor{lightgray} SATA converter & KOUTECH IO-ASS110 mSATA to 2.5' SATA  \\
+             \cellcolor{lightgray}& Device Converter with Metal Frame \\
+             \hline
+             \cellcolor{lightgray} RAID Card    & Adaptec ASR-7805Q Single\\
+             \hline
+
+\end{tabular}
+\end{center}
+\end{table}
+% vector figures
+% Fig. 4 does not have a frame
+% write machine spec
 
@@
 
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
+Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes \kento{Describe node specification in Table I}, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
 On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
@@
 %Also, if we compare the one nodes I/O throughput, 
-Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput 
+Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput \kento{??}
 If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.

### 2014-06-30 paper/src/3_burst_buffer.tex
Changed directory stractures
several updates
Updated 3_burst_buffer

--- 2014-06-30 paper/3_burst_buffer.tex
@@
 \section{I/O Bursting Buffer Overview}
+% Why I/O server in client nodes
+\label{sec:burst_buffer}
 
@@
 As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system.
+The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system
+\kento{how about read ?}.
 %the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
@@
 
-\subsection{System Environment}
-First a general system used in following sections is defined as follow:
-
+\subsection{Assumptions}
+First, we make several assumptions for the federated environments as follows.
 %For security consideration and the fact that IPv4 addresses becomes rare,
@@
 	\centering
-	\includegraphics[width=6cm]{IOserver}
+	\includegraphics[width=6cm]{../img/IOserver}
 	\caption{I/O server and buffer queue}
@@
 	\centering
-	\includegraphics[width=6cm]{overview}
+	\includegraphics[width=6cm]{../img/overview}
 	\caption{overall illustrate of I/O Burst Buffer Architecture}
@@
 	\centering
-	\includegraphics[width=6cm]{read_and_write}
+	\includegraphics[width=6cm]{../img/read_and_write}
 	\caption{read and write operation}

### 2014-06-30 paper/src/4_model.tex
4_model
Added comments in 4_model.tex

@@
 \section{I/O Burst Buffer Model}
-
+\label{sec:model}
+\kento{First, again mention why the modeling is important for reminder}
 %\begin{figure}[tb]
@@
 
-Throughput-based Model, Cost-based Model and buffer queue write back model will be described in this section.
-As we explained in the previous section, two-side buffer model is better than one-side buffer model, in the following section, we will use two-side buffer model as our read from and write back model in I/O burst buffer.
+The throughput-based model, cost-based model and buffer queue write back model are described in this section.
+As we explained in the previous section, two-side buffer model is better than one-side buffer model, in the following section, we will use two-side buffer model as our read from and write back model in I/O burst buffer
+\kento{this sentences should be in the previsou section}.
 
-Throughput-based Model compares throughput with and without I/O burst buffer, cost-based model compare cost with and without I/O burst buffer, and buffer queue write back model shows the situation that I/O buffer queue will be full.
-We make definitions shows in \tabref{definition} in order to describe our model.
+The throughput-based model compares throughput with and without I/O burst buffer, cost-based model compare cost with and without I/O burst buffer, and buffer queue write back model shows the situation that I/O buffer queue will be full.
+We make definitions shows in Table \ref{definition} in order to describe our model.
 \begin{table}[tb]
@@
 %There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
-In the case of direct I/O, computing nodes connect to storage in another system directly, there is only one data transfer, so throughput will be:%there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
+In the case of direct I/O \kento{What is direct I/O.
+I think it means direct connection mode in Section 3, but no explanation at all}, computing nodes connect to storage in another system directly, there is only one data transfer, so throughput \kento{read ?
+or write ?
+or both ?} will be:%there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
 \begin{equation}
@@
 
-When using I/O burst buffer, there will be three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, throughput will be:
+When using I/O burst buffer, there will be three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, throughput \kento{write ?
+and read ?.
+Explain how the buffer queue works (1) if buffer space is avaialble for write, (2) reading data is in the buffer queue.
+We need expian this in both previous section and in here} will be:
 \begin{eqnarray}
-	\text{thr}_{\text{I/O buffer}}=\\\begin{cases}
+	\text{thr}_{\text{I/O buffer}}=\begin{cases}
 		E_2(n_2) &\text{buffer queue available}\\ 
@@
 In this throughput-based model, these two throughputs are evaluated, and a switch is based on these two values:
-
+\kento{Why do you swithches between direct I/O and burst buffer?}
 \begin{equation}
@@
 
+\kento{Mention how do you switch between I/O burst buffers and direct I/O.
+Will you dynamically shutdown/boot burst buffer nodes on demain ?.
+If so, please explain so, but there is a time lag before shutdown/boot are completed.
+So say somthing like "We will solve the problem in future work'' or else}
+
 \subsection{Cost-based Model}
+\kento{Again, it's hard to understand due to lack of information. Please read carfully over and over again and add more explanation like in the above}
 In the case of cost-based model, we consider the overall cost for using direct I/O and using I/O burst buffer.
@@
 \end{equation}
+\kento{According to the difinition of $C_i\_Money(T)$ and $T_i$, the above model seems to be wrong. Please read carfully the model is correct}
 \begin{align}
@@
 \end{equation}
+
+\kento{I'm workding if the throuput is 	$\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}}$ the cost is $\text{cost}_{\text{direct}} \geq \text{cost}_{\text{I/O buffer}}$, which do you use, direct I/O and I/O buffer.}
 
@@
 
-If the buffer size is unlimited. then we can buffer all data in the I/O buffer nodes, and achieve a high throughput in cloud burst.
+If the buffer size is unlimited.
+then we can buffer all data in the I/O buffer nodes, and achieve a high throughput in cloud burst \kento{Good work !!
+As I said in the different sections, it's important to remind its motivation before describing the algorithm, techniques, model, or methods for its reminder}.
 However buffer size can not be unlimited, we can not buffer all data in the I/O buffer nodes, data in buffer nodes have to be write back to storage in another system.
@@
 After that, since buffer queue is full, I/O server can not send more data to I/O buffer nodes, have to block any read and write request since that.
-In this case, jobs running on public cloud have to be moved back to original system until buffer queue is empty.
+In this case, jobs running on public cloud have to be moved back to original system until buffer queue is empty
+\kento{Why ??}.

### 2014-06-30 paper/src/2_motivation.tex
0701

@@
 \label{sec:public_cloud}
-\kento{Please explain what Public cloud is with example of Amazon EC2. Then, the details which is needed to mention for readers understand the rest of the sections.
-  (1-1) Architecture (VM environment \& datacetners are geographically distributed)
-  (1-2) Explain instance types which is related to this paper. Current draft does not mention any instance types.
-  (1-3) introduce pay-as-you-go model to help readers understand the cost-based model in the modeling section 
-  (1-4) [please add whatever you think it's needed]}
-
-\subsection{Federation between supercomputers and clouds}
-\kento{Please explain (2-1) how we federate supercomputers with clouds. $=>$ Virtualize supercomputer (e.g. TSUBAME V) + VM on clouds. 
-                      (2-2) what the advantages are. $=>$ VMs can provide the same execution environment on both supercomputers and clouds
-                      (2-3) [please add whatever you think it's needed]}
-
-\subsection{Challenges in Federation with clouds}
-\label{sec:problems}
-\kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
-                        (3-2) Then, please briefly clarfy why ``(A) cloud-based burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
-                              (Remember we knew that cloud-based burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
-                        (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
-                              In addtion, the choice of instances, the trade-offs are changes depending on given a supercomputer and cloud environments, such as network throughput, PFS performance. 
-                              That's why the ``(B) perfomrance modeling`` is important}
-
-\kento{Then, in the rest of the section, we explain (A) and (B)}
-
-\subsection{(Current Section 2)}
-\kento{Please fit the below sentences to the above sections with additional explanations}
-
-\begin{table}[h]
-\caption{\small XXXXX specification}
-\label{tbl:spec}
-\begin{center}
-\begin{tabular}{|c|l|}
-  \hline
-  \cellcolor{lightgray} CPU   & Intel Core i7-3770K CPU (3.50 GHz x 4 cores)\\
-  \hline
-  \cellcolor{lightgray} Memory   & Cetus DDR3-1600 (16 GB)    \\
-  \hline
-  \cellcolor{lightgray} M/B   & GIGABYTE GA-Z77X-UD5H \\
-  \hline
-  \cellcolor{lightgray} SSD          & Crucial m4 CT256M4SSD3 (256GB,
-  mSATA)\\
-  \cellcolor{lightgray}             & (Peak read:500 MB/s, Peak write: 260
-MB/s)
-             \\
-             \hline
-             \cellcolor{lightgray} SATA converter & KOUTECH IO-ASS110 mSATA to 2.5' SATA  \\
-             \cellcolor{lightgray}& Device Converter with Metal Frame \\
-             \hline
-             \cellcolor{lightgray} RAID Card    & Adaptec ASR-7805Q Single\\
-             \hline
-
-\end{tabular}
-\end{center}
-\end{table}
-% vector figures
-% Fig. 4 does not have a frame
-% write machine spec
-
-%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
-%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
-%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
-%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
-%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
-%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
-%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
-%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shut down to reduce electricity consumption in the case of TSUBAME Supercomputer.
-%Facing these problems, one solution will be federate supercomputer with public cloud.
-%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
-%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
-
-%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
 \begin{figure}[tb]
@@
 
-As we know, throughput gap between interconnection network and Internet is extremely large, also numbers of I/O nodes will affect I/O performance.
+\begin{table}[h]
+\caption{\small TSUBAME thin node specification}
+\label{tbl:spec}
+\begin{center}
+\begin{tabular}{|c|l|}
+  \hline
+  \cellcolor{lightgray} CPU      & Intel Xeon 2.93GHz CPU (4 cores)*2\\
+  %(Hyperthreading enabled)\\
+  \hline
+  \cellcolor{lightgray} Memory   & 54GB (16 GB)    \\
+  \hline
+  \cellcolor{lightgray} SSD      & 120GB \\
+  \hline
+  \cellcolor{lightgray} GPU	 & NVIDIA Tesla K20X *3\\
+  \hline
+  \cellcolor{lightgray} Network  & QDR InfiniBnd *2 (80Gbps)\\
+  \hline
+\end{tabular}
+\end{center}
+\end{table}
+
+\kento{Please explain what Public cloud is with example of Amazon EC2. Then, the details which is needed to mention for readers understand the rest of the sections.
+  (1-1) Architecture (VM environment \& datacetners are geographically distributed)
+  (1-2) Explain instance types which is related to this paper. Current draft does not mention any instance types.
+  (1-3) introduce pay-as-you-go model to help readers understand the cost-based model in the modeling section 
+  (1-4) [please add whatever you think it's needed]}
+Public cloud is one in which the services and infrastructure such as applications and storage are provided off-site over the Internet.
+Among many public cloud, Amazon Elastic Compute Cloud (Amazon EC2) is one of the most famous one, like other public cloud, Amazon EC2 privde VM computing nodes, distributed to several geographic regions.
+Amazon EC2 provide a large amount of instance types optimized to fit different use cases comprise varying combinations of CPU, memory, storage, and networking capacity.
+In this study, we used general purpose m3.xlarge instance which has 4 vCPUs, 15GiB memory, 2*80GB SSD storage and high level Ethernet network condition in Tokyo region, we run Amazon Linux AMI 2014.03.2 (HVM), which is based on Linux 3.10 on these instances.
+About pricing, Amazon use a pay-as-you-go pricing policy, which means you pay only for what you use, there is no minimum fee and you will pay for compute capacity by the hour with no long-term commitments.
+\subsection{Federation between supercomputers and clouds}
+\kento{Please explain (2-1) how we federate supercomputers with clouds. $=>$ Virtualize supercomputer (e.g. TSUBAME V) + VM on clouds. 
+                      (2-2) what the advantages are. $=>$ VMs can provide the same execution environment on both supercomputers and clouds
+                      (2-3) [please add whatever you think it's needed]}
+Since there is a significate performance gap between supercomputer computing nodes and public cloud computing nodes.
+We can not simply federate supercomputers with clouds, in order to get the same execution environment on both supercomputers and clouds, we virtualize supercomputer, e.g.
+TSUBAME V queue with VM on clouds.
+\subsection{Challenges in Federation with clouds}
+\label{sec:problems}
+\kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
+                        (3-2) Then, please briefly clarfy why ``(A) cloud-based burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
+                              (Remember we knew that cloud-based burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
+                        (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
+                              In addtion, the choice of instances, the trade-offs are changes depending on given a supercomputer and cloud environments, such as network throughput, PFS performance. 
+                              That's why the ``(B) perfomrance modeling`` is important}
+Although we virtualize supercomputer and obtain a similiar environment on both supercomputers and clouds, there are still several problems remains, for example, input data of applications running on supercomputer is usually stored in shared storages in the same system and can be read from and wrote to these storages with a extremely high throughput.
+
 We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
+Fig.~\ref{throughput TSUBAME} shows read and write throughput from TSUBAME V queue nodes (VM runing on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}) and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
+On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, which has about 1GBit/s Internet access.
+Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from Amazon.
+We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, which is limited by Internet bandwidth, about 40-80 times smaller than throughput inside TSUBAME.
 
-Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes \kento{Describe node specification in Table I}, which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
-On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 m3.medium nodes, which have moderate network performance, and a file system machine inside our lab, which has about 1GBit/s Internet access.
-Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from AMAZON.
-We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, about 40-80 times smaller than throughput inside TSUBAME.
+To solve this problem, we propose our cloud-based I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
+
+%when we try to move some jobs to public clouds after federation, the data 
+\kento{Then, in the rest of the section, we explain (A) and (B)}
+
+\subsection{(Current Section 2)}
+\kento{Please fit the below sentences to the above sections with additional explanations}
+
+% vector figures
+% Fig. 4 does not have a frame
+% write machine spec
+
+%When people analyze large size of data, parallel programme is widely used in order to reduce computation time, especially when using supercomputer.
+%However, it is usually difficult for a non-computer-scientist to write a parallel program, or re-write some existing applications into parallel version.
+%Many serial applications are submitted to Supercomputer and occupy computing nodes for a long time, causing other applications which offer large number of nodes to wait for nodes, and leading a low utilization of computing resource.
+%Consider following situation, there are 50 nodes available when a user submits a serial program using 1 node for 4 hours, after an hour a user try to run a program using 50 nodes, then he can't start his program until the first user finished his job.
+%Such situation happens frequently when thousands and hundreds of users using one system at the same time and leading a low utilization of computing resource.
+%One solution is running several virtual machines on a single physical machine for increasing utilization, which is used in TSUBAME Supercomputer, but sometime it still can't meet the request.
+%For request not always reaches peak, it is not wise to increase nodes just for a temporary request peak.
+%However even using virtual machines computing nodes still can't meet the request of users, for example, power problem will be critical in summer and nearly half of computing nodes have be shut down to reduce electricity consumption in the case of TSUBAME Supercomputer.
+%Facing these problems, one solution will be federate supercomputer with public cloud.
+%By using public cloud computing nodes just in request peak or when facing with power problem, people can save cost for buying new machines.
+%Of cause, there will be many challenges when Supercomputer federates with public cloud, such as security problems, using public cloud may cause research data opened to public, also connecting with Internet put Supercomputer under threats of hacker's attack.
+
+%Data shown in this section is taken from AMAZON EC2 m3.medium nodes, which have 3.75GiB memory and Moderate Network Performance and TSUBAME 2.5 V queue, which uses VM.
+
+%Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes \kento{Describe node specification in Table I}(VM runing on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}), which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
+%On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, which has about 1GBit/s Internet access.
 %From Fig.~\ref{throughput TSUBAME} and Fig.~\ref{throughput AMAZON to TSUBAME Lustre} we can see that the I/O throughput of interconnection inside supercomputer is quit larger than that from AMAZON.
 %Also, if we compare the one nodes I/O throughput, 
-Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput \kento{??}
-If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.
+%Also if we compare Fig.~\ref{point to point connection LAB} with Fig.~\ref{throughput AMAZON to OURLAB}, the maximum throughput \kento{??}
+%If we move some jobs to AMAZON EC2 with input data stored in TSUBAME Lustre, the execution time will increase because of I/O low throughput,for a data sensitive application, it will be devastating, also according to AMAZON's pay-as-you-go policy\cite{AMAZON_AWS}, longer execution time means more cost.
 
 %But when we compare Fig.~\ref{point to point connection TSUBAME} with FIg.~\ref{point to point connection AMAZON}, the interconnection throughput
+
+using I/O burst buffer requires addtional nodes running on public cloud and means more cost, also like Amazon EC2, public cloud usually provides various instance types with different specification, using which instance type also will affect both cost and performance.
+We provide a cost-based model to determine 
 However, if we consider interconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.

### 2014-06-30 paper/src/1_introduction.tex
modify 1,2,3

@@
 %Multi-user can use supercomputer at the same by using batch queue system which manage nodes and job submission.
-Although supercomputers can offer the high computational power, there are several situations where a supercomputer can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
+%Although supercomputers can offer the high computational power, there are several situations where a supercomputer can not satisfy user's demands even there are still some idle nodes, consider there are 50 nodes available, a user submit a serial application use only one node for an hour, after that, a job using 50 nodes is submitted, and have to wait until previous job finished although there are 49 nodes remainning available.
 %high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
+Although supercomputers can offer high capablity of computation, it is not unlimited, for some request peak, computation resource in supercomputer can not meet the needs of user, or simply user requesst more resource than supercomputers have, also some jobs require a exclusive usage for computing nodes, like grand challenge, will occpy a great amount of computation resource, leads inadequate of reourse for other job.
 Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down (peak shift in TSUBAME\cite{TSUBAME}), reducing numbers of nodes will make the first problem more serous.
@@
 The biggest problem will be data transfer throughput between two environment, 
-supercomputers usual deal with Gigabyte or even Petabyte input and output of data, 
+since we want to move some jobs from supercomputer to public cloud, I/O data need to transfer between these two system, supercomputers usual deal with Gigabyte or even Petabyte input and output of data,
 low I/O throughput will suffer supercomputer user. This paper focuses on methodology 

### 2014-06-30 paper/src/2_motivation.tex
modify 1,2,3

@@
   (1-4) [please add whatever you think it's needed]}
-Public cloud is one in which the services and infrastructure such as applications and storage are provided off-site over the Internet.
-Among many public cloud, Amazon Elastic Compute Cloud (Amazon EC2) is one of the most famous one, like other public cloud, Amazon EC2 privde VM computing nodes, distributed to several geographic regions.
+Public cloud is one in which the services and infrastructure such as applications and storage are provided off-site over the Internet, the main benefit of using a public cloud service are: easy fast and inexpensive set-up because hardware, application and bandwidth are covered by the provider, easy to scale to meet needs, no wasted resources because you pay for what you use.
+There are many companies provide public cloud solution like google, IBM, Microsoft etc., among them, Amazon Elastic Compute Cloud (Amazon EC2)\cite{AMAZON_AWS} is one of the most famous public cloud, like other public cloud, Amazon EC2 privdes Virtualize computing, and owns computing and data centers in several geographic regions.
 Amazon EC2 provide a large amount of instance types optimized to fit different use cases comprise varying combinations of CPU, memory, storage, and networking capacity.
 In this study, we used general purpose m3.xlarge instance which has 4 vCPUs, 15GiB memory, 2*80GB SSD storage and high level Ethernet network condition in Tokyo region, we run Amazon Linux AMI 2014.03.2 (HVM), which is based on Linux 3.10 on these instances.
-About pricing, Amazon use a pay-as-you-go pricing policy, which means you pay only for what you use, there is no minimum fee and you will pay for compute capacity by the hour with no long-term commitments.
+Amazon EC2 charges for nodes usage, Amazon use a pay-as-you-go pricing policy\cite{AMAZON_AWS}, which means you pay only for what you use, there is no minimum fee and you will pay for compute capacity by the hour with no long-term commitments.
 \subsection{Federation between supercomputers and clouds}
@@
                       (2-3) [please add whatever you think it's needed]}
-Since there is a significate performance gap between supercomputer computing nodes and public cloud computing nodes.
-We can not simply federate supercomputers with clouds, in order to get the same execution environment on both supercomputers and clouds, we virtualize supercomputer, e.g.
+When we try to federate supercomputer with public clouds, there are need to have a similiar performance and environment between these two systems.
+So we virtualize the supercomputer(like TSUBAME V queue) and federate VMs running on supercomputers with VMs provided by public cloud.
+By using VMs, we can run the same image on both supercomputer and public cloud as well as set both the same specification, and make it looks the same to user.%we can use in order to get the same execution environment on both supercomputers and clouds, we virtualize supercomputer, e.g.
 TSUBAME V queue with VM on clouds.
@@
 Fig.~\ref{throughput TSUBAME} shows read and write throughput from TSUBAME V queue nodes (VM runing on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}) and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
-On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, which has about 1GBit/s Internet access.
-Since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from Amazon.
+However, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from Amazon.
 We can see that the I/O throughput also grows as number of nodes grows but the aggregate throughput is only 100-140 MB/s, which is limited by Internet bandwidth, about 40-80 times smaller than throughput inside TSUBAME.
+For data-sensitive application, low I/O throughput is devastating, especially for application running on supercomputers, furthermore, lower I/O throughput leads a longer execution time, according to Amazon pay-as-you-go policy, longer execution time means more cost.
 
 To solve this problem, we propose our cloud-based I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
+Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost.
+Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele
 
@@
 
-using I/O burst buffer requires addtional nodes running on public cloud and means more cost, also like Amazon EC2, public cloud usually provides various instance types with different specification, using which instance type also will affect both cost and performance.
-We provide a cost-based model to determine 
-However, if we consider interconnection throughput, as shown in Fig.\ref{point to point connection AMAZON}, although each node can achieve only 1GB/s, the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
-Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
+%using I/O burst buffer requires addtional nodes running on public cloud and means more cost, also like Amazon EC2, public cloud usually provides various instance types with different specification, using which instance type also will affect both cost and performance.
+%We provide a cost-based model to determine 
+Fig.\ref{point to point connection AMAZON} shows the Ethernet throughput inside Amazon EC2 taken by using Iperf, although we only show the result up to 8 pairs of nodes, each node achieved only 135MB/s (1GBit/s), the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
+since when we running the benchmark, many other users were also running applications on Amazon, so we can assume that highest throughput 1GB/s (8Gbit/s) shown in Fig.~\ref{point to point connection AMAZON} is not the maximum bandwidth of Ethernet in Amazon EC2.
+Comparing Fig.~\ref{point to point connection AMAZON} with Fig.~\ref{throughput AMAZON to OURLAB} and Fig.~\ref{point to point connection LAB}, Ethernet throughput is much higher than Internet, it shows that our solution, by using I/O buffer nodes can achieve a higher Ethernet throughput than Internet.
+%Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
 

### 2014-06-30 paper/src/3_burst_buffer.tex
modify 1,2,3

@@
 
-An overview of I/O burst buffer architecture and two kinds of connection: direct connection and I/O bursting buffer are described in this section.
+An overview of I/O burst buffer architecture and two kinds of buffer model: one-side buffer and two-side buffer are described in this section.
 As we mentioned in the previous section, our model takes advantage of high throughput inside a system, and use buffer queue system in order to increase throughput between two systems.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, I/O data will first be buffered in buffer queue in the same system, and then be transferred to final storage system
+Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
+The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, for write I/O data, if buffer queue in I/O buffer nodes is not full, data can first be buffered in buffer queue in the same system, and then be transferred to final storage system, and for reading, if that file is stored in the buffer queue, computing nodes can read from I/O nodes through Ethernet.
+In other cases (buffer queue is full when issue a write requst or requsted file is not stored in buffer queue when issue a read request we call it cache miss), an read from or write back operation described below will be executed.
 \kento{how about read ?}.
 %the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
-Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
 %Although our goal here is to federate supercomputer with public cloud, since there are a great performance gap between normal supercomputer nodes and public cloud nodes and problem described above, here we consider about federating virtual machine nodes which running on supercomputer physical nodes with public cloud.
@@
 	\item All computing nodes are connected by large bandwidth and interconnection network, note network topology maybe different in each system, so topology is not specified here, interconnection network performance is measured by throughput.
-	\item There are a constant number of public IP addresses can be assigned to some computing nodes.
 	\item There is a shared storage for date sharing inside system, all computing nodes are connected with shared storage, also the filesystem of shared storage is not specified and performance is measured by throughput.
+	\item All nodes used by the same job are allocated in the same system, since the Internet bandwidth is low and unstable, user do not want to make communication between nodes via Internet.% so data consistency can be guaranteed since that.
 \end{itemize}
@@
 %Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
-There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application,which assigned only  and I/O burst buffer nodes, which assigned both private IP address.
+There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application and I/O burst buffer nodes.
+Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
 
 Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
-In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data and send to or read from I/O buffer nodes.
-Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
+In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data, communicate with I/O buffer nodes, including send I/O requset and send or receive I/O data.
 
-When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O data will be transferred to I/O burst buffer.
-First, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are allocated in the same system, so data consistency can be guaranteed since that.
-Buffer queue operation including data write back and operation when queue is full will be described in following section.
+When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O server will try to transfer I/O data to buffer queue in I/O burst buffer, if buffer queue in not full, I/O data will be sent to I/O burst buffer via Ethernet and can be seen among computing nodes in the same system after that.
+However if buffer queue is full, I/O server will block user application and wait until buffer queue is ready to recieve new I/O data, causing a low I/O throughput.
 
-When user issue a read request, there are two conditions: file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
+%When I/O server is notified that buffer queue is ready,first, I/O server sends the size of I/O data to master I/O burst buffer node, master node return a list of several I/O buffer nodes, then I/O server split I/O data into pieces, and sends each pieces to a I/O buffer node, after data transfer finished, that file will be added to buffer queue and namespace, and this file can be seen by all computing nodes, since we assume that all nodes used by the same job are allocated in the same system, so data consistency can be guaranteed since that.
+%Buffer queue operation including data write back and operation when queue is full will be described in following section.
+
+Similiarly when user issue a read request, there are two conditions: required file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
 In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
@@
 
-In this section we describe operations when file is not in I/O buffer nodes or file needs to be write back to storage in another system.
+In this section we describe read and write operations when cache miss happens.%file is not in I/O buffer nodes or file needs to be write back to storage in another system.
 We propose two kinds of model: one-side buffer and two-side buffer.
@@
 As Fig.~\ref{read and write} blue arrow shows, one-side buffer is a connection between I/O buffer nodes in system 2 and storage in system 1 directly.
-When I/O nodes need to write data back to storage in another system, since data is already spread among I/O nodes, a parallel write can be achieve to fully utilize the Internet bandwidth.
+When I/O nodes need to write data back to storage in another system, since data is already spread among I/O nodes, a parallel write can be used to fully utilize the Internet bandwidth.
 
@@
 
-On the contrary, two-side buffer solution use I/O buffer nodes in both two systems as Fig.~\ref{read and write} orange arrows show.
+On the contrary, two-side buffer solution uses I/O buffer nodes in both two systems as Fig.~\ref{read and write} orange arrows show.
 I/O data will be split twice, transferred throughput two sides of I/O buffer nodes and then reached the destination.
@@
 
-Compared with one-side buffer, two-side buffer required one more data transfer (I/O nodes to storage in the same system), if storage data transfer throuhput become a bottleneck, two-side buffer will cost more time than one-side buffer.
-Also, two-side buffer require both systems allocate I/O buffer nodes, if node usage is charge in both system, total cost may be larger than one-side buffer.
+Compared with one-side buffer, %two-side buffer required one more data transfer (I/O nodes to storage in the same system), if storage data transfer throuhput become a bottleneck, two-side buffer will cost more time than one-side buffer.
+%Also, 
+two-side buffer require both systems allocate I/O buffer nodes, if node usage is charge in both system, total cost may be larger than one-side buffer.
 
 %the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
-Since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
+However since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
 Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.
 
+For these reasons, in the following section, we will use two-side buffer model as our read from and write back model in I/O burst buffer.
 %I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.

### 2014-07-01 paper/src/1_introduction.tex
Updated 1_intro.tex

@@
 \label{sec:introduction}
-Supercomputers provide an increasing number of scientific applications with high computational power by a large number of processors, large bandwidth memory and low leatency interconnects.
+Supercomputers provide an increasing number of scientific applications with high computational power by a large number of processors, large bandwidth memory and interconnects.
 %Data size need to be processed grows rapidly these days, which is known as Big Data, people perfer to use supercomputer to analyze Big Data for it supports high parallelism.
@@
 %high parallel application runs faster on Supercomputer for fully usage of computing resource, but a serial application will occupy computing nodes for a long time causing other application must wait.
-Although supercomputers can offer high capablity of computation, it is not unlimited, for some request peak, computation resource in supercomputer can not meet the needs of user, or simply user requesst more resource than supercomputers have, also some jobs require a exclusive usage for computing nodes, like grand challenge, will occpy a great amount of computation resource, leads inadequate of reourse for other job.
-Another problem is the power problem in summer, in order to reduce power consumption, some nodes will be forced to be shut down (peak shift in TSUBAME\cite{TSUBAME}), reducing numbers of nodes will make the first problem more serous.
+Although supercomputers can also offer high computational capacity, the computational resources are not unlimited. 
+Supercomputers can not meet the demands of users when the demands exceed the limit. 
+For example, on grand challnge projects, computational resources are exclusively used for the scientific discoveries~\cite{Scientific_Grand_Challenges_Crosscutting_Technologies_for_Computing_at_the_Exascale, Scientific_Grand_Challenges_in_National_Security_the_Role_of_Computing_at_the_Extreme_Scale}, and the system can not provide adequate resources for other jobs.
+In addition, under power badget constrain~\cite{Exploring_Hardware_Overprovisioning_in_Power-constrained_High_Performance_Computing,Operation_of_TSUBAME_2_0_Green_Supercomputer_dealing_with_Power_Crisis}, a part of compute nodes are required to be shutdown to reduce its power consumption, which also leads inadequate of resources for all users.
 
-One solution is federating a supercomputer with a public cloud,
-and moving a part of jobs to the public cloud when there are not enough
+One of solutions to provide adequate computational resources under the constrains, is federating a supercomputer with public cloud.
+By moving a part of jobs to the public cloud when there are not enough
 computing nodes available for user's requests, which is known as \emph{cloud bursting}.
+\cite{Optimizing_Service_Level_Agreements_for_Autonomic_Cloud_Bursting_Schedulers, A_Framework_for_Data-Intensive_Computing_with_Cloud_Bursting}
 Although cloud bursting is technically feasible~\cite{Eucalyptus,stratos,Seagull}, 

### 2014-07-01 paper/src/1_introduction.tex
Updated 1_intro

@@
 
-One of solutions to provide adequate computational resources under the constrains, is federating a supercomputer with public cloud.
-By moving a part of jobs to the public cloud when there are not enough
-computing nodes available for user's requests, which is known as \emph{cloud bursting}.
-\cite{Optimizing_Service_Level_Agreements_for_Autonomic_Cloud_Bursting_Schedulers, A_Framework_for_Data-Intensive_Computing_with_Cloud_Bursting}
+One of solutions to provide adequate computational resources under the constrains, is federating the supercomputer with public clouds.
+By moving a part of jobs to public clouds when there are not enough
+compute nodes available, we can meet the needs for users' requests even under the constrains, which is known as \emph{cloud bursting}~\cite{Optimizing_Service_Level_Agreements_for_Autonomic_Cloud_Bursting_Schedulers, A_Framework_for_Data-Intensive_Computing_with_Cloud_Bursting}.
 Although cloud bursting is technically feasible~\cite{Eucalyptus,stratos,Seagull}, 
-and is employed by several private companies, 
-there is a significant performance gap between supercomputers and clouds, 
-there will still be several problems when we try to federate a supercomputer with a public cloud, 
-and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
-The biggest problem will be data transfer throughput between two environment, 
-since we want to move some jobs from supercomputer to public cloud, I/O data need to transfer between these two system, supercomputers usual deal with Gigabyte or even Petabyte input and output of data,
-low I/O throughput will suffer supercomputer user. This paper focuses on methodology 
-of increasing throughput when we do federation.
+and is employed by several private companies, there are several problems if we apply the techniqu to supercomputers.
+One of the problems is a significant performance gap between supercomputers and public clouds especially in I/O performance
+%there will still be several problems when we try to federate a supercomputer with a public cloud, 
+%and there are several studies on cloud burst about cost\cite{Seagull}, execution time\cite{time_and_cost}, etc..
+%Especially, low I/O performance between supercomputers and public clouds is critical.
+%The biggest problem will be data transfer throughput between two environment, 
+For example, if we migrate a part of jobs from a supercomputer to a public cloud or run jobs on a public cloud insted of a supercomputer, and the jobs need data located in a parallel file system (PFS), the data need to be transfered between the two system.
+% supercomputers usual deal with Gigabyte or even Petabyte input and output of data, 
+Because the two systems are usually geographically distributed, and network throghput between the systems is quite low,
+the low I/O throughput suffers supercomputer users.
+Thus, improving I/O throughputs between two systems, which are geographically distributed each other, is ciritical in federating supercomputers with public clouds
 
-In this paper, we propose an I/O burst buffer architecture that uses multiple nodes in each system as an I/O nodes 
-to achieve high throughput concurrent data transferring, and an I/O burst buffer model 
-that uses to switch between I/O burst buffer mode and direct connect mode.
+In this paper, we propose cloud-based burst buffers.
+The cloud-based burst buffers consists of I/O dedicated staging nodes, which cache hot files in the buffers, and enables asynchronous write back for improving both read and write operations to remote file systems.
+We also model the cloud-based burst buffers to optimize  configurations of the cloud-based burst buffers according to dynamically changing environments
+\kento{Do you think this sentence is resonable to describe your model ?}.
+\kento{please summirize the evaluation resutls here.}
+%  architecture that uses multiple nodes in each system as an I/O nodes 
+%to improve I/O throughput concurrent data transferring, and an I/O burst buffer model 
+%that uses to switch between I/O burst buffer mode and direct connect mode.
 %This I/O bursting buffer architecture can be mainly used two situation, first in data I/O, the other one will be when there are some nodes need to migrate from a cloud to another cloud with snapshot, snapshots can be transferred without be stored to shared storage.
 %Since, I/O bursting buffer needs three times data transfer, sometimes direct transfer will achieve a higher throughput, I/O bursting buffer model using a evaluation throughput using I/O bursting buffer and without I/O bursting buffer to determine I/O bursting buffer mode or direct connection mode.
-Also, public cloud usually charges for nodes usage, I/O bursting buffers may reduce the computation time, 
-but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.
-\kento{please summirize the evaluation resutls here.}
+%Also, public cloud usually charges for nodes usage, I/O bursting buffers may reduce the computation time, 
+%but I/O nodes will be charged for money, we also provide a cost-based model, to reduce the overall cost.
+
 Our contributions can be summrized as following:
@@
 %2
-The remainder of this paper is organized as follow. 
+The rest of this paper is organized as follows. 
 In Section \ref{sec:motivation}, we clarify the motivation and the background.

### 2014-07-01 paper/src/5_evaluation.tex
Changed directory stractures
several updates
0701

--- 2014-06-27 paper/section/evaluation.tex
@@
 \section{Evaluation}
+\label{sec:evaluation}
 
@@
 	\centering
-	%\includegraphics[width=6cm]{}
+	\includegraphics[width=6cm]{../img/throughput_comparison}
 	\caption{throughput comparison with and without I/O burst buffer}
-	\label{throughput}
+	\label{throughput comparison}
 \end{figure}
@@
 	\centering
-	%\includegraphics[width=6cm]{}
-	\caption{cost comparison with and without I/O burst buffer}
-	\label{cost}
+	\includegraphics[width=6cm]{../img/cache_hit_rate_throughput}
+	\caption{throughput comparison between each cache hit rate}
+	\label{throughput cache rate}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=6cm]{compress_rate}
-	\caption{compress rate}
-	\label{compress rate}
+	\includegraphics[width=6cm]{../img/maximum_throughput}
+	\caption{maximum avaliable throughput}
+	\label{maximum throughput}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=6cm]{compress_time}
-	\caption{compress time on TSUBAME V queue and AMAZON EC2}
-	\label{compress time}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics[width=6cm]{}
-	\caption{throughput comparison with and without compress}
-	\label{compress}
-\end{figure}
-
-\begin{figure}[tb]
-	\centering
-	%\includegraphics
-	\caption{cache hit and miss throughput comparison}
-	\label{cache hit}
+	\includegraphics[width=6cm]{../img/cost}
+	\caption{cost comparison}
+	\label{cost}
 \end{figure}
@@
 
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region, using
+In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region%, using
+Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, since when we use I/O burst buffer, read and write throughput are the same, both is equal to throughput between computing nodes and I/O nodes, for using I/O burst buffer, we use this throughput value.
 %m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
-m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}.
+%m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}.
 Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{point to point connection LAB} ).
@@
 %\end{center}
-For throughput between two systems and inside system, from benchmark data, it shows it is hard to achieve a high throughput with only one nodes, and also there is a limit on maximum throughput between two systems and inside system.
-Although incresing nodes can increse throughput before reach the maximum, throughput achieved by each nodes decrease because of conflict.
-For these reason, we use following formular for throughput between two systems and inside system.
+%For throughput between two systems and inside system, from benchmark data, it shows it is hard to achieve a high throughput with only one nodes, and also there is a limit on maximum throughput between two systems and inside system.
+%Although incresing nodes can increse throughput before reach the maximum, throughput achieved by each nodes decrease because of conflict.
+%For these reason, we use following formular for throughput between two systems and inside system.
 %TSUBAME and AMAZON EC2, we use similar model in \cite{ccgrid}:
-\begin{equation}
-throughput=-Ax^2+Bx+C~~ A,B>0\\
-\end{equation}
-we use following equations to determine $A,B,C$
-\begin{equation}
-\begin{cases}
-	-A+B+C=throughput_{one}\\\nonumber
-	\frac{B}{2A}=n_{max}\\\nonumber
-	-An_{max}^2+Bn_{max}+C=throughput_{max}\\
-\end{cases}
-\end{equation}
+%\begin{equation}
+%throughput=-Ax^2+Bx+C~~ A,B>0\\
+%\end{equation}
+%we use following equations to determine $A,B,C$
+%\begin{equation}
+%	\label{throughput equation}
+%\begin{cases}
+%	-A+B+C=throughput_{one}\\\nonumber
+%	\frac{B}{2A}=n_{max}\\\nonumber
+%	-An_{max}^2+Bn_{max}+C=throughput_{max}\\
+%\end{cases}
+%\end{equation}
 
-First, we compare throughput with and without I/O buffer nodes.
-Since it is hard for one node to fully utilize Internet and Ethernet bandwidth, according to Fig.~\ref{throughput AMAZON to OURLAB}, we assume that one node can achieve half of maximum bandwidth.
-We can see from Fig.~\ref{throughput}, when interconnection throughput is larger than Internet throughput, our I/O buffer can achieve a higher throughput.
+%Since it is hard for one node to fully utilize Internet and Ethernet bandwidth, according to Fig.~\ref{throughput AMAZON to OURLAB}, we assume that one node can achieve 80\% of maximum bandwidth, and by using I/O burst buffer, can achieve 100\% of maximum bandwidth of both Ethernet and Internet, here Ethernet throughput refers to Ethernet connection throughput in public cloud.
 
-Then, we compare overall cost by using I/O burst buffer,
+First we compare the I/O throughput between direct connection and I/O burst buffer (both cache miss and cache hit) on TSUBAME and Amazon EC2.
 
-we compare throughput with and without compression, Fig.~\ref{compress rate} shows compress and Fig.~\ref{compress time} shows compress and decompress time on TSUBAME V queue and AMAZON EC2 with a different compress level by using zlib\cite{zlib}.
-We can achieve a high compress rate, but the throughput is low, up to 160MB/s, depends on compress level, it is hard to find a compress library can compress data faster and smaller, so the compress throughput may become a bottleneck.
-On the other hand, the compress rate is high, since the buffer size is limited, if we can make data smaller, it means we can increase the buffer hit rate, Fig.~\ref{cache hit} shows a throughput comparison between cache miss and hit.
+Fig.~\ref{throughput comparison} and Fig.~\ref{throughput cache rate} shows the throughput comparison with and without I/O burst buffer.
+For without I/O burst buffer, each computing nodes will read from and write data to storage directly and concurrently, when number of nodes is small, throughput increases as number of nodes increses, but after throughput reach the Internet throughput(number of nodes equals to 10 in our case), throughput becomes stable, means Internet bandwidth is fully utilized, and since that I/O is limited by Internet bandwidth.
 
-Fig.~\ref{compress}
+For 0\% cache hit cases, since all data should be read from or write back to storage, throughput shows a similiar trade, also limited by Internet bandwidth.
+
+The large difference shows in cache hit 100\%(Fig.~\ref{throughput cache rate}), since all required files are buffered in buffer queue, also buffer queue is not full, computing nodes can read from and write to buffer queue every time.
+As we mentioned, Ethernet throughput in Amazon EC2 shows a strong scalablity, I/O throughput can finially achieve around 2700MB/s, about 20 times faster than direct I/O and also 0\%cache hit cases.
+
+However 100\% cache hit is a ideal condition not pratical, so in Fig.~\ref{throughput cache rate}, we also show predict throughput for 75\%,50\% and 25\% cache hit.
+When there is a cache miss both in read and write, data need to be transfer via both Ethernet and Internet like 0\% cache hit case, and for cache hit, files can be read and written via Ethernet like 100\% cache hit case, so we use two-side Internet throughput($thr_I$) shown in Fig.~\ref{point to point connection LAB}, Ethernet throughput in Amazon($thr_E$) shown in Fig.~\ref{point to point connection AMAZON} and following formular to evaluate throughput for each cache hit rate.
+
+\[throughput=\frac{1}{MAX\{\frac{{hit\_rate}}{thr_E},\frac{1-hit\_rate}{thr_I}+\frac{1-hit\_rate}{thr_E}\}}\]
+
+and result is shown in Fig.~\ref{throughput cache rate}, we can see that althrough, 100\% cache hit achieve a high throughput, even 75\% cache hit is much lower than 100\%, it is because of the great gap between Ethernet bandwidth and Internet bandwidth, also data can transfer faster in Ethernet, user application must wait until cache miss data transferred through Internet.
+
+%If file is buffered in I/O buffer nodes, computing nodes can read it through Ethernet, Fig.~\ref{cache hit}, shows the comparison, we can see that when Ethernet throughput larger than Internet throughput, our solution can achieve a higher I/O throughput, here we assume that Ethernet throuhput can be lower than Internet throughput, but from Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{throughput TSUBAME}, Ethernet usually is faster than Internet, and by using our solution can achieve a high throughput.
+
+%Then, we compare throughput with and without I/O buffer nodes.
+%We can see from Fig.~\ref{throughput},although our solution can be limited by both Internet and Ethernet throughput, our I/O burst buffer can fully utilize both Internet and Ethernet.
+Like previous comparison, when Ethernet is faster than Internet, our solution can achieve a throughput burst even file is not stored in buffer queue in I/O burst buffer like (read data from storage).
+
+Then we compare overall cost with and without I/O burst buffer, As we mentioned, cost will be determined by both number of nodes and execution time, 
+As we showed, By using I/O burst buffer, we can achieve a high I/o throughput, and reduce both the execution time and cost, however, I/O buffer node also will be charged, hence we use following formular to evaluate cost
+\[\frac{Data~size}{throughput}*cost*node\]
+According to Amazon pricing policy, m3.xlarge instance is charged \$0.405 for each hour usage in Asia Pacific(Tokyo).
+
+Fig.~\ref{cost} shows cost comparison between each cache hit rate and direct I/O, which read or write 100GB data, we can see that cost
+%Since we assume number of I/O buffer node increases as number of computing nodes increases, 
+%After that, we compare overall cost when use two-side buffer and one-side buffer, since execution time, in our case, I/O time and I/O throughput will affect cost, for Internet and Ethernet throughput, we use.
+%From Fig.~\ref{cost},

### 2014-07-01 paper/src/5_evaluation.tex
finish evaluation

@@
 
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region%, using
-Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, since when we use I/O burst buffer, read and write throughput are the same, both is equal to throughput between computing nodes and I/O nodes, for using I/O burst buffer, we use this throughput value.
+In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region.%, using
+Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, we compare I/O througput and overall cost between direct I/O and I/O burst buffer with different cache hit rate, here cache hit rate means the percentage of data in total I/O is buffered in buffer queue or the percentage of data can write to buffer queue before queue becomes full.
+since when we use I/O burst buffer, read and write throughput are the same, both is equal to throughput between computing nodes and I/O nodes, for using I/O burst buffer, we use this throughput value.
 %m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
@@
 First we compare the I/O throughput between direct connection and I/O burst buffer (both cache miss and cache hit) on TSUBAME and Amazon EC2.
+In this simulation we assume that both I/O buffer nodes and computing nodes use m3.xlarge instance and Amazon Linux AMI, and the number of I/O buffer nodes is equal to number of computing nodes in order to achieve a maximum Ethernet throughput.
+In practice, I/O buffer nodes may have a better Ethernet condition than computing nodes, but there also will be many users running their application on large amount of computing nodes, so there can be several computing nodes reading data from or writing data to one I/O nodes, Ethernet bandwidth also can be fully utilized.
 
@@
 
-However 100\% cache hit is a ideal condition not pratical, so in Fig.~\ref{throughput cache rate}, we also show predict throughput for 75\%,50\% and 25\% cache hit.
+However 100\% cache hit is a ideal condition not pratical, so in Fig.~\ref{throughput cache rate}, we also show predict throughput for 75\%,50\% and 25\% cache hit rate.
 When there is a cache miss both in read and write, data need to be transfer via both Ethernet and Internet like 0\% cache hit case, and for cache hit, files can be read and written via Ethernet like 100\% cache hit case, so we use two-side Internet throughput($thr_I$) shown in Fig.~\ref{point to point connection LAB}, Ethernet throughput in Amazon($thr_E$) shown in Fig.~\ref{point to point connection AMAZON} and following formular to evaluate throughput for each cache hit rate.
@@
 
-and result is shown in Fig.~\ref{throughput cache rate}, we can see that althrough, 100\% cache hit achieve a high throughput, even 75\% cache hit is much lower than 100\%, it is because of the great gap between Ethernet bandwidth and Internet bandwidth, also data can transfer faster in Ethernet, user application must wait until cache miss data transferred through Internet.
+Result is shown in Fig.~\ref{throughput cache rate}, we can see that althrough, 100\% cache hit achieve a high throughput, even 75\% cache hit is much lower than 100\%, it is because of the great gap between Ethernet bandwidth and Internet bandwidth, also data can transfer faster in Ethernet, user application must wait until cache miss data transferred through Internet.
 
@@
 As we showed, By using I/O burst buffer, we can achieve a high I/o throughput, and reduce both the execution time and cost, however, I/O buffer node also will be charged, hence we use following formular to evaluate cost
-\[\frac{Data~size}{throughput}*cost*node\]
+\[cost=\frac{Data~size}{throughput}\times cost\times node\]
 According to Amazon pricing policy, m3.xlarge instance is charged \$0.405 for each hour usage in Asia Pacific(Tokyo).
+For direct I/O, nodes is equal to number of computing nodes, but for I/O burst buffer, since we assume that number of I/O nodes is equal to number of computing nodes, here the value of node in above formular will be 2 times number of computing nodes.
 
-Fig.~\ref{cost} shows cost comparison between each cache hit rate and direct I/O, which read or write 100GB data, we can see that cost
+Fig.~\ref{cost} shows cost comparison between each cache hit rate and direct I/O, which read or write 100GB data, we can see that cost grows as number of nodes grows, except for 100\% cache hit, which throughput is proportional to nodes number.
+As the Fig.~\ref{cost} shows, if cache hit rate is higher than 50\%, the overall cost using I/O burst buffer will lower than direct I/O, however, if cache hit rate is lower than 50\%, using I/O burst buffer will cost more.
+
+From above simulations, we can see that if we can achieve a high cache hit rate, we can achieve a high throughput up to 4-20 times faster than direct I/O as well as a low cost up to 2-12 times lower than direct I/O for 20 client nodes.
+It is may be difficult for read data cache hit rate to be higher than 50\% (can be possible according to data locality), but it is reasonable for write data can be buffered in buffer queue, since public clouds usually provide instance with large size of memory, and it is easy to achieve a Tera size of buffer queue.
 %Since we assume number of I/O buffer node increases as number of computing nodes increases, 

### 2014-07-01 paper/src/paper.tex
Changed directory stractures
added new command to paper.tex, and update on intro
several updates
add author
Added comments in motication section, updated paper.tex for building
change format

--- 2014-06-30 paper/paper.tex
@@
-\documentclass[JIP,draft]{ipsj}
+\documentclass[techreq,english]{ipsj}
 \usepackage{graphicx}
@@
 \usepackage{supertabular}
+\usepackage{flushend}
+\usepackage{latexsym}
+\usepackage{colortbl}
 \bibliographystyle{ipsjunsrt-e.bst}
 
+\newcommand{\kento}[1]{{\color{blue} [Kento: {\it #1}]}}
+\definecolor{darkgray}{gray}{0.7}
+\definecolor{lightgray}{gray}{0.9}
+
+\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
+\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
+\def\|{\verb|}
+\usepackage[varg]{txfonts}
+\makeatletter
+\input{ot1txtt.fd}
+\makeatother
+\setcounter{volume}{22}% vol21=2013
+\setcounter{number}{1}
+\setcounter{page}{1}
 \begin{document}
-\title{Towards Cloud Bursting for Extreme Scale Supercomputers}
+\title{Towards Cloud Bursting for Extreme Scale Supercomputers\\
+   (Unrefereed Workshop Manuscript)}
+
+\affiliate{Titech}{Tokyo Institute of Technology, Japan, Tokyo, Meguro, okayama 2-12-1}
+\author{Tianqi Xu}{Titech}
+\author{Kento Sato}{Titech}
+\author{Satoshi Matsuoka}{Titech}
 
@@
 \begin{keyword}
-Supercomputer, Cloud, I/O Bursting Buffer Model
+Supercomputer, Cloud, Burst buffer
 \end{keyword}
@@
 
+\input{5-5_related_work}
+
 \input{6_conclusion}
 
-\bibliography{reference}
+\bibliography{../bib/reference}
 \end{document}

### 2014-07-01 paper/src/5_evaluation.tex
modify 5

@@
 In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region.%, using
-Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, we compare I/O througput and overall cost between direct I/O and I/O burst buffer with different cache hit rate, here cache hit rate means the percentage of data in total I/O is buffered in buffer queue or the percentage of data can write to buffer queue before queue becomes full.
-since when we use I/O burst buffer, read and write throughput are the same, both is equal to throughput between computing nodes and I/O nodes, for using I/O burst buffer, we use this throughput value.
+Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, we compare I/O throughput and overall cost between direct I/O and I/O burst buffer with different cache hit rate, here cache hit rate means the percentage of data in total I/O is buffered in buffer queue or the percentage of data can write to buffer queue before queue becomes full.
+since when we use I/O burst buffer, read and write throughput are the same, both are equal to throughput between computing nodes and I/O nodes,  we use this throughput value for I/O throughput when use I/O burst buffer..
 %m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
@@
 
-First we compare the I/O throughput between direct connection and I/O burst buffer (both cache miss and cache hit) on TSUBAME and Amazon EC2.
+First we compare the I/O throughput between direct connection and I/O burst buffer with different cache hit rate on TSUBAME and Amazon EC2.
 In this simulation we assume that both I/O buffer nodes and computing nodes use m3.xlarge instance and Amazon Linux AMI, and the number of I/O buffer nodes is equal to number of computing nodes in order to achieve a maximum Ethernet throughput.
@@
 Fig.~\ref{throughput comparison} and Fig.~\ref{throughput cache rate} shows the throughput comparison with and without I/O burst buffer.
-For without I/O burst buffer, each computing nodes will read from and write data to storage directly and concurrently, when number of nodes is small, throughput increases as number of nodes increses, but after throughput reach the Internet throughput(number of nodes equals to 10 in our case), throughput becomes stable, means Internet bandwidth is fully utilized, and since that I/O is limited by Internet bandwidth.
+For direct I/O, each computing nodes will read from and write data to storage directly and concurrently, when number of nodes is small, throughput increases as number of nodes increses, but after throughput reach the Internet bandwidth( 120MB/s when number of nodes equals to 10 in our case), throughput becomes stable, means Internet bandwidth is fully utilized, and since that I/O is limited by Internet bandwidth.
 
@@
 
-The large difference shows in cache hit 100\%(Fig.~\ref{throughput cache rate}), since all required files are buffered in buffer queue, also buffer queue is not full, computing nodes can read from and write to buffer queue every time.
+The large difference shows in cache hit 100\%(Fig.~\ref{throughput cache rate}), since all required files are buffered in buffer queue, also buffer queue is not full, computing nodes can read from and write to buffer queue each time.
 As we mentioned, Ethernet throughput in Amazon EC2 shows a strong scalablity, I/O throughput can finially achieve around 2700MB/s, about 20 times faster than direct I/O and also 0\%cache hit cases.
@@
 
+In this simulation we only consider one job use up to 20 computing nodes, but in practice, large number of computing nodes issue read and write request concurrently, Fig.~\ref{maximum throughput} shows the maximum throughput of different cache hit rate and direct I/O, we can see that although reading can not achieve a cache hit rate, until buffer queue is full, writing can achieve a extremely high throughput.
 %If file is buffered in I/O buffer nodes, computing nodes can read it through Ethernet, Fig.~\ref{cache hit}, shows the comparison, we can see that when Ethernet throughput larger than Internet throughput, our solution can achieve a higher I/O throughput, here we assume that Ethernet throuhput can be lower than Internet throughput, but from Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{throughput TSUBAME}, Ethernet usually is faster than Internet, and by using our solution can achieve a high throughput.
@@
 
-Then we compare overall cost with and without I/O burst buffer, As we mentioned, cost will be determined by both number of nodes and execution time, 
-As we showed, By using I/O burst buffer, we can achieve a high I/o throughput, and reduce both the execution time and cost, however, I/O buffer node also will be charged, hence we use following formular to evaluate cost
-\[cost=\frac{Data~size}{throughput}\times cost\times node\]
+Then we compare overall cost with and without I/O burst buffer, As we mentioned, cost will be determined by both number of nodes and execution time. 
+As we showed, By using I/O burst buffer, we can achieve a high I/O throughput, and reduce both the execution time and cost, however, I/O buffer node also will be charged, hence we use following formular to evaluate cost
+\[cost=\frac{Data~size}{throughput}\times cost\_per\_hour\times node\]
 According to Amazon pricing policy, m3.xlarge instance is charged \$0.405 for each hour usage in Asia Pacific(Tokyo).

### 2014-07-01 paper/src/6_conclusion.tex
several updates
modify 6_

--- 2014-06-27 paper/section/conclusion.tex
@@
-\section{Conclusion and Future Work}
+\section{Conclusion}
+\label{sec:conclusion}
 
@@
 
-From simulation result, we showed that our I/O burst buffer can increase I/O throughput when Internet throughput is far smaller than interconnection throughput as well as reducing the overall cost.
+From simulation result, we showed that our I/O burst buffer can burst I/O throughput about 4-20 times depends on cache hit rate as well as reduce overall cost about 2-12 times when Internet throughput is far smaller than interconnection throughput.
 

### 2014-07-01 paper/src/1_introduction.tex
modify intro
Updated 1_intro.tex, and 2_motivation.tex

@@
 
-In this paper, we propose cloud-based burst buffers.
-The cloud-based burst buffers consists of I/O dedicated staging nodes, which cache hot files in the buffers, and enables asynchronous write back for improving both read and write operations to remote file systems.
-We also model the cloud-based burst buffers to optimize  configurations of the cloud-based burst buffers according to dynamically changing environments
+In this paper, we propose I/O burst buffers.
+The I/O burst buffers consists of I/O dedicated staging nodes, which cache hot files in the buffers, and enables asynchronous write back for improving both read and write operations to remote file systems.
+We also model the I/O burst buffers to optimize  configurations of the I/O burst buffers according to dynamically changing environments
 \kento{Do you think this sentence is resonable to describe your model ?}.
+According to our simulation, we can achieve a 4-20 times higher throughput (depends on data locality and other factors) by using 20 I/O buffer nodes on Amazon EC2 environment, as well sa reduce 2-12 times of cost.
 \kento{please summirize the evaluation resutls here.}
@@
 \begin{itemize}
-	\item A cloud-based burst buffer for increasing data transfer throughput between two systems;
+	\item A I/O burst buffer for increasing data transfer throughput between two systems;
 	\item A throughput-based I/O burst buffer model, which estimate I/O throughput of systems with I/O burst buffers, and a cost-based I/O burst buffer model, which estimate overall cost give a system configuration;

### 2014-07-01 paper/src/2_motivation.tex
Updated 1_intro.tex, and 2_motivation.tex

@@
 \kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
-                        (3-2) Then, please briefly clarfy why ``(A) cloud-based burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
-                              (Remember we knew that cloud-based burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
+                        (3-2) Then, please briefly clarfy why ``(A) I/O burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
+                              (Remember we knew that I/O burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
                         (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
@@
 
-To solve this problem, we propose our cloud-based I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
+To solve this problem, we propose our I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
 Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost.

### 2014-07-01 paper/src/5-5_related_work.tex
finish related work

\section{Related Work}
\label{sec:related_work}
Cloud computing is becoming a topic of much interest in recent years, not only famous Internet companies like google, Amazon, IBM, Oracle, Microsoft provide public cloud, many companies start to build or have built private cloud for internal computation. Recently hybrid cloud, which is a composition of two or more clouds (private or public) is becoming a hot topic since it allows a business to take advantage of the scalability and cost-effectiveness that a public cloud offers without exposing critical application and data to third-party vulnerabilties, also by using cloud bursting, a small private cloud can easily burst into a large cloud to deal with temporality request peak. 
Several rearch works have been done on hybrid cloud and cloud bursting, Tekin Bicer \emph{el at.}\cite{time_and_cost} considered a software framework to enable data-intensive computing with cloud bursting, which use a combination of compute resources from local cluster and a public cloud to proceesing on a geographically distributed data set.
Their framework assume computation nodes allocated in both local cluster and public cloud, and data set is geographically distributed, However in our study, data set is stored in local system and in order to obtain a high communication throughput between computation nodes, we assume that nodes used for the same job allocated in the same system.
Another cloud bursting application can be seen in Tian Guo\emph{el at.}\cite{Seagull}, they introduced a system called Seagull, designed to facilitate cloud brusting by determining which applications should be transitioned into the cloud and automating the movement process at the proper time. Their work focused on determine which applications should be moved to public cloud, and our work focus on the methdology of filling the I/O throughput in cloud bursting.

There are also several paper about data I/O throughput, transfering and data processing in hybrid cloud.
Chiba Tatsuhiro \emph{el at.}\cite{Chiba} proposed two high performance multicast algorithms used for transfering large amounts of data stored in Amazon S3 to multiple Amazon EC2 nodes.
Tekin Bicer \emph{el at.}\cite{MATE-EC2} also described a middleware that allows the specification of data processing using a high-level API in Amazon S3.

### 2014-07-01 paper/src/2_motivation.tex
finish

@@
 
+However, when we look at Ethernet throughput inside Amazon as Fig.\ref{point to point connection AMAZON} shows, although we only show the result up to 8 pairs of nodes, each node achieved only 135MB/s (1GBit/s), the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
+since when we running the benchmark, many other users were also running applications on Amazon, so we can assume that highest throughput 1GB/s (8Gbit/s) shown in Fig.~\ref{point to point connection AMAZON} is not the maximum bandwidth of Ethernet in Amazon EC2 .
+Comparing Fig.~\ref{point to point connection AMAZON} with Fig.~\ref{throughput AMAZON to OURLAB} and Fig.~\ref{point to point connection LAB}, Ethernet throughput is much higher than Internet, it shows that our solution, by using I/O buffer nodes can achieve a higher Ethernet throughput than Internet.
+
 To solve this problem, we propose our I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
-Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost.
-Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele
+Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost, we will introduce a throughput-based model and a cost-based model to predict the throughput and overall cost.
+%Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele
 
@@
 
-\subsection{(Current Section 2)}
+%\subsection{(Current Section 2)}
 \kento{Please fit the below sentences to the above sections with additional explanations}
@@
 %We provide a cost-based model to determine 
-Fig.\ref{point to point connection AMAZON} shows the Ethernet throughput inside Amazon EC2 taken by using Iperf, although we only show the result up to 8 pairs of nodes, each node achieved only 135MB/s (1GBit/s), the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
-since when we running the benchmark, many other users were also running applications on Amazon, so we can assume that highest throughput 1GB/s (8Gbit/s) shown in Fig.~\ref{point to point connection AMAZON} is not the maximum bandwidth of Ethernet in Amazon EC2.
-Comparing Fig.~\ref{point to point connection AMAZON} with Fig.~\ref{throughput AMAZON to OURLAB} and Fig.~\ref{point to point connection LAB}, Ethernet throughput is much higher than Internet, it shows that our solution, by using I/O buffer nodes can achieve a higher Ethernet throughput than Internet.
 %Since we can achieve a high interconnection throughput inside a system (HPC system, public cloud), we consider use some nodes as a buffer nodes, using a buffer queue to buffer I/O data and achieve a high throughput.
 
-Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with interconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are allocated in the same system.
+%Although there are some studies about workflow optimization and  balance\cite{Workload}, Since data transfer rate is extremely low in Internet compared with interconnection network and data size processed is extremely large, user do not want to settle their nodes across two systems, so in this model, we just consider the situation that all nodes used for the same job are allocated in the same system.

### 2014-07-01 paper/src/4_model.tex
finish

@@
 
-The throughput-based model, cost-based model and buffer queue write back model are described in this section.
-As we explained in the previous section, two-side buffer model is better than one-side buffer model, in the following section, we will use two-side buffer model as our read from and write back model in I/O burst buffer
+Since the instance type choice, Ethernet condition, Internet condition will affect the actual I/O throughput between two system, we introduce a throughput-based model, cost-based model and buffer queue write back model used to predict throughput, overall cost and in buffer rate when use I/O burst buffer and direct I/O, and using these predict model to make decision like which type of instance should use, and how many I/O nodes is needed in a particular cases.
 \kento{this sentences should be in the previsou section}.
@@
 	\label{definition}
-\begin{tabular}{|p{3cm}|p{5cm}|}
+\begin{tabular}{|c|p{5cm}|}
 	\hline
@@
 	$M_1(n_1),M_2(n_2)$& Throughput of connection between storage and $n_1$ I/O nodes in system 1 and storage and $n_2$ I/O nodes in system 2.\\\hline
-	$C_i\_Money(T)$& Cost for standard node in system $i$ for $T$ time usage\\\hline
+	$C_iM(T)$& Cost for standard node in system $i$ for $T$ time usage\\\hline
 	%and cost for node in system 1 is $C_2\_Money(T)$ for $T$ time usage, and since I/O nodes may use a better network, 
-	$C_i\_High\_Money(T)$ &I/O nodes in system $i$ for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
+	$C_iHM(T)$ &I/O nodes in system $i$ for $T$ time usage, since I/O nodes may use a better network condition, we assume it will cost more than normal nodes.\\\hline
 \end{tabular}
@@
 %There are many facts will affect throughput of Internet, so here a moniter is used to evaluate throughput between 
+First we consider direct I/O, computing nodes read from and write back to storage in another system directly.
 In the case of direct I/O \kento{What is direct I/O.
-I think it means direct connection mode in Section 3, but no explanation at all}, computing nodes connect to storage in another system directly, there is only one data transfer, so throughput \kento{read ?
+I think it means direct connection mode in Section 3, but no explanation at all}, computing nodes connect to storage in another system directly, there is only one data transfer, so both read and write throughput \kento{read ?
 or write ?
@@
 
-When using I/O burst buffer, there will be three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1, throughput \kento{write ?
+When using I/O burst buffer, there will be three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1,
+for reading, if required file is buffered in buffer queue, computing node can read data from buffer queue directly, then throughput will be:$E_2(n_2)$, similiarly, if buffer queue still have enough space for I/O data when issue a write request, computing nodes can write data to buffer queue, and throughput also will be:$E_2(n_2)$.
+
+If required file is not buffered in buffer queue when issue a read request, or when issue a write request buffer queue is full, the throughput will be:$\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)$, since for read request, file need to be read from storage in another system Internet, and for write request, it need to wait until buffer buffer write buffered file back the storage.
+throughput \kento{write ?
 and read ?.
 Explain how the buffer queue works (1) if buffer space is avaialble for write, (2) reading data is in the buffer queue.
-We need expian this in both previous section and in here} will be:
+We need expian this in both previous section and in here} here we summary them as:
 \begin{eqnarray}
@@
 		E_2(n_2) &\text{buffer queue available}\\ 
-	\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} &\text{buffer queue full}
+	\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} &\text{buffer queue full or file miss}
 	\end{cases} \label{throughput2}
 \end{eqnarray}
-
-In this throughput-based model, these two throughputs are evaluated, and a switch is based on these two values:
+Although we have two cases for each read and write request (in buffer or not in buffer), it is very difficult to predict the in buffer rate, since it will be affected by I/O size, Internet throughput, buffer queue size and so on.
 \kento{Why do you swithches between direct I/O and burst buffer?}
-\begin{equation}
-	\begin{cases}
-		\text{thr}_{\text{direct}} \geq \text{thr}_{\text{I/O buffer}} & \text{use direct I/O}\\
-		\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}} & \text{use I/O burst buffer}
-	\end{cases}
-\end{equation}
+%\begin{equation}
+%	\begin{cases}
+%		\text{thr}_{\text{direct}} \geq \text{thr}_{\text{I/O buffer}} & \text{use direct I/O}\\
+%		\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}} & \text{use I/O burst buffer}
+%	\end{cases}
+%\end{equation}
 
@@
 \kento{Again, it's hard to understand due to lack of information. Please read carfully over and over again and add more explanation like in the above}
-In the case of cost-based model, we consider the overall cost for using direct I/O and using I/O burst buffer.
+Although we may use I/O burst buffer to achieve a high I/O throughput and leading a decrease of execution time, and according to public cloud pay for usage policy, the cost for computing nodes may reduce, the relation between overall cost and I/O throughput can not be such simple, since I/O nodes will still charged for usage, and if we use a instance with high Ethernet condition in order to get a higher throughput, we may be charged for more money.
+
+Here we provide a cost-based model in order to predict overall cost for using I/O burst buffer and direct I/O.
+Like throughput-based model, cost will be affected by in buffer rate, but it depends on application and buffer queue size, and is very difficult to predict.
+%In the case of cost-based model, we consider the overall cost for using direct I/O and using I/O burst buffer.
 Although using I/O burst buffer will cost for I/O nodes, higher throughput can reduce execution time and also overall cost.
-using \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:
+According to \ref{throughput1},and \ref{throughput2} total time for transferring unit size of data can be compute as:
 
@@
 	\begin{cases}
-		T_1=\frac{1}{D_1(c_2)} & \text{direct}\\
-		T_2=\frac{1}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{buffer queue available}\\
-		T_3=\frac{1}{E_2(n_2)} &\text{buffer queue full}
+		T_1=\frac{Data~size}{D_1(c_2)} & \text{direct}\\
+		T_2=\frac{Data~size}{\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}} &\text{buffer queue full or file miss}\\
+		T_3=\frac{Data~size}{E_2(n_2)} &\text{buffer queue available}
 	\end{cases}
@@
 \begin{equation}
-	\text{cost}_\text{direct}=c_2\times C_2\_Money(T_1)+n_2\times C_2\_High\_Money(T_1)
+	\text{cost}_\text{direct}=c_2\times C_2M(T_1)+n_2\times C_2HM(T_1)
 \end{equation}
@@
 \begin{align}
-	\text{cost}_\text{I/O buffer}=\\\begin{cases}
-				c_2\times C_2\_Money(T_2)+n_1\times C_1\_High\_Money(T_2)+n_2\times C_2\_High\_Money(T_2)&\text{buffer queue available}\\
-				c_2\times C_2\_Money(T_3)+n_1\times C_1\_High\_Money(T_3)+n_2\times C_2\_High\_Money(T_3) &\text{buffer queue full}
+	\begin{cases}
+		c_2\times C_2M(T_2)+n_1\times C_1HM(T_2)+n_2\times C_2HM(T_2)&\text{buffer queue available}\\
+		c_2\times C_2M(T_3)+n_1\times C_1HM(T_3)+n_2\times C_2HM(T_3) &\text{buffer queue full}
 	\end{cases}
@@
 
-In this cost-based model, these two cost are evaluated, and a switch is based on these two values:
-\begin{equation}
-	\begin{cases}
-		\text{cost}_{\text{direct}} \geq \text{cost}_{\text{I/O buffer}} & \text{use direct I/O}\\
-		\text{cost}_{\text{direct}} < \text{cost}_{\text{I/O buffer}} & \text{use I/O burst buffer}
-	\end{cases}
-\end{equation}
+%In this cost-based model, these two cost are evaluated, and a switch is based on these two values:
+%\begin{equation}
+%	\begin{cases}
+%		\text{cost}_{\text{direct}} \geq \text{cost}_{\text{I/O buffer}} & \text{use direct I/O}\\
+%		\text{cost}_{\text{direct}} < \text{cost}_{\text{I/O buffer}} & \text{use I/O burst buffer}
+%	\end{cases}
+%\end{equation}
 
@@
 After that, since buffer queue is full, I/O server can not send more data to I/O buffer nodes, have to block any read and write request since that.
-In this case, jobs running on public cloud have to be moved back to original system until buffer queue is empty
 \kento{Why ??}.

### 2014-07-01 paper/src/5_evaluation.tex
push 5_eval

@@
 %\end{figure}
-
-In this section, a simulation will be introduced based on data taking from several benchmarks on both TSUBAME V queue and AMAZON EC2 public cloud Tokyo region.%, using
-Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, we compare I/O throughput and overall cost between direct I/O and I/O burst buffer with different cache hit rate, here cache hit rate means the percentage of data in total I/O is buffered in buffer queue or the percentage of data can write to buffer queue before queue becomes full.
-since when we use I/O burst buffer, read and write throughput are the same, both are equal to throughput between computing nodes and I/O nodes,  we use this throughput value for I/O throughput when use I/O burst buffer..
+To evaluate how much federated systems with I/O burst buffers can improve I/O performance and the cost, 
+we conduct several simulations based on preliminary performance data taken from several 
+benchmarks on both our in-house cluster and Amazon EC2 in a Tokyo region in Section \ref{sec:motivation}.%, using
+In the simulations, we assume that computing nodes running on one system read or write files on storage of the other system with the same I/O throghputs for both read and write operations.
+We also assume an instance type of both the computing nodes and I/O burst buffer nodes is m3.xlarge provided by Amazon EC2.
+We compare I/O throughputs and overall costs of a system using direct I/O with a system using I/O burst buffer by scaling out up to 20 computing nodes
+under different cahch hit rate.
+For read operations, the cache hit rate means percentage of data, which is read from buffer queues, to total read size. 
+For write operations, the cache hit rate means percentage of data, which is  written to buffer queues before queue becomes full, to total write size.
+%Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, 
+%Since read and write throughput are the same when using caches on I/O burst buffers, read and write throughputs are equal to throghputs  between computing nodes and I/O nodes,  we use this throughput value for I/O throughput when use I/O burst buffer..
+If read and write are completed via caches on I/O burst buffers
+without accessing to remote storage, read and write throghputs become 
+identical to throughputs between a compute node and I/O burst buffer nodes. 
+%Thus, we use these throughputs for I/O throghputs
 %m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
@@
 
-First we compare the I/O throughput between direct connection and I/O burst buffer with different cache hit rate on TSUBAME and Amazon EC2.
-In this simulation we assume that both I/O buffer nodes and computing nodes use m3.xlarge instance and Amazon Linux AMI, and the number of I/O buffer nodes is equal to number of computing nodes in order to achieve a maximum Ethernet throughput.
-In practice, I/O buffer nodes may have a better Ethernet condition than computing nodes, but there also will be many users running their application on large amount of computing nodes, so there can be several computing nodes reading data from or writing data to one I/O nodes, Ethernet bandwidth also can be fully utilized.
+First we compare I/O throughputs of direct connection with the throughput of  I/O burst buffer under different cache hit rates assuming that TSUBAME is federated with Amazon EC2.
+%In this simulation, we assume that both I/O buffer nodes and computing nodes use m3.xlarge instance and Amazon Linux AMI, and the number of I/O buffer nodes is equal to number of computing nodes in order to achieve a maximum Ethernet throughput.
+In this simulation, the number of I/O buffer nodes is equal to the number of computing nodes. This configuration can achieve a maximum I/O throughputs.
+%In practice, I/O buffer nodes may have a better Ethernet condition than computing nodes, but there also will be many users running their application on large amount of computing nodes, so there can be several computing nodes reading data from or writing data to one I/O nodes, Ethernet bandwidth also can be fully utilized.
+In practice, an I/O buffer node may have higher network throghput condition than computing nodes, 
+but there also will be many users running their application on large amount of computing nodes, 
+so there can be several computing nodes reading data from or writing data to one I/O nodes, 
+Ethernet bandwidth also can be fully utilized.
 

### 2014-07-01 paper/src/1_introduction.tex
0701

@@
 Supercomputers can not meet the demands of users when the demands exceed the limit. 
-For example, on grand challnge projects, computational resources are exclusively used for the scientific discoveries~\cite{Scientific_Grand_Challenges_Crosscutting_Technologies_for_Computing_at_the_Exascale, Scientific_Grand_Challenges_in_National_Security_the_Role_of_Computing_at_the_Extreme_Scale}, and the system can not provide adequate resources for other jobs.
-In addition, under power badget constrain~\cite{Exploring_Hardware_Overprovisioning_in_Power-constrained_High_Performance_Computing,Operation_of_TSUBAME_2_0_Green_Supercomputer_dealing_with_Power_Crisis}, a part of compute nodes are required to be shutdown to reduce its power consumption, which also leads inadequate of resources for all users.
+For example, on grand challenge projects, computational resources are exclusively used for the scientific discoveries~\cite{Scientific_Grand_Challenges_Crosscutting_Technologies_for_Computing_at_the_Exascale, Scientific_Grand_Challenges_in_National_Security_the_Role_of_Computing_at_the_Extreme_Scale}, and the system can not provide adequate resources for other jobs.
+In addition, under power budget constrain~\cite{Exploring_Hardware_Overprovisioning_in_Power-constrained_High_Performance_Computing,Operation_of_TSUBAME_2_0_Green_Supercomputer_dealing_with_Power_Crisis}, a part of compute nodes are required to be shutdown to reduce its power consumption, which also leads inadequate of resources for all users.
 
@@
 Although cloud bursting is technically feasible~\cite{Eucalyptus,stratos,Seagull}, 
-and is employed by several private companies, there are several problems if we apply the techniqu to supercomputers.
+and is employed by several private companies, there are several problems if we apply this technique to supercomputers.
 One of the problems is a significant performance gap between supercomputers and public clouds especially in I/O performance
@@
 %The biggest problem will be data transfer throughput between two environment, 
-For example, if we migrate a part of jobs from a supercomputer to a public cloud or run jobs on a public cloud insted of a supercomputer, and the jobs need data located in a parallel file system (PFS), the data need to be transfered between the two system.
+For example, if we migrate a part of jobs from a supercomputer to a public cloud or run jobs on a public cloud insted of a supercomputer, and the jobs need data located in a parallel file system (PFS), the data need to be transferred between the two system.
 % supercomputers usual deal with Gigabyte or even Petabyte input and output of data, 
-Because the two systems are usually geographically distributed, and network throghput between the systems is quite low,
+Because the two systems are usually geographically distributed, and network throughput between the systems is quite low,
 the low I/O throughput suffers supercomputer users.
-Thus, improving I/O throughputs between two systems, which are geographically distributed each other, is ciritical in federating supercomputers with public clouds
+Thus, improving I/O throughput between two systems, which are geographically distributed each other, is critical in federating supercomputers with public clouds.
 
-In this paper, we propose I/O burst buffers.
+In this paper, we propose I/O burst buffer architecture.
 The I/O burst buffers consists of I/O dedicated staging nodes, which cache hot files in the buffers, and enables asynchronous write back for improving both read and write operations to remote file systems.
 We also model the I/O burst buffers to optimize  configurations of the I/O burst buffers according to dynamically changing environments
-\kento{Do you think this sentence is resonable to describe your model ?}.
-According to our simulation, we can achieve a 4-20 times higher throughput (depends on data locality and other factors) by using 20 I/O buffer nodes on Amazon EC2 environment, as well sa reduce 2-12 times of cost.
-\kento{please summirize the evaluation resutls here.}
+%\kento{Do you think this sentence is resonable to describe your model ?}.
+According to our simulation, we can achieve a 4-20 times higher throughput (depends on data locality and other factors) by using 20 I/O buffer nodes on Amazon EC2 environment, as well as reduce 2-12 times of cost.
+%\kento{please summirize the evaluation resutls here.}
 %  architecture that uses multiple nodes in each system as an I/O nodes 
@@
 
-Our contributions can be summrized as following:
+Our contributions can be summarized as following:
 \begin{itemize}
-	\item A I/O burst buffer for increasing data transfer throughput between two systems;
+	\item A I/O burst buffer architecture for increasing data transfer throughput between two systems;
 	\item A throughput-based I/O burst buffer model, which estimate I/O throughput of systems with I/O burst buffers, and a cost-based I/O burst buffer model, which estimate overall cost give a system configuration;
-        \item Evaluation of the I/O burst buffer architecture based the performance models by using real data obtained from several benchmarks from the TSUBAME supercomputer and AMAZON EC2.
+        \item Evaluation of the I/O burst buffer architecture based the performance models by using real data obtained from several benchmarks from the TSUBAME supercomputer and Amazon EC2.
 \end{itemize}
@@
 and show the performance models to evaluate the I/O bursting buffer architecture in Section \ref{sec:model}. 
-In Section \ref{sec:evaluation}, we present our experimental results based of our perfomrance models. %based on data obtained from several benchmark on TSUBAME V queue and AMAZON EC2 
+In Section \ref{sec:evaluation}, we present our experimental results based of our performance models. %based on data obtained from several benchmark on TSUBAME V queue and Amazon EC2 
 Finally, we detail related work in Section \ref{sec:related_work}, and conclusion in Section \ref{sec:conclusion}.

### 2014-07-01 paper/src/4_model.tex
0701

@@
 \label{sec:model}
-\kento{First, again mention why the modeling is important for reminder}
+%\kento{First, again mention why the modeling is important for reminder}
 %\begin{figure}[tb]
@@
 
-Since the instance type choice, Ethernet condition, Internet condition will affect the actual I/O throughput between two system, we introduce a throughput-based model, cost-based model and buffer queue write back model used to predict throughput, overall cost and in buffer rate when use I/O burst buffer and direct I/O, and using these predict model to make decision like which type of instance should use, and how many I/O nodes is needed in a particular cases.
-\kento{this sentences should be in the previsou section}.
+Since the instance type choice, interconnection network condition, Internet condition will affect the actual I/O throughput between two system, we introduce a throughput-based model, cost-based model and buffer queue write back model used to predict throughput, overall cost and in buffer rate when use I/O burst buffer and direct I/O, and using these predict model to make decision like which type of instance should use, and how many I/O nodes is needed in a particular cases.
+%\kento{this sentences should be in the previsou section}.
 
@@
 First we consider direct I/O, computing nodes read from and write back to storage in another system directly.
-In the case of direct I/O \kento{What is direct I/O.
-I think it means direct connection mode in Section 3, but no explanation at all}, computing nodes connect to storage in another system directly, there is only one data transfer, so both read and write throughput \kento{read ?
-or write ?
-or both ?} will be:%there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
+In the case of direct I/O, computing nodes connect to storage in another system directly, there is only one data transfer, so both read and write throughput will be:%there are two data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to storage in system 1, so throughput will be:
 \begin{equation}
@@
 When using I/O burst buffer, there will be three data transfers: computation nodes to I/O buffer nodes in system 2, I/O buffer nodes in system 2 to I/O buffer nodes in system 1, I/O buffer nodes in system 1 to storage in system 1,
-for reading, if required file is buffered in buffer queue, computing node can read data from buffer queue directly, then throughput will be:$E_2(n_2)$, similiarly, if buffer queue still have enough space for I/O data when issue a write request, computing nodes can write data to buffer queue, and throughput also will be:$E_2(n_2)$.
+for reading, if required file is buffered in buffer queue, computing node can read data from buffer queue directly, then throughput will be:$E_2(n_2)$, similarly, if buffer queue still have enough space for I/O data when issue a write request, computing nodes can write data to buffer queue, and throughput also will be:$E_2(n_2)$.
 
 If required file is not buffered in buffer queue when issue a read request, or when issue a write request buffer queue is full, the throughput will be:$\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)$, since for read request, file need to be read from storage in another system Internet, and for write request, it need to wait until buffer buffer write buffered file back the storage.
-throughput \kento{write ?
+throughput% \kento{write ?
 and read ?.
@@
 	\text{thr}_{\text{I/O buffer}}=\begin{cases}
-		E_2(n_2) &\text{buffer queue available}\\ 
-	\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\} &\text{buffer queue full or file miss}
+		E_2(n_2)&\\
+		\text{buffer queue available}&\\ 
+		\min\{M_1(n_1),I(n_1,n_2),E_2(n_2)\}& \\
+		\text{buffer queue full or file miss}&
 	\end{cases} \label{throughput2}
@@
 Although we have two cases for each read and write request (in buffer or not in buffer), it is very difficult to predict the in buffer rate, since it will be affected by I/O size, Internet throughput, buffer queue size and so on.
-\kento{Why do you swithches between direct I/O and burst buffer?}
+%\kento{Why do you swithches between direct I/O and burst buffer?}
 %\begin{equation}
@@
 
-\kento{Mention how do you switch between I/O burst buffers and direct I/O.
+%\kento{Mention how do you switch between I/O burst buffers and direct I/O.
 Will you dynamically shutdown/boot burst buffer nodes on demain ?.
@@
 \subsection{Cost-based Model}
-\kento{Again, it's hard to understand due to lack of information. Please read carfully over and over again and add more explanation like in the above}
-Although we may use I/O burst buffer to achieve a high I/O throughput and leading a decrease of execution time, and according to public cloud pay for usage policy, the cost for computing nodes may reduce, the relation between overall cost and I/O throughput can not be such simple, since I/O nodes will still charged for usage, and if we use a instance with high Ethernet condition in order to get a higher throughput, we may be charged for more money.
+%\kento{Again, it's hard to understand due to lack of information. Please read carfully over and over again and add more explanation like in the above}
+Although we may use I/O burst buffer to achieve a high I/O throughput and leading a decrease of execution time, and according to public cloud pay for usage policy, the cost for computing nodes may reduce, the relation between overall cost and I/O throughput can not be such simple, since I/O nodes will still charged for usage, and if we use a instance with high interconnection network condition in order to get a higher throughput, we may be charged for more money.
 
@@
 \end{equation}
-\kento{According to the difinition of $C_i\_Money(T)$ and $T_i$, the above model seems to be wrong. Please read carfully the model is correct}
+%\kento{According to the difinition of $C_i\_Money(T)$ and $T_i$, the above model seems to be wrong. Please read carfully the model is correct}
 \begin{align}
 	\begin{cases}
-		c_2\times C_2M(T_2)+n_1\times C_1HM(T_2)+n_2\times C_2HM(T_2)&\text{buffer queue available}\\
-		c_2\times C_2M(T_3)+n_1\times C_1HM(T_3)+n_2\times C_2HM(T_3) &\text{buffer queue full}
+		c_2\times C_2M(T_2)+n_1\times C_1HM(T_2)+n_2\times C_2HM(T_2)&\\
+		\text{buffer queue available}&\\
+		c_2\times C_2M(T_3)+n_1\times C_1HM(T_3)+n_2\times C_2HM(T_3)&\\
+		\text{buffer queue full}&
 	\end{cases}
@@
 
-\kento{I'm workding if the throuput is 	$\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}}$ the cost is $\text{cost}_{\text{direct}} \geq \text{cost}_{\text{I/O buffer}}$, which do you use, direct I/O and I/O buffer.}
+%\kento{I'm workding if the throuput is 	$\text{thr}_{\text{direct}} < \text{thr}_{\text{I/O buffer}}$ the cost is $\text{cost}_{\text{direct}} \geq \text{cost}_{\text{I/O buffer}}$, which do you use, direct I/O and I/O buffer.}
 
@@
 If the buffer size is unlimited.
-then we can buffer all data in the I/O buffer nodes, and achieve a high throughput in cloud burst \kento{Good work !!
+then we can buffer all data in the I/O buffer nodes, and achieve a high throughput in cloud burst% \kento{Good work !!
 As I said in the different sections, it's important to remind its motivation before describing the algorithm, techniques, model, or methods for its reminder}.
@@
 Consider Fig.~\ref{buffer queue}, assume average incoming throughput is A MB/s and average outgoing throughput is B MB/s, if A always larger than B, after $T$ time buffer queue will full.
-\[T=\frac{m_2\times n_2}{A-B}\]
+\begin{equation}
+T=\frac{m_2\times n_2}{A-B}
+\end{equation}
 
 After that, since buffer queue is full, I/O server can not send more data to I/O buffer nodes, have to block any read and write request since that.
-\kento{Why ??}.
+%\kento{Why ??}.

### 2014-07-01 paper/src/5-5_related_work.tex
0701

@@
 Cloud computing is becoming a topic of much interest in recent years, not only famous Internet companies like google, Amazon, IBM, Oracle, Microsoft provide public cloud, many companies start to build or have built private cloud for internal computation.
-Recently hybrid cloud, which is a composition of two or more clouds (private or public) is becoming a hot topic since it allows a business to take advantage of the scalability and cost-effectiveness that a public cloud offers without exposing critical application and data to third-party vulnerabilties, also by using cloud bursting, a small private cloud can easily burst into a large cloud to deal with temporality request peak.
-Several rearch works have been done on hybrid cloud and cloud bursting, Tekin Bicer \emph{el at.}\cite{time_and_cost} considered a software framework to enable data-intensive computing with cloud bursting, which use a combination of compute resources from local cluster and a public cloud to proceesing on a geographically distributed data set.
+Recently hybrid cloud, which is a composition of two or more clouds (private or public) is becoming a hot topic since it allows a business to take advantage of the scalability and cost-effectiveness that a public cloud offers without exposing critical application and data to third-party vulnerabilities, also by using cloud bursting, a small private cloud can easily burst into a large cloud to deal with temporarily request peak.
+Several research works have been done on hybrid cloud and cloud bursting, Tekin Bicer \emph{el at.}\cite{time_and_cost} considered a software framework to enable data-intensive computing with cloud bursting, which use a combination of compute resources from local cluster and a public cloud to processing on a geographically distributed data set.
 Their framework assume computation nodes allocated in both local cluster and public cloud, and data set is geographically distributed, However in our study, data set is stored in local system and in order to obtain a high communication throughput between computation nodes, we assume that nodes used for the same job allocated in the same system.
-Another cloud bursting application can be seen in Tian Guo\emph{el at.}\cite{Seagull}, they introduced a system called Seagull, designed to facilitate cloud brusting by determining which applications should be transitioned into the cloud and automating the movement process at the proper time.
-Their work focused on determine which applications should be moved to public cloud, and our work focus on the methdology of filling the I/O throughput in cloud bursting.
+Another cloud bursting application can be seen in Tian Guo\emph{el at.}\cite{Seagull}, they introduced a system called Seagull, designed to facilitate cloud bursting by determining which applications should be transitioned into the cloud and automating the movement process at the proper time.
+Their work focused on determine which applications should be moved to public cloud, and our work focus on the methodology of filling the I/O throughput in cloud bursting.
 
-There are also several paper about data I/O throughput, transfering and data processing in hybrid cloud.
-Chiba Tatsuhiro \emph{el at.}\cite{Chiba} proposed two high performance multicast algorithms used for transfering large amounts of data stored in Amazon S3 to multiple Amazon EC2 nodes.
+There are also several paper about data I/O throughput, transferring and data processing in hybrid cloud.
+Chiba Tatsuhiro \emph{el at.}\cite{Chiba} proposed two high performance multicast algorithms used for transferring large amounts of data stored in Amazon S3 to multiple Amazon EC2 nodes.
 Tekin Bicer \emph{el at.}\cite{MATE-EC2} also described a middleware that allows the specification of data processing using a high-level API in Amazon S3.

### 2014-07-01 paper/src/6_conclusion.tex
0701

@@
 
-From simulation result, we showed that our I/O burst buffer can burst I/O throughput about 4-20 times depends on cache hit rate as well as reduce overall cost about 2-12 times when Internet throughput is far smaller than interconnection throughput.
+From simulation result, we showed that our I/O burst buffer solution can burst I/O throughput about 4-20 times depends on cache hit rate as well as reduce overall cost about 2-12 times when Internet throughput is far smaller than interconnection throughput.
 

### 2014-07-01 paper/src/5_evaluation.tex
Partially updated 5_evalu, but not all.l

@@
 %In practice, I/O buffer nodes may have a better Ethernet condition than computing nodes, but there also will be many users running their application on large amount of computing nodes, so there can be several computing nodes reading data from or writing data to one I/O nodes, Ethernet bandwidth also can be fully utilized.
-In practice, an I/O buffer node may have higher network throghput condition than computing nodes, 
-but there also will be many users running their application on large amount of computing nodes, 
-so there can be several computing nodes reading data from or writing data to one I/O nodes, 
-Ethernet bandwidth also can be fully utilized.
+In practice, an I/O buffer node may have higher network throghput than computing nodes, and the throughput can not fully utilized.
+But we assume there are many users running their applications on large amount of computing nodes, which concurrently read data from or write data to one I/O bust buffer nodes, the network throughput to I/O buffer is fully utilized.
 
-Fig.~\ref{throughput comparison} and Fig.~\ref{throughput cache rate} shows the throughput comparison with and without I/O burst buffer.
-For direct I/O, each computing nodes will read from and write data to storage directly and concurrently, when number of nodes is small, throughput increases as number of nodes increses, but after throughput reach the Internet bandwidth( 120MB/s when number of nodes equals to 10 in our case), throughput becomes stable, means Internet bandwidth is fully utilized, and since that I/O is limited by Internet bandwidth.
+Fig.~\ref{throughput comparison} and Fig.~\ref{throughput cache rate} shows the throughput comparisons between systems  with and without I/O burst buffers.
+For direct I/O, each computing nodes read from and write data to storage directly and concurrently.
+When the number of nodes is small, throughput increases as the number of nodes increses.
+However, after throughput reach the peak bandwidth between two systems, (120MB/s when number of nodes equals to 10 in our case), 
+the throughput becomes flat. %, means Internet bandwidth is fully utilized, and since that I/O is limited by Internet bandwidth.
 
-For 0\% cache hit cases, since all data should be read from or write back to storage, throughput shows a similiar trade, also limited by Internet bandwidth.
+%For 0\% cache hit cases, since all data should be read from or write back to storage, throughput shows a similiar trade, also limited by Internet bandwidth.
+In 0\% cache rate cases, since all data should be read from or write back to storage, 
+the throughputs show a similiar trend.%, also limited by Internet bandwidth.
+\kento{Please explain why 0\% is better than others}
 
-The large difference shows in cache hit 100\%(Fig.~\ref{throughput cache rate}), since all required files are buffered in buffer queue, also buffer queue is not full, computing nodes can read from and write to buffer queue each time.
-As we mentioned, Ethernet throughput in Amazon EC2 shows a strong scalablity, I/O throughput can finially achieve around 2700MB/s, about 20 times faster than direct I/O and also 0\%cache hit cases.
+The large difference is shown in cache hit 100\%(Fig.~\ref{throughput cache rate}).
+In the 100\% cases, all reading files are buffered in buffer queue, 
+also buffer queue is not full for writes.
+Thus, computing nodes can read from and write to buffer queue each time withouth accessing to remote storage, 
+and the throghputs becomens identical to network throughputs between computing nodes and I/O buffer nodes.
+As we mentioned, network throughput between two instances within Amazon EC2 shows the scalablity even if we increase the pairs of two instances.
+I/O throughput can finially achieve around 2700MB/s, which is about 20 times faster than one of direct I/O.% and also 0\%cache hit cases.
 
-However 100\% cache hit is a ideal condition not pratical, so in Fig.~\ref{throughput cache rate}, we also show predict throughput for 75\%,50\% and 25\% cache hit rate.
-When there is a cache miss both in read and write, data need to be transfer via both Ethernet and Internet like 0\% cache hit case, and for cache hit, files can be read and written via Ethernet like 100\% cache hit case, so we use two-side Internet throughput($thr_I$) shown in Fig.~\ref{point to point connection LAB}, Ethernet throughput in Amazon($thr_E$) shown in Fig.~\ref{point to point connection AMAZON} and following formular to evaluate throughput for each cache hit rate.
+However, the 100\% cache rate is an ideal condition, and is not pratical in real applications, 
+so we also estimate the throughputs under 75\%,50\% and 25\% cache rates in Fig.~\ref{throughput cache rate}.
+%When there is a cache miss both in read and write, data need to be transfer via both Ethernet and Internet like 0\% cache hit case, and for cache hit, files can be read and written via Ethernet like 100\% cache hit case, so we use two-side Internet throughput($thr_I$) shown in Fig.~\ref{point to point connection LAB}, Ethernet throughput in Amazon($thr_E$) shown in Fig.~\ref{point to point connection AMAZON} and following formular to evaluate throughput for each cache hit rate.
+If the cache rate is low, most of reading and writing data need to be transferred via a network between the two systems, i.e, TSUBAME and Amazon EC2.
+If applications can use the cache for read or write, I/O throughputs can be improved depending on the cache rates.
+To estimate the throughputs under different cache rates, we use the below model.
 
@@
 
-Result is shown in Fig.~\ref{throughput cache rate}, we can see that althrough, 100\% cache hit achieve a high throughput, even 75\% cache hit is much lower than 100\%, it is because of the great gap between Ethernet bandwidth and Internet bandwidth, also data can transfer faster in Ethernet, user application must wait until cache miss data transferred through Internet.
+ we denote $thr_I$ as two-side network throughput shown in Fig.~\ref{point to point connection LAB}, 
+$thr_E$ network throughput within Amazon EC2 shown in Fig.~\ref{point to point connection AMAZON}.
 
-In this simulation we only consider one job use up to 20 computing nodes, but in practice, large number of computing nodes issue read and write request concurrently, Fig.~\ref{maximum throughput} shows the maximum throughput of different cache hit rate and direct I/O, we can see that although reading can not achieve a cache hit rate, until buffer queue is full, writing can achieve a extremely high throughput.
+%Result is shown in Fig.~\ref{throughput cache rate}, we can see that althrough, 100\% cache hit achieve a high throughput, even 75\% cache hit is much lower than 100\%, it is because of the great gap between Ethernet bandwidth and Internet bandwidth, also data can transfer faster in Ethernet, user application must wait until cache miss data transferred through Internet.
+As shown in Fig.~\ref{throughput cache rate}, we can also see that I/O throughputs in 75\% cache rate are much lower than ones of 100\% cache rate.
+This is because of a larege gap between network throughputs within Amazon EC2 and between the two systems, 
+applications must wait until reading or writing data, which is not in caches, are transferred from or to remote storage.
+
+In this simulation we only consider one job use up to 20 computing nodes, but in practice, a large number of computing nodes issue read and write requests concurrently, 
+Fig.~\ref{maximum throughput} shows the maximum throughput of different cache rates and direct I/O.
+%we can see  that although reading can not achieve a cache hit rate, until buffer queue is full, writing can achieve a extremely high throughput
+We can see that write can achieve an extremely high throughput using caches on I/O burst buffer nodes while read can not achieve that high throughput unless target files are in caches.
 %If file is buffered in I/O buffer nodes, computing nodes can read it through Ethernet, Fig.~\ref{cache hit}, shows the comparison, we can see that when Ethernet throughput larger than Internet throughput, our solution can achieve a higher I/O throughput, here we assume that Ethernet throuhput can be lower than Internet throughput, but from Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{throughput TSUBAME}, Ethernet usually is faster than Internet, and by using our solution can achieve a high throughput.
@@
 
-Then we compare overall cost with and without I/O burst buffer, As we mentioned, cost will be determined by both number of nodes and execution time. 
-As we showed, By using I/O burst buffer, we can achieve a high I/O throughput, and reduce both the execution time and cost, however, I/O buffer node also will be charged, hence we use following formular to evaluate cost
+%Then we compare overall cost with and without I/O burst buffer, As we mentioned, cost will be determined by both number of nodes and execution time. 
+Then we compare overall cost between systems with and without I/O burst buffers.
+As we mentioned, the cost is  determined by both the number of nodes and the execution time. 
+%As we showed, By using I/O burst buffer, we can achieve a high I/O throughput, and reduce both the execution time and cost, however, I/O buffer node also will be charged, hence we use following formular to evaluate cost
+As we showed, by using I/O burst buffers, we can achieve a high I/O throughput, 
+and reduce both the execution time and cost.
+However, I/O buffer nodes also is charged, hence we use following formular to evaluate the cost.
 \[cost=\frac{Data~size}{throughput}\times cost\_per\_hour\times node\]
-According to Amazon pricing policy, m3.xlarge instance is charged \$0.405 for each hour usage in Asia Pacific(Tokyo).
-For direct I/O, nodes is equal to number of computing nodes, but for I/O burst buffer, since we assume that number of I/O nodes is equal to number of computing nodes, here the value of node in above formular will be 2 times number of computing nodes.
+%According to the Amazon pricing policy, m3.xlarge instance is charged  \$0.405 for each hour usage in Asia Pacific(Tokyo).
+According to the Amazon pricing policy, m3.xlarge instance is charged by \$0.405 par hour in a Asia Pacific region (Tokyo).
+%For direct I/O, nodes is equal to number of computing nodes, but for I/O burst buffer, since we assume that number of I/O nodes is equal to number of computing nodes, here the value of node in above formular will be 2 times number of computing nodes.
+For direct I/O, we denotes $node$ as the total number of instances used at Amazon EC2. 
+Therefore, $node$ becomes the total number of compute nodes in a system with direct I/O, while $node$ is equal to the total number of both computing nodes and I/O buffer nodes in a system with I/O nodes.
+Since we assume that the number of I/O nodes is equal to the number of computing nodes, $node$ for a systen with I/O nodes becomes 2 times higher than $node$ for a system with direct I/O.
 
-Fig.~\ref{cost} shows cost comparison between each cache hit rate and direct I/O, which read or write 100GB data, we can see that cost grows as number of nodes grows, except for 100\% cache hit, which throughput is proportional to nodes number.
-As the Fig.~\ref{cost} shows, if cache hit rate is higher than 50\%, the overall cost using I/O burst buffer will lower than direct I/O, however, if cache hit rate is lower than 50\%, using I/O burst buffer will cost more.
+Fig.~\ref{cost} shows cost comparison between each cache hit rate and direct I/O, which read or write 100GB data.
+As shown in the figure,  we can see that cost grows as the number of nodes grows while there is an exception for 100\% cache hit, which throughput is proportional to nodes number.
+As shown in Fig.~\ref{cost}, if cache rate is higher than 50\%, the overall cost using I/O burst buffers become lower than direct I/O, however, if cache rate is lower than 50\%, using I/O burst buffer cost more.
 
-From above simulations, we can see that if we can achieve a high cache hit rate, we can achieve a high throughput up to 4-20 times faster than direct I/O as well as a low cost up to 2-12 times lower than direct I/O for 20 client nodes.
+From above simulations, we can see that if we can achieve a high cache rate, we can achieve a high throughput up to 4-20 times faster than direct I/O as well as a low cost up to 2-12 times lower than direct I/O for 20 client nodes.
 It is may be difficult for read data cache hit rate to be higher than 50\% (can be possible according to data locality), but it is reasonable for write data can be buffered in buffer queue, since public clouds usually provide instance with large size of memory, and it is easy to achieve a Tera size of buffer queue.

### 2014-07-01 paper/src/2_motivation.tex

@@
   \hline
-  \cellcolor{lightgray} Network  & QDR InfiniBnd *2 (80Gbps)\\
+  \cellcolor{lightgray} Network  & QDR InfiniBand *2 (80Gbps)\\
   \hline
@@
 
-\kento{Please explain what Public cloud is with example of Amazon EC2. Then, the details which is needed to mention for readers understand the rest of the sections.
-  (1-1) Architecture (VM environment \& datacetners are geographically distributed)
-  (1-2) Explain instance types which is related to this paper. Current draft does not mention any instance types.
-  (1-3) introduce pay-as-you-go model to help readers understand the cost-based model in the modeling section 
-  (1-4) [please add whatever you think it's needed]}
+%\kento{Please explain what Public cloud is with example of Amazon EC2. Then, the details which is needed to mention for readers understand the rest of the sections.
+ % (1-1) Architecture (VM environment \& datacetners are geographically distributed)
+  %(1-2) Explain instance types which is related to this paper. Current draft does not mention any instance types.
+  %(1-3) introduce pay-as-you-go model to help readers understand the cost-based model in the modeling section 
+  %(1-4) [please add whatever you think it's needed]}
 Public cloud is one in which the services and infrastructure such as applications and storage are provided off-site over the Internet, the main benefit of using a public cloud service are: easy fast and inexpensive set-up because hardware, application and bandwidth are covered by the provider, easy to scale to meet needs, no wasted resources because you pay for what you use.
-There are many companies provide public cloud solution like google, IBM, Microsoft etc., among them, Amazon Elastic Compute Cloud (Amazon EC2)\cite{AMAZON_AWS} is one of the most famous public cloud, like other public cloud, Amazon EC2 privdes Virtualize computing, and owns computing and data centers in several geographic regions.
+There are many companies provide public cloud solution like google, IBM, Microsoft etc., among them, Amazon Elastic Compute Cloud (Amazon EC2)\cite{AMAZON_AWS} is one of the most famous public cloud, like other public cloud, Amazon EC2 provides Virtualize computing, and owns computing and data centers in several geographic regions.
 Amazon EC2 provide a large amount of instance types optimized to fit different use cases comprise varying combinations of CPU, memory, storage, and networking capacity.
-In this study, we used general purpose m3.xlarge instance which has 4 vCPUs, 15GiB memory, 2*80GB SSD storage and high level Ethernet network condition in Tokyo region, we run Amazon Linux AMI 2014.03.2 (HVM), which is based on Linux 3.10 on these instances.
+In this study, we used general purpose m3.xlarge instance which has 4 vCPUs, 15GiB memory, 2*80GB SSD storage and high level interconnection network network condition in Tokyo region, we run Amazon Linux AMI 2014.03.2 (HVM), which is based on Linux 3.10 on these instances.
 Amazon EC2 charges for nodes usage, Amazon use a pay-as-you-go pricing policy\cite{AMAZON_AWS}, which means you pay only for what you use, there is no minimum fee and you will pay for compute capacity by the hour with no long-term commitments.
 \subsection{Federation between supercomputers and clouds}
-\kento{Please explain (2-1) how we federate supercomputers with clouds. $=>$ Virtualize supercomputer (e.g. TSUBAME V) + VM on clouds. 
-                      (2-2) what the advantages are. $=>$ VMs can provide the same execution environment on both supercomputers and clouds
-                      (2-3) [please add whatever you think it's needed]}
-When we try to federate supercomputer with public clouds, there are need to have a similiar performance and environment between these two systems.
-So we virtualize the supercomputer(like TSUBAME V queue) and federate VMs running on supercomputers with VMs provided by public cloud.
+%\kento{Please explain (2-1) how we federate supercomputers with clouds. $=>$ Virtualize supercomputer (e.g. TSUBAME V) + VM on clouds. 
+%                      (2-2) what the advantages are. $=>$ VMs can provide the same execution environment on both supercomputers and clouds
+%                      (2-3) [please add whatever you think it's needed]}
+When we try to federate supercomputer with public clouds, there are need to have a similar performance and environment between these two systems.
+So we virtualize the supercomputer(like TSUBAME U queue) and federate VMs running on supercomputers with VMs provided by public cloud.
 By using VMs, we can run the same image on both supercomputer and public cloud as well as set both the same specification, and make it looks the same to user.%we can use in order to get the same execution environment on both supercomputers and clouds, we virtualize supercomputer, e.g.
@@
 \label{sec:problems}
-\kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
-                        (3-2) Then, please briefly clarfy why ``(A) I/O burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
-                              (Remember we knew that I/O burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
-                        (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
-                              In addtion, the choice of instances, the trade-offs are changes depending on given a supercomputer and cloud environments, such as network throughput, PFS performance. 
-                              That's why the ``(B) perfomrance modeling`` is important}
-Although we virtualize supercomputer and obtain a similiar environment on both supercomputers and clouds, there are still several problems remains, for example, input data of applications running on supercomputer is usually stored in shared storages in the same system and can be read from and wrote to these storages with a extremely high throughput.
+%\kento{In this section, (3-1) First explain I/O problems in federation with clouds based on the cloud architecture explained in the above (1-1) as well as using Fig.1-4. 
+%                        (3-2) Then, please briefly clarfy why ``(A) I/O burst buffer`` can improve I/O performance without using model. For example, parallel I/O, cacheing .... 
+%                              (Remember we knew that I/O burst buffer is effective before compareing the performances between w/ and w/o burst buffers by using performance model)
+%                        (3-3) Another challenge is a choice of instance types for burst buffer, and understanding the trade-off between I/O perfomrance and the monetary cost. 
+%                              In addtion, the choice of instances, the trade-offs are changes depending on given a supercomputer and cloud environments, such as network throughput, PFS performance. 
+%                              That's why the ``(B) perfomrance modeling`` is important}
+Although we virtualize supercomputer and obtain a similar environment on both supercomputers and clouds, there are still several problems remains, for example, input data of applications running on supercomputer is usually stored in shared storages in the same system and can be read from and wrote to these storages with a extremely high throughput.
 
 We use Iperf\cite{iperf}, which was developed by NLANR/DAST as a modern alternative for measuring TCP and UDP bandwidth performance, and IOR\cite{IOR}, which is widely used for benchmarking parallel file systems using POSIX, MPIIO, or HDF5 interfaces.
-Fig.~\ref{throughput TSUBAME} shows read and write throughput from TSUBAME V queue nodes (VM runing on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}) and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
+Fig.~\ref{throughput TSUBAME} shows read and write throughput from TSUBAME V queue nodes (VM running on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}) and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
 However, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, since TSUBAME Lustre can not be accessed outside of TSUBAME because of security problem, instead of TSUBAME Lustre file system, we used a file server inside our lab, which has 1GBit/s internet bandwidth, also because of security problem, we used sshfs\cite{sshfs},which is a filesystem client based on SSH File Transfer Protocol, to mount this file system from Amazon.
@@
 
-However, when we look at Ethernet throughput inside Amazon as Fig.\ref{point to point connection AMAZON} shows, although we only show the result up to 8 pairs of nodes, each node achieved only 135MB/s (1GBit/s), the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
-since when we running the benchmark, many other users were also running applications on Amazon, so we can assume that highest throughput 1GB/s (8Gbit/s) shown in Fig.~\ref{point to point connection AMAZON} is not the maximum bandwidth of Ethernet in Amazon EC2 .
-Comparing Fig.~\ref{point to point connection AMAZON} with Fig.~\ref{throughput AMAZON to OURLAB} and Fig.~\ref{point to point connection LAB}, Ethernet throughput is much higher than Internet, it shows that our solution, by using I/O buffer nodes can achieve a higher Ethernet throughput than Internet.
+However, when we look at interconnection network throughput inside Amazon as Fig.\ref{point to point connection AMAZON} shows, although we only show the result up to 8 pairs of nodes, each node achieved only 135MB/s (1GBit/s), the influence between nodes is extremely small, figure shows a perfect linear line also a strong scalability.
+since when we running the benchmark, many other users were also running applications on Amazon, so we can assume that highest throughput 1GB/s (8Gbit/s) shown in Fig.~\ref{point to point connection AMAZON} is not the maximum bandwidth of interconnection network in Amazon EC2 .
+Comparing Fig.~\ref{point to point connection AMAZON} with Fig.~\ref{throughput AMAZON to OURLAB} and Fig.~\ref{point to point connection LAB}, interconnection network throughput is much higher than Internet, it shows that our solution, by using I/O buffer nodes can achieve a higher interconnection network throughput than Internet.
 
-To solve this problem, we propose our I/O burst buffer architecture, since usually Internet throuhput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transfering file between two systems, hence achieve a high I/O throughput.
-Althought using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost, we will introduce a throughput-based model and a cost-based model to predict the throughput and overall cost.
+To solve this problem, we propose our I/O burst buffer architecture, since usually Internet throughput is the bottleneck, by using parallel I/O and cacheing file in I/O buffer nodes, we can fully utilize the Internet bandwidth as well as avoid frequently transferring file between two systems, hence achieve a high I/O throughput.
+Although using I/O buffer can increase I/O throughput, reduce the execution time and cost, I/O buffer nodes will be charged for usage, also a better instance will cost more than a normal one, there will be a trade-off between I/O performance and monetary cost, we introduce a throughput-based model and a cost-based model to predict the throughput and overall cost.
 %Moreover, the instance choice, number of I/O nodes depends on supercomputer and pulic cloud environment, in our following section, we will provide a performance modele
@@
 %when we try to move some jobs to public clouds after federation, the data 
-\kento{Then, in the rest of the section, we explain (A) and (B)}
+%\kento{Then, in the rest of the section, we explain (A) and (B)}
 
 %\subsection{(Current Section 2)}
-\kento{Please fit the below sentences to the above sections with additional explanations}
+%\kento{Please fit the below sentences to the above sections with additional explanations}
 
@@
 
-%Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes \kento{Describe node specification in Table I}(VM runing on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}), which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
+%Fig.~\ref{throughput TSUBAME} shows I/O throughput between TSUBAME V queue nodes \kento{Describe node specification in Table I}(VM running on TSUBAME Thin node, which specification is shown in \tabref{tbl:spec}), which run on VM on several shared machines and TSBUAME Lustre file system, which is mounted by using lustre client, it is a interconnection throughput inside TSUBAME supercomputer, we can see that I/O throughput growing as numbers of nodes growing, and the aggregate read and write throughput reach 6-8GB/s with 64 nodes, the same result also can be seen in \cite{checkpointing}.
 %On the other hand, Fig.~\ref{throughput AMAZON to OURLAB} shows I/O throughput between AMAZON EC2 nodes and a file system machine inside our lab, which has about 1GBit/s Internet access.

### 2014-07-01 paper/src/3_burst_buffer.tex

@@
-\section{I/O Bursting Buffer Overview}
+\section{I/O Burst Buffer Overview}
 % Why I/O server in client nodes
@@
 Two kinds of buffer are used in our I/O burst buffer architecture, the first one is in client computing node, first buffer user I/O in the same node, another one is in I/O buffer nodes.
-The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, for write I/O data, if buffer queue in I/O buffer nodes is not full, data can first be buffered in buffer queue in the same system, and then be transferred to final storage system, and for reading, if that file is stored in the buffer queue, computing nodes can read from I/O nodes through Ethernet.
-In other cases (buffer queue is full when issue a write requst or requsted file is not stored in buffer queue when issue a read request we call it cache miss), an read from or write back operation described below will be executed.
-\kento{how about read ?}.
+The main idea is that some of computing nodes serve as a I/O buffer nodes in each system, for write I/O data, if buffer queue in I/O buffer nodes is not full, data can first be buffered in buffer queue in the same system, and then be transferred to final storage system, and for reading, if that file is stored in the buffer queue, computing nodes can read from I/O nodes through interconnection network.
+In other cases (buffer queue is full when issue a write request or requested file is not stored in buffer queue when issue a read request we call it cache miss), an read from or write back operation described below will be executed.
+%\kento{how about read ?}.
 %the same computing nodes and then these I/O buffer nodes, after that data will be  transferred to storage in another system.
@@
 %Fig.~\ref{overview} and Fig.~\ref{I/O server} are the overall illustrate of I/O Bursting Buffer:
-There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst buffer nodes}, computing nodes run user's application and I/O burst buffer nodes.
-Among I/O burst buffer nodes, there is a master nodes, which maintain a global buffer queue and a namespace, controll buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
+There are two kinds of nodes in our I/O burst buffer architecture: \emph{computing nodes} and \emph{I/O burst nodes}, computing nodes run user's application and I/O burst nodes.
+Among I/O burst nodes, there is a master nodes, which maintain a global buffer queue and a namespace, control buffer read and write, and manage I/O buffer nodes, buffer data is distributed to all I/O buffer nodes in order to enable concurrent read and write.
 
-Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst buffer nodes.
-In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data, communicate with I/O buffer nodes, including send I/O requset and send or receive I/O data.
+Fig.~\ref{I/O server} is a illustrate of I/O server inside client nodes and buffer queue in I/O burst nodes.
+In each computing node, there is a I/O server, which is a filesystem client used to buffer I/O data, communicate with I/O buffer nodes, including send I/O request and send or receive I/O data.
 
-When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O server will try to transfer I/O data to buffer queue in I/O burst buffer, if buffer queue in not full, I/O data will be sent to I/O burst buffer via Ethernet and can be seen among computing nodes in the same system after that.
-However if buffer queue is full, I/O server will block user application and wait until buffer queue is ready to recieve new I/O data, causing a low I/O throughput.
+When a user application issue a write request, I/O data will be buffered in that node by I/O server, when user close the file, call flush function or I/O data size exceed I/O server buffer size, I/O server will try to transfer I/O data to buffer queue in I/O burst buffer, if buffer queue in not full, I/O data will be sent to I/O burst buffer via interconnection network and can be seen among computing nodes in the same system after that.
+However if buffer queue is full, I/O server will block user application and wait until buffer queue is ready to receieve new I/O data, causing a low I/O throughput.
 
@@
 
-Similiarly when user issue a read request, there are two conditions: required file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
+Similarly when user issue a read request, there are two conditions: required file is buffered in buffer queue in I/O burst buffer, or file is stored only in storage in another system.
 In the first cases, file can be transferred to computing nodes from buffer queue directly, and can achieve a high throughput.
@@
 
-In this section we describe read and write operations when cache miss happens.%file is not in I/O buffer nodes or file needs to be write back to storage in another system.
+In this section we describe read and write operations when cache miss happens.
+%file is not in I/O buffer nodes or file needs to be write back to storage in another system.
 We propose two kinds of model: one-side buffer and two-side buffer.
@@
 %the bottleneck is still Internet throughput, since interconnection is far faster than Internet.
-However since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than tranferring time, and compress data can make more data buffered in buffer queue.
+However since two-side buffer does not read data from or write data to storage directly, it means we can compress data before transfer it, though it will take some time to compress and decompress data, when the Internet throughput is extremely low, compress and decompress time will be far smaller than transferring time, and compress data can make more data buffered in buffer queue.
 Also, unlike one-side buffer, two-side buffer do not require storage to be opened to Internet, only required several I/O nodes have access to Internet.
 
-For these reasons, in the following section, we will use two-side buffer model as our read from and write back model in I/O burst buffer.
+For these reasons, in the following section, we use two-side buffer model as our read from and write back model in I/O burst buffer.
 %I/O bursting buffer model may be used when throughput of direct connection between I/O buffer nodes and storage in different cloud is smaller then throughput between I/O buffer nodes, it is possible when storage is consist of few nodes, and direct connection will be 1-N connection, on the contrary, connection between I/O buffer nodes is N-N connection, has larger parallelism.

### 2014-07-01 paper/src/5_evaluation.tex
a

@@
 benchmarks on both our in-house cluster and Amazon EC2 in a Tokyo region in Section \ref{sec:motivation}.%, using
-In the simulations, we assume that computing nodes running on one system read or write files on storage of the other system with the same I/O throghputs for both read and write operations.
+In the simulations, we assume that computing nodes running on one system read or write files on storage of the other system with the same I/O throughput for both read and write operations.
 We also assume an instance type of both the computing nodes and I/O burst buffer nodes is m3.xlarge provided by Amazon EC2.
-We compare I/O throughputs and overall costs of a system using direct I/O with a system using I/O burst buffer by scaling out up to 20 computing nodes
+We compare I/O throughput and overall costs of a system using direct I/O with a system using I/O burst buffer by scaling out up to 20 computing nodes
 under different cahch hit rate.
@@
 %Consider we have up to 20 m3.xlarge computing nodes need to transfer data between two systems, 
-%Since read and write throughput are the same when using caches on I/O burst buffers, read and write throughputs are equal to throghputs  between computing nodes and I/O nodes,  we use this throughput value for I/O throughput when use I/O burst buffer..
+%Since read and write throughput are the same when using caches on I/O burst buffers, read and write throughput are equal to throughput  between computing nodes and I/O nodes,  we use this throughput value for I/O throughput when use I/O burst buffer..
 If read and write are completed via caches on I/O burst buffers
-without accessing to remote storage, read and write throghputs become 
-identical to throughputs between a compute node and I/O burst buffer nodes. 
-%Thus, we use these throughputs for I/O throghputs
-%m3.medium instance, which has a moderate Ethernet condition and one vcpu with 3.75GiB memory, and
-%m3.xlarge instance, which has a high Ethernet condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}.
+without accessing to remote storage, read and write throughput become 
+identical to throughput between a compute node and I/O burst buffer nodes. 
+%Thus, we use these throughput for I/O throughput
+%m3.medium instance, which has a moderate interconnection network condition and one vcpu with 3.75GiB memory, and
+%m3.xlarge instance, which has a high interconnection network condition and 8 vCPUs with 30GiB memory, run Amazon Linux AMI 2014.03.2(HVM) ( Fig.~\ref{throughput TSUBAME}, Fig.~\ref{throughput AMAZON to OURLAB}.
 Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{point to point connection LAB} ).
@@
 
-%Since it is hard for one node to fully utilize Internet and Ethernet bandwidth, according to Fig.~\ref{throughput AMAZON to OURLAB}, we assume that one node can achieve 80\% of maximum bandwidth, and by using I/O burst buffer, can achieve 100\% of maximum bandwidth of both Ethernet and Internet, here Ethernet throughput refers to Ethernet connection throughput in public cloud.
+%Since it is hard for one node to fully utilize Internet and interconnection network bandwidth, according to Fig.~\ref{throughput AMAZON to OURLAB}, we assume that one node can achieve 80\% of maximum bandwidth, and by using I/O burst buffer, can achieve 100\% of maximum bandwidth of both interconnection network and Internet, here interconnection network throughput refers to interconnection network connection throughput in public cloud.
 
-First we compare I/O throughputs of direct connection with the throughput of  I/O burst buffer under different cache hit rates assuming that TSUBAME is federated with Amazon EC2.
-%In this simulation, we assume that both I/O buffer nodes and computing nodes use m3.xlarge instance and Amazon Linux AMI, and the number of I/O buffer nodes is equal to number of computing nodes in order to achieve a maximum Ethernet throughput.
-In this simulation, the number of I/O buffer nodes is equal to the number of computing nodes. This configuration can achieve a maximum I/O throughputs.
-%In practice, I/O buffer nodes may have a better Ethernet condition than computing nodes, but there also will be many users running their application on large amount of computing nodes, so there can be several computing nodes reading data from or writing data to one I/O nodes, Ethernet bandwidth also can be fully utilized.
+First we compare I/O throughput of direct connection with the throughput of  I/O burst buffer under different cache hit rates assuming that TSUBAME is federated with Amazon EC2.
+%In this simulation, we assume that both I/O buffer nodes and computing nodes use m3.xlarge instance and Amazon Linux AMI, and the number of I/O buffer nodes is equal to number of computing nodes in order to achieve a maximum interconnection network throughput.
+In this simulation, the number of I/O buffer nodes is equal to the number of computing nodes. This configuration can achieve a maximum I/O throughput.
+%In practice, I/O buffer nodes may have a better interconnection network condition than computing nodes, but there also will be many users running their application on large amount of computing nodes, so there can be several computing nodes reading data from or writing data to one I/O nodes, interconnection network bandwidth also can be fully utilized.
 In practice, an I/O buffer node may have higher network throghput than computing nodes, and the throughput can not fully utilized.
@@
 
-%For 0\% cache hit cases, since all data should be read from or write back to storage, throughput shows a similiar trade, also limited by Internet bandwidth.
+%For 0\% cache hit cases, since all data should be read from or write back to storage, throughput shows a similar trade, also limited by Internet bandwidth.
 In 0\% cache rate cases, since all data should be read from or write back to storage, 
-the throughputs show a similiar trend.%, also limited by Internet bandwidth.
-\kento{Please explain why 0\% is better than others}
+the throughput show a similar trend.%, also limited by Internet bandwidth.
+%\kento{Please explain why 0\% is better than others}
 
@@
 also buffer queue is not full for writes.
-Thus, computing nodes can read from and write to buffer queue each time withouth accessing to remote storage, 
-and the throghputs becomens identical to network throughputs between computing nodes and I/O buffer nodes.
+Thus, computing nodes can read from and write to buffer queue each time without accessing to remote storage, 
+and the throughput becomens identical to network throughput between computing nodes and I/O buffer nodes.
 As we mentioned, network throughput between two instances within Amazon EC2 shows the scalablity even if we increase the pairs of two instances.
-I/O throughput can finially achieve around 2700MB/s, which is about 20 times faster than one of direct I/O.% and also 0\%cache hit cases.
+I/O throughput can finally achieve around 2700MB/s, which is about 20 times faster than one of direct I/O.% and also 0\%cache hit cases.
 
-However, the 100\% cache rate is an ideal condition, and is not pratical in real applications, 
-so we also estimate the throughputs under 75\%,50\% and 25\% cache rates in Fig.~\ref{throughput cache rate}.
-%When there is a cache miss both in read and write, data need to be transfer via both Ethernet and Internet like 0\% cache hit case, and for cache hit, files can be read and written via Ethernet like 100\% cache hit case, so we use two-side Internet throughput($thr_I$) shown in Fig.~\ref{point to point connection LAB}, Ethernet throughput in Amazon($thr_E$) shown in Fig.~\ref{point to point connection AMAZON} and following formular to evaluate throughput for each cache hit rate.
+However, the 100\% cache rate is an ideal condition, and is not practical in real applications, 
+so we also estimate the throughput under 75\%,50\% and 25\% cache rates in Fig.~\ref{throughput cache rate}.
+%When there is a cache miss both in read and write, data need to be transfer via both interconnection network and Internet like 0\% cache hit case, and for cache hit, files can be read and written via interconnection network like 100\% cache hit case, so we use two-side Internet throughput($thr_I$) shown in Fig.~\ref{point to point connection LAB}, interconnection network throughput in Amazon($thr_E$) shown in Fig.~\ref{point to point connection AMAZON} and following formular to evaluate throughput for each cache hit rate.
 If the cache rate is low, most of reading and writing data need to be transferred via a network between the two systems, i.e, TSUBAME and Amazon EC2.
-If applications can use the cache for read or write, I/O throughputs can be improved depending on the cache rates.
-To estimate the throughputs under different cache rates, we use the below model.
+If applications can use the cache for read or write, I/O throughput can be improved depending on the cache rates.
+To estimate the throughput under different cache rates, we use the below model.
 
-\[throughput=\frac{1}{MAX\{\frac{{hit\_rate}}{thr_E},\frac{1-hit\_rate}{thr_I}+\frac{1-hit\_rate}{thr_E}\}}\]
+\[throughput(n)=\frac{1}{MAX\{\frac{{cache\_rate}}{E_2(n)},\frac{1-cache\_rate}{I(n,n)}+\frac{1-cache\_rate}{E_2(n)}\}}\]
 
- we denote $thr_I$ as two-side network throughput shown in Fig.~\ref{point to point connection LAB}, 
-$thr_E$ network throughput within Amazon EC2 shown in Fig.~\ref{point to point connection AMAZON}.
+we denote $I(n,n)$ as two-side network throughput shown in Fig.~\ref{point to point connection LAB}, 
+$E_2(n)$ network throughput within Amazon EC2 shown in Fig.~\ref{point to point connection AMAZON}.
 
-%Result is shown in Fig.~\ref{throughput cache rate}, we can see that althrough, 100\% cache hit achieve a high throughput, even 75\% cache hit is much lower than 100\%, it is because of the great gap between Ethernet bandwidth and Internet bandwidth, also data can transfer faster in Ethernet, user application must wait until cache miss data transferred through Internet.
-As shown in Fig.~\ref{throughput cache rate}, we can also see that I/O throughputs in 75\% cache rate are much lower than ones of 100\% cache rate.
-This is because of a larege gap between network throughputs within Amazon EC2 and between the two systems, 
+%Result is shown in Fig.~\ref{throughput cache rate}, we can see that althrough, 100\% cache hit achieve a high throughput, even 75\% cache hit is much lower than 100\%, it is because of the great gap between interconnection network bandwidth and Internet bandwidth, also data can transfer faster in interconnection network, user application must wait until cache miss data transferred through Internet.
+As shown in Fig.~\ref{throughput cache rate}, we can also see that I/O throughput in 75\% cache rate are much lower than ones of 100\% cache rate.
+This is because of a larege gap between network throughput within Amazon EC2 and between the two systems, 
 applications must wait until reading or writing data, which is not in caches, are transferred from or to remote storage.
@@
 We can see that write can achieve an extremely high throughput using caches on I/O burst buffer nodes while read can not achieve that high throughput unless target files are in caches.
-%If file is buffered in I/O buffer nodes, computing nodes can read it through Ethernet, Fig.~\ref{cache hit}, shows the comparison, we can see that when Ethernet throughput larger than Internet throughput, our solution can achieve a higher I/O throughput, here we assume that Ethernet throuhput can be lower than Internet throughput, but from Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{throughput TSUBAME}, Ethernet usually is faster than Internet, and by using our solution can achieve a high throughput.
+%If file is buffered in I/O buffer nodes, computing nodes can read it through interconnection network, Fig.~\ref{cache hit}, shows the comparison, we can see that when interconnection network throughput larger than Internet throughput, our solution can achieve a higher I/O throughput, here we assume that interconnection network throuhput can be lower than Internet throughput, but from Fig.~\ref{point to point connection AMAZON}, Fig.~\ref{throughput TSUBAME}, interconnection network usually is faster than Internet, and by using our solution can achieve a high throughput.
 
 %Then, we compare throughput with and without I/O buffer nodes.
-%We can see from Fig.~\ref{throughput},although our solution can be limited by both Internet and Ethernet throughput, our I/O burst buffer can fully utilize both Internet and Ethernet.
-Like previous comparison, when Ethernet is faster than Internet, our solution can achieve a throughput burst even file is not stored in buffer queue in I/O burst buffer like (read data from storage).
+%We can see from Fig.~\ref{throughput},although our solution can be limited by both Internet and interconnection network throughput, our I/O burst buffer can fully utilize both Internet and interconnection network.
+Like previous comparison, when interconnection network is faster than Internet, our solution can achieve a throughput burst even file is not stored in buffer queue in I/O burst buffer like (read data from storage).
 
@@
 However, I/O buffer nodes also is charged, hence we use following formular to evaluate the cost.
-\[cost=\frac{Data~size}{throughput}\times cost\_per\_hour\times node\]
+\[cost(n)=\frac{Data~size}{throughput(n)}\times C_2HM\times n\]
 %According to the Amazon pricing policy, m3.xlarge instance is charged  \$0.405 for each hour usage in Asia Pacific(Tokyo).
@@
 %For direct I/O, nodes is equal to number of computing nodes, but for I/O burst buffer, since we assume that number of I/O nodes is equal to number of computing nodes, here the value of node in above formular will be 2 times number of computing nodes.
-For direct I/O, we denotes $node$ as the total number of instances used at Amazon EC2. 
-Therefore, $node$ becomes the total number of compute nodes in a system with direct I/O, while $node$ is equal to the total number of both computing nodes and I/O buffer nodes in a system with I/O nodes.
-Since we assume that the number of I/O nodes is equal to the number of computing nodes, $node$ for a systen with I/O nodes becomes 2 times higher than $node$ for a system with direct I/O.
+For direct I/O, we denotes $n$ as the total number of instances used at Amazon EC2. 
+Therefore, $n$ becomes the total number of compute nodes in a system with direct I/O, while $n$ is equal to the total number of both computing nodes and I/O buffer nodes in a system with I/O nodes.
+Since we assume that the number of I/O nodes is equal to the number of computing nodes, $n$ for a systen with I/O nodes becomes 2 times higher than $n$ for a system with direct I/O.
 
@@
 %Since we assume number of I/O buffer node increases as number of computing nodes increases, 
-%After that, we compare overall cost when use two-side buffer and one-side buffer, since execution time, in our case, I/O time and I/O throughput will affect cost, for Internet and Ethernet throughput, we use.
+%After that, we compare overall cost when use two-side buffer and one-side buffer, since execution time, in our case, I/O time and I/O throughput will affect cost, for Internet and interconnection network throughput, we use.
 %From Fig.~\ref{cost},
